### 2019-11-23 1-illusion/report.tex
Add the report template for Project 1

\documentclass[journal]{IEEEtran}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{amsmath}
\usepackage{comment}
%\usepackage{cases}
%\usepackage{subeqnarray}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Bare Demo of IEEEtran.cls for Journals}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
        John~Doe,~\IEEEmembership{Fellow,~OSA,}
        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\thanks{M. Shell is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
%
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}
\IEEEPARstart{T}{his}

\section{Subjective IQA}

\section{Objective IQA}

\subsection{FR}

\subsubsection{Spatial Method}
Peak signal-to-noise ($PSNR$) is a classic objective full-reference $IQA$ metric and is commonly used to measure the fidelity of degraded images. $PSNR$ is most easily defined via mean square error ($MSE$). Given a $m \times n$ reference image $I$ and its distorted version $K$, the $MSE$ is defined as equation \ref{eq:PSNR 1}.
\begin{equation}
MSE = \frac{1}{mn} \sum\limits_{i=0}^{m-1} \sum\limits_{j=0}^{n-1} [I(i,j)-K(i,j)]^2
\label{eq:PSNR 1}
\end{equation}
And the $PSNR$ (in $dB$) is defined as:
\begin{equation}
PSNR = 10\log_{10} (\frac{MAX_I^2}{MSE})
\label{eq:PSNR 2}
\end{equation}
where $MAX_I^2$ is the maximum possible pixel value of the $I$ ($i.e.$ peak value). However, in some circumstances, the $PSNR$ is unequal to the perceptual quality prediction task because the human perception is depended on much more complicated factors.

\subsubsection{Transformation-based Method}
Sheikh \textit{et al.} \cite{ilg2017flownet} explored the image quality assessment problem from the perspective of information theory, and they utilized the widely investigated natural scene statistics ($NSS$) models to fit the quality score. Specifically, they adopted two different $NSS$ models to represent the reference image and distorted image. The reference image is expressed by Gaussian Scale Mixtures ($GSM$) in the wavelet domain, while the distorted image is expressed by a simple signal attenuation and additive Gaussian noise model in the wavelet domain. The final information fidelity criterion ($IFC$) is derived from the mutual information between the source and distorted images as equation \ref{eq:NSS 1}-\ref{eq:NSS 2}.
\begin{equation}
I(C^N; D^N | S^N) = \frac{1}{2} \sum\limits_{i=1}^{N}\log_2(1+\frac{g_i^2 s_i^2 \sigma_U^2}{\sigma_V^2})
\label{eq:NSS 1}
\end{equation}

\begin{equation}
IFC = \sum_{k \in subbands}I(C^{N_k,k};D^{N_k,k}|s^{N_k,k})
\label{eq:NSS 2}
\end{equation}
where equation \ref{eq:NSS 1} is the derived for one subband, and the final $IFC$ is the sum over all subbands.

\subsubsection{Learning-based Method}
Narwaria \textit{et al.} \cite{lotter2016deep} developed the machine learning technique and proposed a novel objective $IQA$ metric in 2010. The contribution of this job is using singular value decomposition ($SVD$) as features for quantifying image structural information. And the support vector regression served as a feature fusion tool to generate the quality score. The authors also pointed that the advantages of machine learning technique in $IQA$ devising are that the combination of the features are optimal and the weighting coefficients are adjustable so as to obtain the most appropriate settings.

\subsection{Saliency-Guided IQA}
Human visual attention is the behavioral and cognitive process of selectively concentrating on the special region of the stimulus. Image quality is highly related with artifacts located at salient regions. Saliency-gudied IQA has been widely investigated recently. We divided the saliency-gudied IQA metrics into two categories, which are indirect pooling manner and direct fitting manner. The indirect pooling manner is utilizing human attention information as weighting map to emphasize salient regions so as to promote IQA metrics' performances, while the direct fitting manner aims to explore the relationship between human attention variation and image quality degradation so as to devise new IQA metrics.
Moreover, the indirect pooling manner can be further classified as subjective ground truth-based pooling manner and objective saliency map-based pooling manner.

\subsubsection{Indirect Pooling Manner}
\paragraph{Subjective Ground Truth-based Pooling Manner}

Although objective saliency prediction model has been widely investigated, there is still a gap between state-of-the-art saliency models and real human fixation data. Fortunately, relying on the development of eye-tracking equipment, eye-tracking data has been the most accurate and solid proxy for visual attention information. Eye-tracking data-guided pooling strategy has been explored in recent years for improving IQA metrics.

\section{Conclusion}
The conclusion goes here.

\bibliographystyle{IEEEtran}
\bibliography{ref}

\end{document}

### 2019-11-24 1-illusion/prednet/img_process.py
can save predicted frames as individual files

@@ -56,4 +56,41 @@ def get_static_test_data(IMG_DIR, nt=10, size=(160, 128)):
     # print(test_data)
     return test_data
 
-# get_static_test_data()
+
+def get_raw_images(IMG_DIR, size=(160, 128)):
+    raw = []
+    for filename in os.listdir(IMG_DIR):
+        im = Image.open(os.path.join(IMG_DIR, filename))
+
+        im = im.resize(size, Image.ANTIALIAS)
+        # frame.save("./imgs/frame%d.png" % index)
+
+        raw.append(np.asarray(im.convert('RGB')))
+
+    raw = np.array(raw)
+    raw = raw / 255
+    print(raw.shape)
+    return raw
+
+
+def save_images_from_np(X_hat, raw_img):
+    for j in range(X_hat.shape[0]):
+        print('saving image ' + str(j) + '...')
+        im = Image.fromarray((raw_img[j]*255).astype(np.uint8))
+        im.save('results/output/img' + str(j) + '-0.png')
+
+        frames = X_hat[j]
+        for i in range(1, frames.shape[0]):
+            im = Image.fromarray((frames[i]*255).astype(np.uint8))
+            im.save('results/output/img' + str(j) + '-' + str(i) + '.png')
+            # plt.imshow(frames[i])
+            # plt.axis('off')
+            # plt.tight_layout()
+            # plt.savefig('results/output/img' + str(j) + '-' + str(i) + '.png', bbox_inches='tight', pad_inches=0.0)
+            # plt.show()
+
+
+if __name__ == '__main__':
+    X_hat = np.load('./results/pred_rotate.npy')
+    raw_img = get_raw_images('test_data/static')
+    save_images_from_np(X_hat, raw_img)

### 2019-11-24 1-illusion/prednet/predict_frames.py

@@ -13,7 +13,7 @@ from keras.layers import Input, Dense, Flatten
 from prednet import PredNet
 # from data_utils import SequenceGenerator
 
-from preprocess import *
+from img_process import *
 
 matplotlib.use('Agg')
 
@@ -69,24 +69,24 @@ def predict(test_model, X_test, nt, mode='fixed', initial=2, batch_size=10):
 
 
 # Compare MSE of PredNet predictions vs. using last frame.  Write results to prediction_scores.txt
-def mse_error(X_test, X_hat):
+def mse_error(X_test, X_hat, name=""):
     mse_model = np.mean((X_test[:, 1:] - X_hat[:, 1:]) ** 2)  # look at all timesteps except the first
     mse_prev = np.mean((X_test[:, :-1] - X_test[:, 1:]) ** 2)
     if not os.path.exists(RESULTS_SAVE_DIR):
         os.mkdir(RESULTS_SAVE_DIR)
-    f = open(RESULTS_SAVE_DIR + 'prediction_scores.txt', 'w')
+    f = open(RESULTS_SAVE_DIR + 'prediction_scores_' + name + '.txt', 'w')
     f.write("Model MSE: %f\n" % mse_model)
     f.write("Previous Frame MSE: %f" % mse_prev)
     f.close()
 
 
 # Plot some predictions
-def plot_pred(X_test, X_hat, nt=10, n_plot=100):
+def plot_pred(X_test, X_hat, nt=10, n_plot=100, name=""):
     aspect_ratio = float(X_hat.shape[2]) / X_hat.shape[3]
     plt.figure(figsize=(nt, 2 * aspect_ratio))
     gs = gridspec.GridSpec(2, nt)
     gs.update(wspace=0., hspace=0.)
-    plot_save_dir = os.path.join(RESULTS_SAVE_DIR, 'prediction_plots/')
+    plot_save_dir = os.path.join(RESULTS_SAVE_DIR, 'prediction_plots_' + name + '/')
     if not os.path.exists(plot_save_dir):
         os.mkdir(plot_save_dir)
     plot_idx = np.random.permutation(X_test.shape[0])[:n_plot]
@@ -112,17 +112,27 @@ def plot_pred(X_test, X_hat, nt=10, n_plot=100):
         plt.clf()
 
 
+def adjacent_frame_mse(X_hat):
+    n_frames = X_hat.shape[1]
+    mses = [np.mean((X_hat[:, i] - X_hat[:, i + 1]) ** 2) for i in range(1, n_frames - 1)]
[…]

### 2019-11-25 1-illusion/prednet/img_process.py
bugs fixed

@@ -73,24 +73,29 @@ def get_raw_images(IMG_DIR, size=(160, 128)):
     return raw
 
 
-def save_images_from_np(X_hat, raw_img):
+def save_images_from_np(X_hat, raw_img, outname):
+    if not os.path.exists('results/pred_'+outname):
+        os.mkdir('results/pred_'+outname)
     for j in range(X_hat.shape[0]):
         print('saving image ' + str(j) + '...')
         im = Image.fromarray((raw_img[j]*255).astype(np.uint8))
-        im.save('results/output/img' + str(j) + '-0.png')
+        im.save('results/pred_'+outname+'/img' + str(j) + '-0.png')
 
         frames = X_hat[j]
         for i in range(1, frames.shape[0]):
             im = Image.fromarray((frames[i]*255).astype(np.uint8))
-            im.save('results/output/img' + str(j) + '-' + str(i) + '.png')
+            im.save('results/pred_'+outname+'/img' + str(j) + '-' + str(i) + '.png')
             # plt.imshow(frames[i])
             # plt.axis('off')
             # plt.tight_layout()
             # plt.savefig('results/output/img' + str(j) + '-' + str(i) + '.png', bbox_inches='tight', pad_inches=0.0)
             # plt.show()
 
+def main():
+    X_hat = np.load('./results/pred_rotate0.npy')
+    raw_img = get_raw_images('test_data/static')
+    save_images_from_np(X_hat, raw_img, 'rotate0')
+
 
 if __name__ == '__main__':
-    X_hat = np.load('./results/pred_rotate.npy')
-    raw_img = get_raw_images('test_data/static')
-    save_images_from_np(X_hat, raw_img)
+    main()

### 2019-11-25 1-illusion/prednet/predict_frames.py

@@ -64,8 +64,17 @@ def predict(test_model, X_test, nt, mode='fixed', initial=2, batch_size=10):
         for i in range(initial, nt):
             print('Predicting the {}-th frame'.format(i + 1))
             X_hat = test_model.predict(new_test, batch_size)
+            new_test[:, i, :, :, :] = X_hat[:, i, :, :, :]
+        return new_test.transpose((0, 1, 3, 4, 2))
+    if mode == 'feedback2':  # wrong
+        new_test = X_test.transpose((0, 1, 4, 2, 3)).copy()
+        test_model.predict(new_test[:, :1], batch_size)
+        test_model.predict(new_test[:, :1], batch_size)
+        for i in range(initial, nt):
+            print('Predicting the {}-th frame'.format(i + 1))
+            X_hat = test_model.predict(new_test[:, i:i + 1], batch_size)
             new_test[:, i, :, :, :] = X_hat[:, -1, :, :, :]
-        return X_hat.transpose((0, 1, 3, 4, 2))
+        return new_test.transpose((0, 1, 3, 4, 2))
 
 
 # Compare MSE of PredNet predictions vs. using last frame.  Write results to prediction_scores.txt
@@ -123,17 +132,19 @@ def main():
     nt = 5
     # batch_size = 8
     test_model = init_model(nt)
-    X_test = get_static_test_data('test_data/control', nt)
-    X_hat = predict(test_model, X_test, nt, 'feedback', 2)
-    np.save('results/pred_control', X_hat)
+    X_test = get_static_test_data('test_data/static', nt)
+    X_hat = predict(test_model, X_test, 5, 'feedback', 3)
+    np.save('results/pred_rotate3', X_hat)
     print(X_hat.shape)
     print(X_test.shape)
 
     print(adjacent_frame_mse(X_hat))
 
-    mse_error(X_test, X_hat, name='control')
-    plot_pred(X_test, X_hat, nt, name='control')
+    # mse_error(X_test, X_hat, name='control')
+    # plot_pred(X_test, X_hat, nt, name='control')
 
+    raw_img = get_raw_images('test_data/static')
+    save_images_from_np(X_hat, raw_img, 'rotate3')
 
 if __name__ == '__main__':
     main()

### 2019-11-25 1-illusion/report/report.tex

\documentclass[journal]{IEEEtran}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{amsmath}
\usepackage{comment}
%\usepackage{cases}
%\usepackage{subeqnarray}
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{xcolor}
\usepackage{listings}
\lstset{
  basicstyle=\fontsize{9}{10}\selectfont\ttfamily,
  numbers=left,
  numberstyle= \tiny,
  keywordstyle= \color{ blue!70},
  commentstyle= \color{red!50!green!50!blue!50},
  frame=single,
  rulesepcolor= \color{ red!20!green!20!blue!20} ,
  escapeinside=``,
  xleftmargin=1.5em,xrightmargin=0em, aboveskip=1em,
  framexleftmargin=2em,
  showstringspaces=false,
  showtabs=false,
  breaklines=true
}
\lstdefinelanguage{Solidity}
{
  morekeywords={contract, mapping, address, uint, private, function, public, if, payable},
  morecomment=[l]{//},
  morestring=[b]"
}

\usepackage{multicol}
\usepackage{lipsum}
\usepackage{mathtools}
\usepackage{cuted}

\usepackage{amsmath}
\usepackage{extpfeil}
\usepackage{mathpartir}
\usepackage[mathscr]{eucal}

\usepackage{hyperref}
\usepackage{cleveref}

\crefformat{section}{\S#2#1#3} % see manual of cleveref, section 8.2.1
\crefformat{subsection}{\S#2#1#3}
\crefformat{subsubsection}{\S#2#1#3}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Motion Illusion Detection and Creation}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{
	Shangning~Xu,~\IEEEmembership{SJTU,}
	Jinyu~Li,~\IEEEmembership{SJTU,}
	Zhongye~Wang,~\IEEEmembership{SJTU,}
	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
	and Chenxuan~Li,~\IEEEmembership{SJTU}
}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
%
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peer review papers.
\begin{IEEEkeywords}
Motion Illusion, Deep Neural Network, Generative Adversary Network
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}
\label{sec:intro}
\IEEEPARstart{M}{otion} illusion is one type of optical illusion where people perceive motions from some static images.
Figure~\ref{fig:motion_example} shows some sample images with illusory motions.
\begin{figure}[h]
	\centering
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth]{fig/illusion_eg.jpg}
	\end{minipage}\hfill
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth]{fig/illusion_eg.jpg}
	\end{minipage}
	\caption{Motion Illusion Examples}
	\label[]{fig:motion_example}
\end{figure}

Rest of the introduction \dots

\section{Motion Illusion Detection: Prednet \& Flownet}
\label{sec:detection}
In this section, we will address the detection problem of motion illusion in static images.
We first explore and re-implement illusion reproduction strategy devised by Watanable \textit{et al.} \cite{watanable2018illusory} in \cref{sec:detection_dnn}, where they use a combination of Prednet \cite{lotter2016deep}, a deep neural network, and optical flow analysis to identify illusory motions.
Based on such strategy, we extract several metrics to evaluate the intensity of illusory motion of images in \cref{sec:detection_measure}.

We embed entire detector into a neural network by implementing the optical flow analysis using the Flownet \cite{ilg2017flownet}.
Therefore, we could easily get back-propagated feedback on how to improve the illusory image.
The integrated detector with Flownet (IDF) serves as a static discriminator in the illusion generative model we propose in \cref{sec:generation}.

\subsection{Detecting Motion Illusion by DNN \& Optic Flow Analysis}
\label{sec:detection_dnn}
Watanable \textit{et al.} \cite{watanable2018illusory} manage to reproduce the illusory motion human perceive from images.
The key idea in their strategy is to simulate the visual perception of human.
Unlike machines, human do not treat the visual input to their eyes as separated images, but instead as a consecutive sequence of image, i.e., a video.
When human observing the image with illusory motions, they tend to believe the image is part of the dynamic video they see through eyes.
In the meantime, the illusion information embedded in images relies on such belief that the image is not static and can produce motions.
Therefore, human can perceive these information, while the computer treat images as numerous static pixels and would neglect those information.

Guided by this intuition, they first use Prednet, a DNN model that predicts future frames in a video given first few frames, to simulate the process of human thinking images as videos.
They then apply the optical flow analysis to the generated video to extract the optical flow vector at some critical pixels.
These vectors can be interpreted as velocity vectors of the illusory motion.
Figure~\ref{fig:scheme} shows the scheme diagram for such reproduction strategy.

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{fig/pred-flow-procedure.png}
	\caption{Prednet-Flow Scheme for Illusion Reproduction}
	\label{fig:scheme}
\end{figure}

% $$
% \left[\begin{matrix}
% 	x_1 & y_1 & v_{x1} & v_{y1} \\
% 	x_2 & y_2 & v_{x2} & v_{y2} \\
% 	\vdots & \vdots & \vdots & \vdots \\
% 	x_n & y_n & v_{xn} & v_{yn} \\
% \end{matrix}\right]
% $$

\subsection{Measuring Illusion Intensity}
\label{sec:detection_measure}

\subsection{Integrated Detector with Flownet}
\label{sec:detection_idf}

\section{Motion Illusion Creation: Asymmetric GAN}
\label{sec:generation}

\subsection{Motion Illusion Generator}
\label{sec:generation_generator}

\subsection{Sanity Constraint Criteria}
\label{sec:generation_criteria}

\section{Experiments}
\label{sec:experiments}

\subsection{Illusion Detection}
\label{sec:experiments_detection}

\subsection{Illusion Generation}
\label{sec:experiments_generation}

\section{Related Work}
\label{sec:related}

\section{Conclusion}
\label{sec:conclusion}
The conclusion of the paper \dots

\bibliographystyle{IEEEtran}
\bibliography{ref}

\end{document}

### 2019-11-26 2-oracle/code/Dataset.py
include project report template and data load utils

@@ -1,0 +1,68 @@
+import os
+from PIL import Image
+
+import numpy as np
+from keras.utils import to_categorical
+
+# resize images to following size
+IMG_HEIGHT = 89
+IMG_WIDTH = 81
+
+
+class Dataset:
+    @staticmethod
+    def folder_to_cat(folder, num_cat=10):
+        assert num_cat in [10, 40], "Number of categories can only be 10 or 40"
+        return (int(folder) - 102) // (40 / num_cat)
+
+    @staticmethod
+    def get_image_file(fname):
+        img = Image.open(fname)
+        return np.array(img)
+
+    @staticmethod
+    def get_image_folder(folder, num_cat=10, one_hot=False):
+        path = '../dataset/' + folder + '/'
+        fnames = os.listdir(path)
+        cat = Dataset.folder_to_cat(folder, num_cat)
+        imgs = []
+        for fname in fnames:
+            img = Dataset.get_image_file(path + fname)
+            # print(img.shape)
+            imgs.append(img.resize((IMG_WIDTH, IMG_HEIGHT), Image.ANTIALIAS))
+        imgs = np.array(imgs)
+        cats = np.repeat(cat, imgs.shape[0])
+        if one_hot:
+            cats = to_categorical(cats, num_cat)
+        return imgs, cats
+
+    @staticmethod
+    def to_onehot(cats, num_cat=10):
+        return to_categorical(cats, num_cat)
+
+    @staticmethod
+    def load_data(num_cat=10, one_hot=False):
+        dirs = os.listdir('../dataset/')
+        X = []
+        y = []
+        for dir in dirs:
+            _X, _y = Dataset.get_image_folder(dir, num_cat)
+            # print(_X.shape)
+            X = np.concatenate([X, _X])
+            y = np.concatenate([y, _y])
+        if one_hot:
+            y = Dataset.to_onehot(y, num_cat)
+        return X, y
+
+
+if __name__ == '__main__':
+    X, y = Dataset.load_data()
+    print(X.shape)
+    print(y.shape)
+
+    # shapes = np.array([x.shape for x in X])
+    # print(np.unique(shapes[:, 0]))
+    # print(np.unique(shapes[:, 1]))
+    # [89 93 101]
+    # [81 91]
+    pass

### 2019-11-26 2-oracle/traditional/template_matching.py
naive template matching

@@ -1,0 +1,19 @@
+import cv2
+import numpy as np
+import matplotlib.pyplot as plt
+from utils import *
+
+
+templates = []
+groups = []
+for i in range(40):
+    g = get_group(i)
+    groups.append(g)
+    temp = get_template(g)
+    templates.append(temp)
+    # plt.imshow(temp,cmap='gray')
+    # plt.show()
+
+for i in range(40):
+    m = match(groups[i], templates)
+    print(i, np.mean(m == i))

### 2019-11-26 2-oracle/traditional/utils.py

@@ -1,0 +1,37 @@
+import cv2
+import numpy as np
+import matplotlib.pyplot as plt
+import os
+
+
+# label: [0,39]
+def get_group(label, size=(93, 81)):
+    DIR = "data/0" + str(102 + label)
+    group = np.zeros((len(os.listdir(DIR)), *size))
+    for i, filename in enumerate(os.listdir(DIR)):
+        path = os.path.join(DIR, filename)
+        img = cv2.imread(path, 0)
+        img.resize(size)
+        group[i] = img
+    return group
+
+
+def get_template(group):
+    return group.mean(axis=0)
+
+
+# mse error
+def score(group, template):
+    return np.array([1 / np.mean((group[i] - template) ** 2) for i in range(group.shape[0])])
+
+
+def match(dataset, templates):
+    scores = np.array([score(dataset, t) for t in templates])
+    return scores.argmax(axis=0)
+
+
+if __name__ == '__main__':
+    g = get_group(0)
+    t = get_template(g)
+    print(score(g,t).shape)
+    print(match(g,[t,t]).shape)

### 2019-11-26 2-oracle/code/Dataset.py
unify works of WZY and LJY in 2-oracle

@@ -10,11 +10,13 @@ IMG_WIDTH = 81
 
 
 class Dataset:
+    # convert the folder name into categories
     @staticmethod
     def folder_to_cat(folder, num_cat=10):
         assert num_cat in [10, 40], "Number of categories can only be 10 or 40"
         return (int(folder) - 102) // (40 / num_cat)
 
+    # read single image
     @staticmethod
     def get_image_file(fname):
         img = Image.open(fname)
@@ -22,14 +24,21 @@ class Dataset:
 
     @staticmethod
     def get_image_folder(folder, num_cat=10, one_hot=False):
+        """
+        get all resized images and their labels in one folder
+        :param folder: folder name
+        :param num_cat: number of categories, 10 or 40
+        :param one_hot: whether to use one hot encoding
+        :return: images, labels
+        """
         path = '../dataset/' + folder + '/'
         fnames = os.listdir(path)
         cat = Dataset.folder_to_cat(folder, num_cat)
         imgs = []
         for fname in fnames:
             img = Dataset.get_image_file(path + fname)
-            # print(img.shape)
-            imgs.append(img.resize((IMG_WIDTH, IMG_HEIGHT), Image.ANTIALIAS))
+            img.resize(IMG_WIDTH, IMG_HEIGHT, Image.ANTIALIAS)
+            imgs.append(img)
         imgs = np.array(imgs)
         cats = np.repeat(cat, imgs.shape[0])
         if one_hot:
@@ -42,12 +51,18 @@ class Dataset:
 
     @staticmethod
     def load_data(num_cat=10, one_hot=False):
+        """
+        load all images in dataset folder
+        :param num_cat: number of categories
+        :param one_hot: whether to use one hot encoding
+        :return: X: shape [N, IMG_HEIGHT, IMG_WIDTH],
+                 y: shape [N,] or [N, num_cat]
+        """
         dirs = os.listdir('../dataset/')
         X = []
         y = []
         for dir in dirs:
             _X, _y = Dataset.get_image_folder(dir, num_cat)
-            # print(_X.shape)
             X = np.concatenate([X, _X])
             y = np.concatenate([y, _y])
         if one_hot:

### 2019-11-26 2-oracle/code/template_matching.py

@@ -1,0 +1,33 @@
+import cv2
+import numpy as np
+import matplotlib.pyplot as plt
+from Dataset import Dataset
+
+
+def get_template(group):
+    return group.mean(axis=0)
+
+
+# mse error
+def score(group, template):
+    return np.array([1 / np.mean((group[i] - template) ** 2) for i in range(group.shape[0])])
+
+
+def match(dataset, templates):
+    scores = np.array([score(dataset, t) for t in templates])
+    return scores.argmax(axis=0)
+
+
+templates = []
+groups = []
+for i in range(40):
+    g, _ = Dataset.get_image_folder('0' + str(102 + i), 40)
+    groups.append(g)
+    temp = get_template(g)
+    templates.append(temp)
+    # plt.imshow(temp,cmap='gray')
+    # plt.show()
+
+for i in range(40):
+    m = match(groups[i], templates)
+    print(i, np.mean(m == i))

### 2019-11-26 2-oracle/code/traditional/template_matching.py

@@ -1,19 +1,0 @@
-import cv2
-import numpy as np
-import matplotlib.pyplot as plt
-from utils import *
-
-
-templates = []
-groups = []
-for i in range(40):
-    g = get_group(i)
-    groups.append(g)
-    temp = get_template(g)
-    templates.append(temp)
-    # plt.imshow(temp,cmap='gray')
-    # plt.show()
-
-for i in range(40):
-    m = match(groups[i], templates)
-    print(i, np.mean(m == i))

### 2019-11-26 2-oracle/code/traditional/utils.py

@@ -1,37 +1,0 @@
-import cv2
-import numpy as np
-import matplotlib.pyplot as plt
-import os
-
-
-# label: [0,39]
-def get_group(label, size=(93, 81)):
-    DIR = "data/0" + str(102 + label)
-    group = np.zeros((len(os.listdir(DIR)), *size))
-    for i, filename in enumerate(os.listdir(DIR)):
-        path = os.path.join(DIR, filename)
-        img = cv2.imread(path, 0)
-        img.resize(size)
-        group[i] = img
-    return group
-
-
-def get_template(group):
-    return group.mean(axis=0)
-
-
-# mse error
-def score(group, template):
-    return np.array([1 / np.mean((group[i] - template) ** 2) for i in range(group.shape[0])])
-
-
-def match(dataset, templates):
-    scores = np.array([score(dataset, t) for t in templates])
-    return scores.argmax(axis=0)
-
-
-if __name__ == '__main__':
-    g = get_group(0)
-    t = get_template(g)
-    print(score(g,t).shape)
-    print(match(g,[t,t]).shape)

### 2019-11-26 2-oracle/code/Dataset.py
bugfix for data loading

@@ -4,12 +4,20 @@ from PIL import Image
 import numpy as np
 from keras.utils import to_categorical
 
-# resize images to following size
-IMG_HEIGHT = 89
-IMG_WIDTH = 81
+# default resize images to following size
+# IMG_HEIGHT = 89
+# IMG_WIDTH = 81
+IMG_HEIGHT = 64
+IMG_WIDTH = 64
 
 
 class Dataset:
+    @staticmethod
+    def aug_filter(fname, keys=None):
+        if keys is not None:
+            return True
+        return True
+
     # convert the folder name into categories
     @staticmethod
     def folder_to_cat(folder, num_cat=10):
@@ -23,7 +31,7 @@ class Dataset:
         return np.array(img)
 
     @staticmethod
-    def get_image_folder(folder, num_cat=10, one_hot=False):
+    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None):
         """
         get all resized images and their labels in one folder
         :param folder: folder name
@@ -32,12 +40,12 @@ class Dataset:
         :return: images, labels
         """
         path = '../dataset/' + folder + '/'
-        fnames = os.listdir(path)
+        fnames = list(filter(lambda x: Dataset.aug_filter(x, filter_keys), os.listdir(path)))
         cat = Dataset.folder_to_cat(folder, num_cat)
         imgs = []
         for fname in fnames:
             img = Dataset.get_image_file(path + fname)
-            img.resize(IMG_WIDTH, IMG_HEIGHT, Image.ANTIALIAS)
+            img.resize(IMG_HEIGHT, IMG_WIDTH, Image.ANTIALIAS)
             imgs.append(img)
         imgs = np.array(imgs)
         cats = np.repeat(cat, imgs.shape[0])
@@ -50,7 +58,7 @@ class Dataset:
         return to_categorical(cats, num_cat)
 
     @staticmethod
-    def load_data(num_cat=10, one_hot=False):
+    def load_data(num_cat=10, one_hot=False, filter_keys=None):
         """
         load all images in dataset folder
         :param num_cat: number of categories
@@ -59,11 +67,14 @@ class Dataset:
                  y: shape [N,] or [N, num_cat]
         """
         dirs = os.listdir('../dataset/')
-        X = []
+        X = None
         y = []
         for dir in dirs:
-            _X, _y = Dataset.get_image_folder(dir, num_cat)
-            X = np.concatenate([X, _X])
[…]

### 2019-11-26 2-oracle/code/Dataset.py
implement framework for training oracle net

@@ -24,6 +24,10 @@ class Dataset:
         assert num_cat in [10, 40], "Number of categories can only be 10 or 40"
         return (int(folder) - 102) // (40 / num_cat)
 
+    @staticmethod
+    def cat40_to_cat10(cats):
+        return cats // 4
+
     # read single image
     @staticmethod
     def get_image_file(fname):

### 2019-11-26 2-oracle/code/OracleNet.py

@@ -1,0 +1,70 @@
+import numpy as np
+import tensorflow as tf
+import keras.layers as L
+
+from keras.models import Sequential
+from keras.optimizers import SGD
+from keras.callbacks import *
+
+from sklearn.model_selection import train_test_split
+
+from Dataset import Dataset
+from utils import *
+
+
+# training framework for oracle net
+class OracleNetTrainer(object):
+    def __init__(self, test_size=0.1, autosave_path='./tmp/weights.{val_loss:.2f}.hdf5', vis_on_batch=False):
+        """
+
+        :param test_size: ratio of test (validation) set
+        :param autosave_path: path to auto save training results
+        :param vis_on_batch: whether to record visualization on batch
+        """
+        # load original data
+        X, y = Dataset.load_data(one_hot=False, num_cat=40)
+        # normalize image to 0.0 - 1.0
+        X = X / 255
+        # covert to different categories
+        y40 = Dataset.to_onehot(y, 40)
+        y = Dataset.cat40_to_cat10(y)
+        y10 = Dataset.to_onehot(y, 10)
+        # train test split
+        idx = list(range(y40.shape[0]))
+        self.y_train = {}
+        self.y_val = {}
+        self.X_train, self.X_val, y_train_idx, y_val_idx = train_test_split(X, idx, test_size=test_size, shuffle=True)
+        self.y_train[40], self.y_val[40] = y40[y_train_idx], y40[y_val_idx]
+        self.y_train[10], self.y_val[10] = y10[y_train_idx], y10[y_val_idx]
+        # initialize callbacks
+        self.checkpointer = ModelCheckpoint(filepath=autosave_path, verbose=1, save_best_only=True)
+        self.visualizer = VisualizationCallback(vis_on_batch)
+
+    def train(self, model, num_cat=10, batch_size=32, epochs=50):
+        assert num_cat in [10, 40], "Number of categories can only be 10 or 40"
+        model.fit(self.X_train, self.y_train[num_cat], batch_size=batch_size, epochs=epochs,
+                  validation_data=(self.X_val, self.y_val[num_cat]),
+                  callbacks=[self.visualizer, self.checkpointer],
+                  # verbose set to 0 only when running in console
+                  verbose=0)
+
+
+def cat10_model_simple():
+    # build model structure
+    model = Sequential()
+    model.add(L.Flatten(input_shape=(64, 64, 1)))
[…]

### 2019-11-26 2-oracle/code/utils.py

@@ -1,0 +1,71 @@
+from keras.callbacks import *
+import matplotlib.pyplot as plt
+
+
+class VisualizationCallback(Callback):
+    def __init__(self, on_batch=False):
+        Callback.__init__(self)
+        self.on_batch = on_batch
+
+    def visualize(self):
+        plt.figure(figsize=[12, 4])
+
+        plt.subplot(1, 2, 1)
+        plt.title("losses")
+        plt.plot(self.loss_train, label='train loss')
+        plt.plot(self.loss_val, label='val loss')
+        plt.grid()
+        plt.legend()
+
+        plt.subplot(1, 2, 2)
+        plt.title("accuracy")
+        plt.plot(self.val_x, self.acc_train, label='train acc')
+        plt.plot(self.val_x, self.acc_val, label='val acc')
+        plt.grid()
+        plt.legend()
+        plt.show()
+
+    def on_train_begin(self, logs={}):
+        self.loss_train = []
+        self.acc_train = []
+        self.loss_val = []
+        self.acc_val = []
+        self.val_x = []
+
+    def on_batch_end(self, batch, logs={}):
+        if self.on_batch:
+            self.loss_val.append(logs['val_loss'])
+            self.acc_val.append(logs['val_acc'])
+            print("Batch {0}: Train acc: {1:.4f}, Train loss: {2:.4f}".format(
+                batch, logs['acc'], logs['loss']
+            ))
+
+    def on_epoch_end(self, epoch, logs={}):
+        self.loss_val.append(logs['val_loss'])
+        self.acc_val.append(logs['val_acc'])
+        if not self.on_batch:
+            self.loss_train.append(logs['loss'])
+            self.acc_train.append(logs['acc'])
+        self.val_x.append(len(self.acc_train)-1)
+        print("Epoch {0}: Train acc: {1:.4f}, Train loss: {2:.4f}, Val acc: {3:.4f}, Val loss: {4:.4f}".format(
+            epoch, logs['acc'], logs['loss'], logs['val_acc'], logs['val_loss']
+        ))
+
+    def on_train_end(self, logs={}):
+        plt.figure(figsize=[12, 4])
+
+        plt.subplot(1, 2, 1)
+        plt.title("losses")
+        plt.plot(self.loss_train, label='train loss')
+        plt.plot(self.loss_val, label='val loss')
+        plt.grid()
+        plt.legend()
+
+        plt.subplot(1, 2, 2)
[…]

### 2019-11-27 2-oracle/code/Dataset.py
fix load data to correctly resize images

@@ -1,8 +1,11 @@
 import os
 from PIL import Image
-
 import numpy as np
+import matplotlib.pyplot as plt
 from keras.utils import to_categorical
+
+import imgaug as ia
+import imgaug.augmenters as iaa
 
 # default resize images to following size
 # IMG_HEIGHT = 89
@@ -15,7 +18,9 @@ class Dataset:
     @staticmethod
     def aug_filter(fname, keys=None):
         if keys is not None:
-            return True
+            for key in keys:
+                if key in fname:
+                    return False
         return True
 
     # convert the folder name into categories
@@ -31,11 +36,12 @@ class Dataset:
     # read single image
     @staticmethod
     def get_image_file(fname):
+        # img = np.array(Image.open(fname))
         img = Image.open(fname)
-        return np.array(img)
+        return img #.reshape(img.shape + (1,))
 
     @staticmethod
-    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None):
+    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None, names=False):
         """
         get all resized images and their labels in one folder
         :param folder: folder name
@@ -49,8 +55,10 @@ class Dataset:
         imgs = []
         for fname in fnames:
             img = Dataset.get_image_file(path + fname)
-            img.resize(IMG_HEIGHT, IMG_WIDTH, Image.ANTIALIAS)
-            imgs.append(img)
+            img = img.resize((IMG_HEIGHT, IMG_WIDTH), Image.ANTIALIAS)
+            imgs.append(np.array(img))
+        if names:
+            return imgs, fnames
         imgs = np.array(imgs)
         cats = np.repeat(cat, imgs.shape[0])
         if one_hot:
@@ -85,10 +93,55 @@ class Dataset:
         return X, y
 
 
+class DataAugmentation(object):
+    def __init__(self):
+        self.flip_aug = iaa.Fliplr(1.0)
+        self.slight_affine_aug = iaa.Affine(
+            scale={'x': (0.95, 1.05), 'y': (0.95, 1.05)},
+            translate_px={'x': (-5, 5), 'y': (-5, 5)},
+            rotate=(-5, 5),
+            shear=(-3, 3),
+            mode='constant',
+            cval=(255, 255)
+        )
+
+    def flip(self, imgs):
+        return self.flip_aug(images=imgs)
+
[…]

### 2019-11-27 2-oracle/code/Dataset.py
data augmentation: double the amount of data

@@ -13,6 +13,7 @@ import imgaug.augmenters as iaa
 IMG_HEIGHT = 64
 IMG_WIDTH = 64
 
+ALL_KEYS = ('val', 'flipped', 'affine')
 
 class Dataset:
     @staticmethod
@@ -41,7 +42,7 @@ class Dataset:
         return img #.reshape(img.shape + (1,))
 
     @staticmethod
-    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None, names=False):
+    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None, inclusive=False, names=False):
         """
         get all resized images and their labels in one folder
         :param folder: folder name
@@ -50,7 +51,7 @@ class Dataset:
         :return: images, labels
         """
         path = '../dataset/' + folder + '/'
-        fnames = list(filter(lambda x: Dataset.aug_filter(x, filter_keys), os.listdir(path)))
+        fnames = list(filter(lambda x: Dataset.aug_filter(x, filter_keys)^inclusive, os.listdir(path)))
         cat = Dataset.folder_to_cat(folder, num_cat)
         imgs = []
         for fname in fnames:
@@ -70,7 +71,7 @@ class Dataset:
         return to_categorical(cats, num_cat)
 
     @staticmethod
-    def load_data(num_cat=10, one_hot=False, filter_keys=None):
+    def load_data(num_cat=10, one_hot=False, filter_keys=None, inclusive=False):
         """
         load all images in dataset folder
         :param num_cat: number of categories
@@ -82,7 +83,7 @@ class Dataset:
         X = None
         y = []
         for dir in dirs:
-            _X, _y = Dataset.get_image_folder(dir, num_cat, filter_keys)
+            _X, _y = Dataset.get_image_folder(folder=dir, num_cat=num_cat, filter_keys=filter_keys, inclusive=inclusive)
             if X is None:
                 X = _X
             else:
@@ -92,15 +93,36 @@ class Dataset:
             y = Dataset.to_onehot(y, num_cat)
         return X, y
 
+    @staticmethod
+    def clear_folder(folder, path='../dataset/', filter_keys=None):
+        """
+
+        :param folder:
+        :param path:
+        :param filter_keys: inclusive, remove files with keys
+        :return:
+        """
+        path = path + folder + '/'
[…]

### 2019-11-27 2-oracle/code/template_matching.py
add different match methods from cv2

@@ -9,25 +9,70 @@ def get_template(group):
 
 
 # mse error
-def score(group, template):
-    return np.array([1 / np.mean((group[i] - template) ** 2) for i in range(group.shape[0])])
+def score(group, template, method):
+    assert method in ['MSE', 'SQDIFF', 'SQDIFF_NORMED', 'CCORR', 'CCORR_NORMED', 'CCOEFF', 'CCOEFF_NORMED']
+
+    # custom implement
+    if method == 'MSE':
+        return np.array([np.mean((group[i] - template) ** 2) for i in range(group.shape[0])])
+        # return np.mean((group - template) ** 2, axis=(1, 2))
+
+    # use cv2.matchTemplate
+    else:
+        # move template around to get the best match
+        res = [cv2.matchTemplate(group[i], template.astype(np.uint8), eval('cv2.TM_' + method)) for i in
+               range(group.shape[0])]
+        minmax = np.array([cv2.minMaxLoc(res[i]) for i in range(group.shape[0])])
+        min_vals = minmax[:, 0]
+        max_vals = minmax[:, 1]
+        if method in ['SQDIFF', 'SQDIFF_NORMED']:
+            return min_vals
+        else:
+            return max_vals
 
 
-def match(dataset, templates):
-    scores = np.array([score(dataset, t) for t in templates])
-    return scores.argmax(axis=0)
+def match(dataset, templates, method):
+    scores = np.array([score(dataset, t, method) for t in templates])
+    if method in ['MSE', 'SQDIFF', 'SQDIFF_NORMED']:
+        return scores.argmin(axis=0)
+    else:
+        return scores.argmax(axis=0)
 
 
-templates = []
-groups = []
-for i in range(40):
-    g, _ = Dataset.get_image_folder('0' + str(102 + i), 40)
-    groups.append(g)
-    temp = get_template(g)
-    templates.append(temp)
-    # plt.imshow(temp,cmap='gray')
-    # plt.show()
+def main():
+    templates = []
+    groups = []
+    methods = ['MSE', 'SQDIFF', 'SQDIFF_NORMED', 'CCORR', 'CCORR_NORMED', 'CCOEFF', 'CCOEFF_NORMED']
+    for i in range(40):
+        g, _ = Dataset.get_image_folder('0' + str(102 + i), 40)
+        groups.append(g)
+        temp = get_template(g)
+        templates.append(temp)
+        # plt.imshow(temp,cmap='gray')
+        # plt.show()
 
-for i in range(40):
[…]

### 2019-11-27 2-oracle/code/Dataset.py
add load with padding. move global var inside class

@@ -1,5 +1,5 @@
 import os
-from PIL import Image
+from PIL import Image, ImageOps
 import numpy as np
 import matplotlib.pyplot as plt
 from keras.utils import to_categorical
@@ -7,14 +7,14 @@ from keras.utils import to_categorical
 import imgaug as ia
 import imgaug.augmenters as iaa
 
-# default resize images to following size
-# IMG_HEIGHT = 89
-# IMG_WIDTH = 81
-IMG_HEIGHT = 64
-IMG_WIDTH = 64
-
 
 class Dataset:
+    # default resize images to following size
+    # IMG_HEIGHT = 89
+    # IMG_WIDTH = 81
+    IMG_HEIGHT = 64
+    IMG_WIDTH = 64
+
     @staticmethod
     def aug_filter(fname, keys=None):
         if keys is not None:
@@ -38,15 +38,16 @@ class Dataset:
     def get_image_file(fname):
         # img = np.array(Image.open(fname))
         img = Image.open(fname)
-        return img #.reshape(img.shape + (1,))
+        return img  # .reshape(img.shape + (1,))
 
     @staticmethod
-    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None, names=False):
+    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None, names=False, padding=0):
         """
         get all resized images and their labels in one folder
         :param folder: folder name
         :param num_cat: number of categories, 10 or 40
         :param one_hot: whether to use one hot encoding
+        :param padding: add white padding around the image
         :return: images, labels
         """
         path = '../dataset/' + folder + '/'
@@ -55,7 +56,9 @@ class Dataset:
         imgs = []
         for fname in fnames:
             img = Dataset.get_image_file(path + fname)
-            img = img.resize((IMG_HEIGHT, IMG_WIDTH), Image.ANTIALIAS)
+            img = img.resize((Dataset.IMG_HEIGHT, Dataset.IMG_WIDTH), Image.ANTIALIAS)
+            if padding > 0:
+                img = ImageOps.expand(img, (padding, padding, padding, padding), 255)
             imgs.append(np.array(img))
         if names:
             return imgs, fnames

### 2019-11-27 2-oracle/code/template_matching.py
impove with scale change

@@ -2,27 +2,71 @@ import cv2
 import numpy as np
 import matplotlib.pyplot as plt
 from Dataset import Dataset
+from PIL import Image
+
+Dataset.IMG_HEIGHT = 89
+Dataset.IMG_WIDTH = 81
 
 
-def get_template(group):
-    return group.mean(axis=0)
+def get_best_scale(img):
+    # find the center of mass
+    accx = np.array([np.arange(img.shape[0])]).T
+    accy = np.arange(img.shape[1])
+    inv = 255 - img
+    suminv = np.sum(inv)
+    cx = int(round(np.sum(inv * accx) / suminv))
+    cy = int(round(np.sum(inv * accy) / suminv))
+    # print(cx,cy)
+
+    # find the smallest square that enclose 99% of mass
+    thres = 0.99
+    halfsize = 30
+    while 1:
+        tmp = inv[cx - halfsize:cx + halfsize + 1, cy - halfsize:cy + halfsize + 1]
+        if np.sum(tmp) > thres * suminv:
+            break
+        halfsize += 1
+
+    return img[cx - halfsize:cx + halfsize + 1, cy - halfsize:cy + halfsize + 1]
+
+
+def get_template(group, size=(80, 80)):
+    """
+    Generate template for one category.
+    :param group: a group of images with the same category
+    :param size: the size of the template
+    :return: template image
+    """
+    templ = np.zeros(size, np.float)
+    for i in range(group.shape[0]):
+        img = get_best_scale(group[i])
+        templ += cv2.resize(img, size)
+    # show template
+    # plt.imshow(templ / group.shape[0])
+    # plt.show()
+    return templ / group.shape[0]
 
 
 # mse error
 def score(group, template, method):
     assert method in ['MSE', 'SQDIFF', 'SQDIFF_NORMED', 'CCORR', 'CCORR_NORMED', 'CCOEFF', 'CCOEFF_NORMED']
 
+    # get best scale
+    new_group = np.zeros((group.shape[0],*template.shape),np.uint8)
+    for i in range(group.shape[0]):
+        new_group[i] = cv2.resize(get_best_scale(group[i]),template.shape)
+
     # custom implement
     if method == 'MSE':
-        return np.array([np.mean((group[i] - template) ** 2) for i in range(group.shape[0])])
+        return np.array([np.mean((new_group[i] - template) ** 2) for i in range(new_group.shape[0])])
[…]

### 2019-11-27 2-oracle/code/Dataset.py
fix some bugs

@@ -3,11 +3,13 @@ from PIL import Image, ImageOps
 import numpy as np
 import matplotlib.pyplot as plt
 from keras.utils import to_categorical
+from utils import *
 
 import imgaug as ia
 import imgaug.augmenters as iaa
 
 ALL_KEYS = ('val', 'flipped', 'affine')
+
 
 class Dataset:
     # default resize images to following size
@@ -52,7 +54,7 @@ class Dataset:
         :return: images, labels
         """
         path = '../dataset/' + folder + '/'
-        fnames = list(filter(lambda x: Dataset.aug_filter(x, filter_keys)^inclusive, os.listdir(path)))
+        fnames = list(filter(lambda x: Dataset.aug_filter(x, filter_keys) ^ inclusive, os.listdir(path)))
         cat = Dataset.folder_to_cat(folder, num_cat)
         imgs = []
         for fname in fnames:
@@ -74,7 +76,7 @@ class Dataset:
         return to_categorical(cats, num_cat)
 
     @staticmethod
-    def load_data(num_cat=10, one_hot=False, filter_keys=None, inclusive=False):
+    def load_data(num_cat=10, one_hot=False, filter_keys=None, inclusive=False, padding=0):
         """
         load all images in dataset folder
         :param num_cat: number of categories
@@ -86,7 +88,8 @@ class Dataset:
         X = None
         y = []
         for dir in dirs:
-            _X, _y = Dataset.get_image_folder(folder=dir, num_cat=num_cat, filter_keys=filter_keys, inclusive=inclusive)
+            _X, _y = Dataset.get_image_folder(folder=dir, num_cat=num_cat, filter_keys=filter_keys, inclusive=inclusive,
+                                              padding=padding)
             if X is None:
                 X = _X
             else:
@@ -111,7 +114,7 @@ class Dataset:
             os.remove(path + fname)
 
     @staticmethod
-    def clear_all(path = '../dataset/', filter_keys=None):
+    def clear_all(path='../dataset/', filter_keys=None):
         if filter_keys is None:
             filter_keys = set(ALL_KEYS) - {'val'}
         for folder in os.listdir(path):

### 2019-11-27 2-oracle/code/utils.py

@@ -34,10 +34,11 @@ def plot_confusion_matrix(y_true, y_pred, classes,
     im = ax.imshow(cm, interpolation='nearest', cmap=cmap)
     ax.figure.colorbar(im, ax=ax)
     # We want to show all ticks...
+    print(cm.shape)
     ax.set(xticks=np.arange(cm.shape[1]),
            yticks=np.arange(cm.shape[0]),
            # ... and label them with the respective list entries
-           xticklabels=classes, yticklabels=classes,
+           xticklabels=np.arange(classes), yticklabels=np.arange(classes),
            title=title,
            ylabel='True label',
            xlabel='Predicted label')
@@ -50,14 +51,15 @@ def plot_confusion_matrix(y_true, y_pred, classes,
     fmt = '.2f' if normalize else 'd'
     thresh = cm.max() / 2.
     for i in range(cm.shape[0]):
-        if num_cat == 40 and (i + 1) % 4 == 0:
-            plt.plot([i+0.5, i+0.5], [-0.5, 39.5], c='k', linewidth=2)
-            plt.plot([-0.5, 39.5], [i+0.5, i+0.5], c='k', linewidth=2)
+        if classes == 40 and (i + 1) % 4 == 0:
+            plt.plot([i + 0.5, i + 0.5], [-0.5, 39.5], c='k', linewidth=2)
+            plt.plot([-0.5, 39.5], [i + 0.5, i + 0.5], c='k', linewidth=2)
         for j in range(cm.shape[1]):
             ax.text(j, i, format(cm[i, j], fmt),
                     ha="center", va="center",
                     color="white" if cm[i, j] > thresh else "black")
     fig.tight_layout()
+    # plt.savefig(title, dpi=500)
     return ax
 
 
@@ -105,7 +107,7 @@ class VisualizationCallback(Callback):
         if not self.on_batch:
             self.loss_train.append(logs['loss'])
             self.acc_train.append(logs['acc'])
-        self.val_x.append(len(self.acc_train)-1)
+        self.val_x.append(len(self.acc_train) - 1)
         print("Epoch {0}: Train acc: {1:.4f}, Train loss: {2:.4f}, Val acc: {3:.4f}, Val loss: {4:.4f}".format(
             epoch, logs['acc'], logs['loss'], logs['val_acc'], logs['val_loss']
         ))

### 2019-11-27 2-oracle/code/template_matching.py
visualization

@@ -1,8 +1,10 @@
 import cv2
 import numpy as np
 import matplotlib.pyplot as plt
-from Dataset import Dataset
+from Dataset import Dataset, pipeline, ALL_KEYS
 from PIL import Image
+
+from utils import plot_confusion_matrix
 
 Dataset.IMG_HEIGHT = 89
 Dataset.IMG_WIDTH = 81
@@ -52,9 +54,9 @@ def score(group, template, method):
     assert method in ['MSE', 'SQDIFF', 'SQDIFF_NORMED', 'CCORR', 'CCORR_NORMED', 'CCOEFF', 'CCOEFF_NORMED']
 
     # get best scale
-    new_group = np.zeros((group.shape[0],*template.shape),np.uint8)
+    new_group = np.zeros((group.shape[0], *template.shape), np.uint8)
     for i in range(group.shape[0]):
-        new_group[i] = cv2.resize(get_best_scale(group[i]),template.shape)
+        new_group[i] = cv2.resize(get_best_scale(group[i]), template.shape)
 
     # custom implement
     if method == 'MSE':
@@ -87,11 +89,13 @@ def main():
     templates = []
     groups = []
     methods = ['MSE', 'SQDIFF', 'SQDIFF_NORMED', 'CCORR', 'CCORR_NORMED', 'CCOEFF', 'CCOEFF_NORMED']
+    # load original data
+    X_train, y_train = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=ALL_KEYS, inclusive=False, padding=40)
+    X_val, y_val = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val'], inclusive=True, padding=40)
+    print(y_train.shape, y_val.shape)
     for i in range(40):
-        g, _ = Dataset.get_image_folder('0' + str(102 + i), 40, padding=40)
-        groups.append(g)
-        temp = get_template(g)
-        templates.append(temp)
+        templ = get_template(X_train[y_train == i])
+        templates.append(templ)
         # plt.imshow(temp,cmap='gray')
         # plt.show()
 
@@ -101,19 +105,22 @@ def main():
         hits40 = []
         hits10 = []
         total = []
-        for i in range(40):
-            m = match(groups[i], templates, method)
-            hits40.append(np.sum(m == i))
-            hits10.append(np.sum(m // 4 == i // 4))
-            total.append(len(m))
-            print(i, np.mean(m == i))
 
[…]

### 2019-12-03 2-oracle/report/paper.tex
initialize paper organization

--- 2019-11-23 1-illusion/report.tex
@@
 
-\section{Subjective IQA}
+% wzy
+\section{Data Augmentation}
 
-\section{Objective IQA}
+\section{Character Recognition}
+% wzy
+\subsection{Convolutional Neural Network}
+% ljy
+\subsection{Template Matching}
+% ljy
+\subsection{Ensemble of Two Methods}
 
-\subsection{FR}
-
-\subsubsection{Spatial Method}
-Peak signal-to-noise ($PSNR$) is a classic objective full-reference $IQA$ metric and is commonly used to measure the fidelity of degraded images.
-$PSNR$ is most easily defined via mean square error ($MSE$).
-Given a $m \times n$ reference image $I$ and its distorted version $K$, the $MSE$ is defined as equation \ref{eq:PSNR 1}.
-\begin{equation}
-MSE = \frac{1}{mn} \sum\limits_{i=0}^{m-1} \sum\limits_{j=0}^{n-1} [I(i,j)-K(i,j)]^2
-\label{eq:PSNR 1}
-\end{equation}
-And the $PSNR$ (in $dB$) is defined as:
-\begin{equation}
-PSNR = 10\log_{10} (\frac{MAX_I^2}{MSE})
-\label{eq:PSNR 2}
-\end{equation}
-where $MAX_I^2$ is the maximum possible pixel value of the $I$ ($i.e.$ peak value).
-However, in some circumstances, the $PSNR$ is unequal to the perceptual quality prediction task because the human perception is depended on much more complicated factors.
-
-\subsubsection{Transformation-based Method}
-Sheikh \textit{et al.} \cite{ilg2017flownet} explored the image quality assessment problem from the perspective of information theory, and they utilized the widely investigated natural scene statistics ($NSS$) models to fit the quality score.
-Specifically, they adopted two different $NSS$ models to represent the reference image and distorted image.
-The reference image is expressed by Gaussian Scale Mixtures ($GSM$) in the wavelet domain, while the distorted image is expressed by a simple signal attenuation and additive Gaussian noise model in the wavelet domain.
-The final information fidelity criterion ($IFC$) is derived from the mutual information between the source and distorted images as equation \ref{eq:NSS 1}-\ref{eq:NSS 2}.
-\begin{equation}
-I(C^N; D^N | S^N) = \frac{1}{2} \sum\limits_{i=1}^{N}\log_2(1+\frac{g_i^2 s_i^2 \sigma_U^2}{\sigma_V^2})
-\label{eq:NSS 1}
-\end{equation}
-
-\begin{equation}
-IFC = \sum_{k \in subbands}I(C^{N_k,k};D^{N_k,k}|s^{N_k,k})
-\label{eq:NSS 2}
-\end{equation}
-where equation \ref{eq:NSS 1} is the derived for one subband, and the final $IFC$ is the sum over all subbands.
-
-\subsubsection{Learning-based Method}
-Narwaria \textit{et al.} \cite{lotter2016deep} developed the machine learning technique and proposed a novel objective $IQA$ metric in 2010.
-The contribution of this job is using singular value decomposition ($SVD$) as features for quantifying image structural information.
-And the support vector regression served as a feature fusion tool to generate the quality score.
-The authors also pointed that the advantages of machine learning technique in $IQA$ devising are that the combination of the features are optimal and the weighting coefficients are adjustable so as to obtain the most appropriate settings.
-
-\subsection{Saliency-Guided IQA}
-Human visual attention is the behavioral and cognitive process of selectively concentrating on the special region of the stimulus.
-Image quality is highly related with artifacts located at salient regions.
-Saliency-gudied IQA has been widely investigated recently.
-We divided the saliency-gudied IQA metrics into two categories, which are indirect pooling manner and direct fitting manner.
-The indirect pooling manner is utilizing human attention information as weighting map to emphasize salient regions so as to promote IQA metrics' performances, while the direct fitting manner aims to explore the relationship between human attention variation and image quality degradation so as to devise new IQA metrics.
-Moreover, the indirect pooling manner can be further classified as subjective ground truth-based pooling manner and objective saliency map-based pooling manner.
-
-\subsubsection{Indirect Pooling Manner}
-\paragraph{Subjective Ground Truth-based Pooling Manner}
-
-Although objective saliency prediction model has been widely investigated, there is still a gap between state-of-the-art saliency models and real human fixation data.
-Fortunately, relying on the development of eye-tracking equipment, eye-tracking data has been the most accurate and solid proxy for visual attention information.
-Eye-tracking data-guided pooling strategy has been explored in recent years for improving IQA metrics.
+\section{Experiments}
+\subsection{Test Set}
+\subsection{Results}
 
@@
 \bibliographystyle{IEEEtran}
-\bibliography{ref}
+\bibliography{Ref}
 
+% that's all folks
 \end{document}

### 2019-12-03 2-oracle/report/paper.tex
write data augmentation section

@@
 \usepackage{comment}
-%\usepackage{cases}
-%\usepackage{subeqnarray}
+\usepackage{booktabs}
+\usepackage{subfigure}
+\usepackage{xcolor}
+\usepackage{listings}
+\lstset{
+  basicstyle=\fontsize{9}{10}\selectfont\ttfamily,
+  numbers=left,
+  numberstyle= \tiny,
+  keywordstyle= \color{ blue!70},
+  commentstyle= \color{red!50!green!50!blue!50},
+  frame=single,
+  rulesepcolor= \color{ red!20!green!20!blue!20} ,
+  escapeinside=``,
+  xleftmargin=1.5em,xrightmargin=0em, aboveskip=1em,
+  framexleftmargin=2em,
+  showstringspaces=false,
+  showtabs=false,
+  breaklines=true
+}
+\lstdefinelanguage{Solidity}
+{
+  morekeywords={contract, mapping, address, uint, private, function, public, if, payable},
+  morecomment=[l]{//},
+  morestring=[b]"
+}
+
+\usepackage{multicol}
+\usepackage{lipsum}
+\usepackage{mathtools}
+\usepackage{cuted}
+
+\usepackage{amsmath}
+\usepackage{extpfeil}
+\usepackage{mathpartir}
+\usepackage[mathscr]{eucal}
+
+\usepackage{hyperref}
+\usepackage{cleveref}
+
+\crefformat{section}{\S#2#1#3} % see manual of cleveref, section 8.2.1
+\crefformat{subsection}{\S#2#1#3}
+\crefformat{subsubsection}{\S#2#1#3}
 
@@
 \section{Data Augmentation}
+The original dataset contains 40 micro categories of oracle bone characters, each with 85 samples.
+Therefore, we have $40 \times 85 = 3400$ samples in total.
+This is barely enough for training a convolutional neural network without overfitting, and we need to apply data augmentation to obtain larger dataset adequate for training.
+
+We first make the following observations.
+
+\paragraph{Observation 1} For each pair of characters in Figure~\ref{fig:sym-across}, we may consider them horizontally symmetric.
+Thus we can double the number of samples by flipping characters in one category horizontally to obtain those in another category.
+
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{0.2\linewidth}
+		\includegraphics[width=0.8\linewidth]{fig/observation-1-1.png}
+		\includegraphics[width=0.8\linewidth]{fig/observation-1-2.png}
+	\end{minipage}
+	% \hfill
+	\begin{minipage}{0.2\linewidth}
+		\includegraphics[width=0.8\linewidth]{fig/observation-1-3.png}
+		\includegraphics[width=0.8\linewidth]{fig/observation-1-4.png}
+	\end{minipage}
+	% \hfill
+	\begin{minipage}{0.2\linewidth}
+		\includegraphics[width=0.8\linewidth]{fig/observation-1-5.png}
+		\includegraphics[width=0.8\linewidth]{fig/observation-1-6.png}
+	\end{minipage}
+	\caption{Symmetric Samples Across Micro-Categories}
+	\label{fig:sym-across}
+\end{figure}
+
+\paragraph{Observation 2} For characters in Figure~\ref{fig:sym-in}, they are horizontally symmetric by themselves.
+We can flip them horizontally to double the number of samples in these categories.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.8\linewidth]{fig/observation-2.png}
+	\caption{Symmetric Samples in Micro-Categories}
+	\label{fig:sym-in}
+\end{figure}
+
+To balance the samples in different categories after applying above two methods of data augmentation, we need to also double the number of samples in the rest of categories.
+We choose to apply affine transforms to the remaining images.
+More specifically, we randomly scale images up/down by 0 to 10 percent, randomly translate the image horizontally/vertically by 0 to 10 pixels, randomly rotate and shear images by -10 to 10 degrees.
+The augmented images is with the same categories as the original ones.
+
+Then, we need to introduce more noises into the dataset to allow the model trained on it generalize well.
+We apply gaussian blur to original images, randomly strengthen/weaken the contrast in each images, randomly add some gaussian noise to each pixel or one channel of images, and randomly make some images brighter or darker by multiplying channels of images.
+
+Figure~\ref{fig:aug-example} shows an example of the affine augmentation and the noise augmentation.
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{0.2\linewidth}
+		\subfigure[Original]{
+			\includegraphics[width=\linewidth]{fig/person_0001.jpg}
+		}
+	\end{minipage}
+	\begin{minipage}{0.2\linewidth}
+		\subfigure[Affine]{
+			\includegraphics[width=\linewidth]{fig/person_0001_affine.jpg}
+		}
+	\end{minipage}
+	\begin{minipage}{0.2\linewidth}
+		\subfigure[Noise]{
+			\includegraphics[width=\linewidth]{fig/person_0001_noise.jpg}
+		}
+	\end{minipage}
+	\caption{An Example of Affine Augmentation and Noise Augmentation}
+	\label{fig:aug-example}
+\end{figure}
+
+When we actually apply the above augmentation methods to images, we first split the dataset into training set and validation set and only apply augment the samples in the training set to avoid data leakage.
+We select 10 images from each micro categories to form the validation set.
+Eventually, we end up tripling the size of the dataset with 9120 training samples and 400 validation samples.
 

### 2019-12-03 2-oracle/report/paper.tex
write network section

@@
 \usepackage{cleveref}
+
+\usepackage{CJK}
 
@@
 \section{Character Recognition}
+We use two different methods to address the character recognition task for oracle bone characters.
+We first learn a deep convolutional neural network to recognize characters, then use the template matching method for the same task.
+
 % wzy
 \subsection{Convolutional Neural Network}
+The deep neural network for learning the oracle bone characters has the structure in Figure~\ref{fig:network}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{fig/network.png}
+	\caption{Structure of the DNN}
+	\label{fig:network}
+\end{figure}
+
+The network first uses 2 convolutional layer with 16 filters, then apply max-pooling and batch normalization, then another 2 convolutional layer with 32 filters and pooling layer with normalization.
+Lastly, it uses one dense layer and an output layer.
+All trainable layers except the output layer uses ReLU activation and the output layer uses softmax activation.
+
+We use a simple stochastic gradient descent optimizer to train the network on the 9120 training samples and validate it on the remaining 400 samples.
+
+The network for 10 category classification achieves 98\% accuracy on the validation set at the save point, and the one for 40 category classification achieves 88.5\% accuracy on the validation set at the save point.
+Figure~\ref{fig:network-confusion} shows the confusion matrix for the validation results.
+
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{\linewidth}
+		\subfigure[Confusion Matrix for 10 Category Classification]{
+			\includegraphics[width=\linewidth]{fig/confusion_oraclenet_conv10.png}
+			\label{fig:network-confusion-10}
+		}
+	\end{minipage}
+	\begin{minipage}{\linewidth}
+		\hspace{-2em}
+		\subfigure[Confusion Matrix for 40 Category Classification]{
+			\includegraphics[width=1.15\linewidth]{fig/confusion_oraclenet_conv40.png}
+			\label{fig:network-confusion-40}
+		}
+	\end{minipage}
+	\caption{Validation Results}
+	\label{fig:network-confusion}
+\end{figure}
+
+In Figure~\ref{fig:network-confusion-10}, we can see the classification for 10 macro category is quite accurate, only 7 samples out of 400 is miss-classified.
+In Figure~\ref{fig:network-confusion-40}, we use solid lines to separate 10 macro categories among 40 micro categories.
+We can see the mistakes made between macro categories is very low and we can use this model for the macro classification task with 98\% accuracy as well.
+Most mistakes are made within the macro category.
+For example, it miss-classifies many samples for variants of the 3rd and 8th macro categories.
+
 % ljy

### 2019-12-04 2-oracle/code/template_matching.py
rewrite as class

@@ -5,149 +5,170 @@ from Dataset import Dataset, pipeline, ALL_KEYS
 from PIL import Image
 import pickle
 import os
+from scipy.special import softmax
 
 from utils import plot_confusion_matrix
 
-Dataset.IMG_HEIGHT = 89
-Dataset.IMG_WIDTH = 81
-
-PADDING = 40
-SCALE_THRESHOLD = 0.99
+Dataset.IMG_HEIGHT = 64
+Dataset.IMG_WIDTH = 64
 
 
-def get_best_scale(img):
-    # find the center of mass
-    accx = np.array([np.arange(img.shape[0])]).T
-    accy = np.arange(img.shape[1])
-    inv = 255 - img
-    suminv = np.sum(inv)
-    cx = int(round(np.sum(inv * accx) / suminv))
-    cy = int(round(np.sum(inv * accy) / suminv))
-    # print(cx,cy)
+# PADDING = 40
+# SCALE_THRESHOLD = 0.99
 
-    # find the smallest square that enclose 99% of mass
-    thres = SCALE_THRESHOLD
-    halfsize = 30
-    while 1:
-        tmp = inv[cx - halfsize:cx + halfsize + 1, cy - halfsize:cy + halfsize + 1]
-        if np.sum(tmp) > thres * suminv:
-            break
-        halfsize += 1
+class TemplateMatch:
+    def __init__(self, padding=40, scale_threshold=0.99, method='CCORR_NORMED'):
+        self.padding = padding
+        self.scale_threshold = scale_threshold
+        self.templates = []
+        self.method = method
 
-    return img[cx - halfsize:cx + halfsize + 1, cy - halfsize:cy + halfsize + 1]
+    def get_best_scale(self, img):
+        # add padding
+        img = cv2.copyMakeBorder(img, self.padding, self.padding, self.padding, self.padding,
+                                 cv2.BORDER_CONSTANT, None, 255)
 
+        # find the center of mass
+        accx = np.array([np.arange(img.shape[0])]).T
+        accy = np.arange(img.shape[1])
+        inv = 255 - img
+        suminv = np.sum(inv)
+        cx = int(round(np.sum(inv * accx) / suminv))
+        cy = int(round(np.sum(inv * accy) / suminv))
+        # print(cx,cy)
 
-def get_template(group, size=(80, 80)):
-    """
-    Generate template for one category.
-    :param group: a group of images with the same category
-    :param size: the size of the template
-    :return: template image
[…]

### 2019-12-04 2-oracle/code/OracleNet.py
reformat

@@ -16,10 +16,10 @@ from sklearn.model_selection import train_test_split
 from Dataset import Dataset
 from utils import *
 
-
 CLASS_NAMES = ["聨", "蚑", ""]
 
-# training framework for oracle net
+
+# training framework for oracle conv_net
 class OracleNetTrainer(object):
     def __init__(self, test_size=0.1, autosave_path='./tmp/weights.{val_loss:.2f}.hdf5', vis_on_batch=False):
         """

### 2019-12-06 2-oracle/report/paper.tex
write template matching section

@@
 \subsection{Template Matching}
+For the oracle bone character recognition task, we also try a traditional method, template matching, to solve it.
+
+The principle is simple.
+We construct a template for each character and measure the similarity of the sample and templates.
+The template that has the highest similarity is believed to be the character that sample represents.
+
+In order to construct a template, the intuition is to take all the samples of one category and take the average.
+However, we observe that the samples of the same character may have different size and position in the box.
+So the template generated by the above procedure may be blur and unrepresentative.
+Therefore, we preprocess the samples to find the best focus and scale.
+First find the center of mass of the box, which is analogous to the same term in physics.
+We denote the gray scale image as $G$.
+Consider the blackness as a measure of intensity, so we take the complement image of $G$, denoted as $\hat{G}$.
+i.e.
+$\hat{G}(i,j)=255-G(i,j)$.
+Then we can calculate the center of mass by the following formula:
+\begin{align*}
+	c_x=\frac{\sum_{i,j}\hat{G}(i,j)\cdot i}{\sum_{i,j} \hat{G}(i,j)}\\
+	c_y=\frac{\sum_{i,j}\hat{G}(i,j)\cdot j}{\sum_{i,j} \hat{G}(i,j)}
+\end{align*}
+
+To determine the scale, we first set a standard scale for all the templates, say $(M,N)$.
+Then we search the scaling coefficient $k$ for each sample such that the new box with size $(kM,kN)$ can enclose $\sigma$ of the mass of the original box, where $\sigma\in (0,1)$ is the scaling threshold.
+When we increase $k$ the new box may exceed the boundary of the original box, so we add padding of all zeros (which represents white in our complement image) to thoses areas.
+Then we resize the new box to the standard template size.
+We denote the transformed sample image as $G'$.
+Average over such new boxes of the samples and the get the templates.
+
+To measure the similarity of a sample and a template, we think of two metrics, normed mean square error and normed correlation, which is defined below:
+\begin{align*}
+	\text{NMSE}(G',T)= \frac{\sum_{x,y} (T(x,y)-G'(x,y))^2}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}\\
+	\text{NCOR}(G',T)= \frac{\sum_{x,y} (T(x,y) \cdot G'(x,y))}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}
+\end{align*}
+
+To compare this method with the above convolutional neural network, we do the same train-validation split.
+
 % ljy

### 2019-12-07 2-oracle/code/OracleNet.py
some update on network

@@ -74,6 +74,22 @@ class OracleNetTrainer(object):
             plot_confusion_matrix(self.y_val[num_cat].argmax(axis=1), y_pred, num_cat)
             print(y_pred)
 
+    def error_matrix(self, model_cat10, model_cat40):
+        y_pred_train = [model_cat10(self.X_train).argmax(axis=1),
+                        model_cat40(self.X_train).argmax(axis=1)]
+        y_pred_val = [model_cat10(self.X_val).argmax(axis=1),
+                      model_cat40(self.X_val).argmax(axis=1)]
+        mask_train = [(y_pred_train[0] == self.y_train[10]),
+                      (y_pred_train[1] == self.y_train[40])]
+        print(mask_train[0])
+        mask_val = [(y_pred_val[0] == self.y_val[10]),
+                    (y_pred_val[1] == self.y_val[40])]
+        matrix_train = [sum(mask_train[0] & mask_train[1]), sum(mask_train[0] & (~mask_train[1])),
+                        sum((~mask_train[0]) & mask_train[1]), sum((~mask_train[0]) & (~mask_train[1]))]
+        matrix_val = [sum(mask_val[0] & mask_val[1]), sum(mask_val[0] & (~mask_val[1])),
+                      sum((~mask_val[0]) & mask_val[1]), sum((~mask_val[0]) & (~mask_val[1]))]
+        return mask_train, mask_val
+
 
 def cat10_model_simple():
     # build model structure
@@ -107,16 +123,18 @@ def cat40_model_conv():
     # build model structure
     model = Sequential()
 
-    model.add(L.Conv2D(16, (3, 3), padding='same', activation='relu', input_shape=(64, 64, 1)))
-    model.add(L.Conv2D(16, (3, 3), padding='same', activation='relu'))
+    model.add(L.Conv2D(32, (3, 3), padding='same', activation='relu', input_shape=(64, 64, 1)))
+    model.add(L.Conv2D(32, (3, 3), padding='same', activation='relu'))
     model.add(L.MaxPooling2D())
+    model.add(L.BatchNormalization())
 
-    model.add(L.Conv2D(32, (3, 3), padding='same', activation='relu'))
-    model.add(L.Conv2D(32, (3, 3), padding='same', activation='relu'))
+    model.add(L.Conv2D(64, (3, 3), padding='same', activation='relu'))
+    model.add(L.Conv2D(64, (3, 3), padding='same', activation='relu'))
[…]

### 2019-12-07 2-oracle/code/utils.py

@@ -39,7 +39,7 @@ def plot_confusion_matrix(y_true, y_pred, classes,
            yticks=np.arange(cm.shape[0]),
            # ... and label them with the respective list entries
            xticklabels=np.arange(classes), yticklabels=np.arange(classes),
-           title=title,
+           # title=title,
            ylabel='True label',
            xlabel='Predicted label')
 

### 2019-12-08 2-oracle/code/Dataset.py
include code for test run

@@ -8,7 +8,7 @@ from utils import *
 import imgaug as ia
 import imgaug.augmenters as iaa
 
-ALL_KEYS = ('val', 'flipped', 'affine', 'noise')
+ALL_KEYS = ('val', 'flipped', 'affine', 'noise', 'test')
 
 
 class Dataset:
@@ -40,11 +40,11 @@ class Dataset:
     @staticmethod
     def get_image_file(fname):
         # img = np.array(Image.open(fname))
-        img = Image.open(fname)
+        img = Image.open(fname).convert('L')
         return img  # .reshape(img.shape + (1,))
 
     @staticmethod
-    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None, inclusive=False, names=False, padding=0):
+    def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None, inclusive=False, names=False, padding=0, normalize=False):
         """
         get all resized images and their labels in one folder
         :param folder: folder name
@@ -60,12 +60,17 @@ class Dataset:
         for fname in fnames:
             img = Dataset.get_image_file(path + fname)
             img = img.resize((Dataset.IMG_HEIGHT, Dataset.IMG_WIDTH), Image.ANTIALIAS)
+            if normalize:
+                img = np.array(img)
+                img = (img - img.min()) / (img.max() - img.min())
             if padding > 0:
                 img = ImageOps.expand(img, (padding, padding, padding, padding), 255)
             imgs.append(np.array(img))
         if names:
             return imgs, fnames
         imgs = np.array(imgs)
+        if len(imgs.shape) < 4:
+            imgs = imgs.reshape(imgs.shape + (1,))
         cats = np.repeat(cat, imgs.shape[0])
         if one_hot:
             cats = to_categorical(cats, num_cat)
@@ -76,7 +81,7 @@ class Dataset:
         return to_categorical(cats, num_cat)
 
     @staticmethod
-    def load_data(num_cat=10, one_hot=False, filter_keys=None, inclusive=False, padding=0):
+    def load_data(num_cat=10, one_hot=False, filter_keys=None, inclusive=False, padding=0, normalize=False):
         """
         load all images in dataset folder
         :param num_cat: number of categories
@@ -89,7 +94,7 @@ class Dataset:
         y = []
         for dir in dirs:
             _X, _y = Dataset.get_image_folder(folder=dir, num_cat=num_cat, filter_keys=filter_keys, inclusive=inclusive,
[…]

### 2019-12-08 2-oracle/code/OracleNet.py

@@ -29,10 +29,10 @@ class OracleNetTrainer(object):
         :param vis_on_batch: whether to record visualization on batch
         """
         # load original data
-        X_train, y_train = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val'])
+        X_train, y_train = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val', 'test'])
         X_val, y_val = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val'], inclusive=True)
-        X_train = X_train.reshape(X_train.shape + (1,))
-        X_val = X_val.reshape(X_val.shape + (1,))
+        X_train = X_train.reshape(X_train.shape)
+        X_val = X_val.reshape(X_val.shape)
         # X, y = Dataset.load_data(one_hot=False, num_cat=40)
         # normalize image to 0.0 - 1.0
         self.X_train = X_train / 255
@@ -73,6 +73,14 @@ class OracleNetTrainer(object):
             y_pred = model.predict(self.X_val).argmax(axis=1)
             plot_confusion_matrix(self.y_val[num_cat].argmax(axis=1), y_pred, num_cat)
             print(y_pred)
+
+    @staticmethod
+    def run_test(model, num_cat):
+        X_test, y_test = Dataset.load_data(num_cat=num_cat, one_hot=True, filter_keys=['test'], inclusive=True,
+                                           normalize=True)
+        print(model.evaluate(X_test, y_test))
+        y_pred = model.predict(X_test).argmax(axis=1)
+        plot_confusion_matrix(y_test.argmax(axis=1), y_pred, num_cat)
 
     def error_matrix(self, model_cat10, model_cat40):
         y_pred_train = [model_cat10(self.X_train).argmax(axis=1),
@@ -170,7 +178,7 @@ def cat10_model_conv():
 
 
 if __name__ == '__main__':
-    trainer = OracleNetTrainer()
+    # trainer = OracleNetTrainer()
 
     # model_cat10 = load_model('./model/weights_norm_cat10.hdf5')
     # model_cat40 = load_model('./model/weights_norm_cat40.hdf5')
@@ -183,11 +191,13 @@ if __name__ == '__main__':
     # trainer.train(model, num_cat=40, epochs=30)
 
     model = load_model('./model/weights_norm_cat40.hdf5')
-    trainer.evaluate(model, num_cat=40)
[…]

### 2019-12-08 2-oracle/code/OracleNet.py
implement ensemble for oraclenet

@@ -10,6 +10,7 @@ from keras.models import Sequential
 from keras.optimizers import SGD
 from keras.callbacks import *
 from keras.models import load_model
+from keras.models import Model
 
 from sklearn.model_selection import train_test_split
 
@@ -29,14 +30,12 @@ class OracleNetTrainer(object):
         :param vis_on_batch: whether to record visualization on batch
         """
         # load original data
-        X_train, y_train = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val', 'test'])
-        X_val, y_val = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val'], inclusive=True)
-        X_train = X_train.reshape(X_train.shape)
-        X_val = X_val.reshape(X_val.shape)
+        self.X_train, y_train = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val', 'test'], normalize=True)
+        self.X_val, y_val = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val'], inclusive=True, normalize=True)
+        # X_train = X_train.reshape(X_train.shape)
+        # X_val = X_val.reshape(X_val.shape)
         # X, y = Dataset.load_data(one_hot=False, num_cat=40)
         # normalize image to 0.0 - 1.0
-        self.X_train = X_train / 255
-        self.X_val = X_val / 255
         # covert to different categories
         # y40 = Dataset.to_onehot(y, 40)
         # y = Dataset.cat40_to_cat10(y)
@@ -78,6 +77,7 @@ class OracleNetTrainer(object):
     def run_test(model, num_cat):
         X_test, y_test = Dataset.load_data(num_cat=num_cat, one_hot=True, filter_keys=['test'], inclusive=True,
                                            normalize=True)
+        X_test[X_test < 0.5] = 0
         print(model.evaluate(X_test, y_test))
         y_pred = model.predict(X_test).argmax(axis=1)
         plot_confusion_matrix(y_test.argmax(axis=1), y_pred, num_cat)
@@ -129,21 +129,23 @@ def cat40_model_simple():
 
 def cat40_model_conv():
     # build model structure
-    model = Sequential()
+    model = Sequential(name='cat40')
 
[…]

### 2019-12-08 2-oracle/report/paper.tex
write some part for experiments

@@
 We use a simple stochastic gradient descent optimizer to train the network on the 9120 training samples and validate it on the remaining 400 samples.
+The data has been normalized into the range from 0 to 1.
 
@@
 \section{Experiments}
+Then we test the accuracy of our models under more realistic circumstances.
+
 \subsection{Test Set}
-\subsection{Results}
+We test models on our homebrew dataset where we write oracle bone characters using different pens, on different papers, and captured under different lighting condition.
+Figure~\ref{fig:testset} shows samples in the test set.
+We can see that the background color and character color varies dramatically from those of the original dataset.
+Moreover, there are other noises such as the texture of the paper that could disturb our models.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.19\linewidth]{fig/testset/test_bxy_2_30.jpg}
+	\includegraphics[width=0.19\linewidth]{fig/testset/test_lcx_1_40.jpg}
+	\includegraphics[width=0.19\linewidth]{fig/testset/test_ljy_2_28.jpg}
+	\includegraphics[width=0.19\linewidth]{fig/testset/test_wzy_1_30.jpg}
+	\includegraphics[width=0.19\linewidth]{fig/testset/test_xsn_2_28.jpg}
+	\caption{Samples in Test Set}
+	\label{fig:testset}
+\end{figure}
+
+There are 400 samples in the test set, 10 samples for each micro category.
+We only write 200 samples and double the size by capturing them under different lighting.
+
+\subsection{Evaluation and Improvements}
+To recognize characters in the test set, we need to first preprocess the samples.
+
+We first obtain the grey scale version of the images.
+For the test on the neural network, we normalize images as before and set pixels with values less than some threshold $\delta$ to 0.
+For the test on the template matching, we do not normalize images but set pixels with values less than some threshold $\Delta$ to 0.
+In this way, we can remove the influence of the background color on the recognition result.
+
+\begin{table}[h]
+	\centering
+	\caption{Accuracy for Different Models}
+	\label{tab:result}
+	\begin{tabular}{|c|c|c|}
+		\hline
+		& Cat10 & Cat40 \\\hline
+		DNN ($\delta=0.5$) & 0.8475 & 0.5275 \\\hline
+		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56 \\\hline
+		TM ($\Delta=?$) & ? & ? \\\hline
+		TM Ensemble ($\Delta=?$) & ? & ? \\\hline
+	\end{tabular}
+\end{table}
+
+Table~\ref{tab:result} shows the accuracy of different models wrt. the test set.
 

### 2019-12-08 2-oracle/code/OracleNet.py

@@ -214,16 +214,19 @@ if __name__ == '__main__':
     # model = cat40_model_conv()
     # trainer.train(model, num_cat=40, epochs=30)
 
-    # model = load_model('./model/weights_ensemble_cat40.hdf5')
-    # trainer.evaluate(model, num_cat=40)
-    # OracleNetTrainer.run_test(model, 40)
+    model = load_model('./model/weights_ensemble_cat40.hdf5')
+    OracleNetTrainer.run_test(model, 40)
     # plt.show()
 
-    # model = load_model('./model/weights_ensemble_cat10.hdf5')
-    # model = load_model('./model/weights_norm_cat10.hdf5')
-    # trainer.evaluate(model, num_cat=10)
+    model = load_model('./model/weights_ensemble_cat10.hdf5')
     OracleNetTrainer.run_test(model, 10)
-    plt.show()
+
+    model = load_model('./model/weights_norm_cat40.hdf5')
+    OracleNetTrainer.run_test(model, 40)
+
+    model = load_model('./model/weights_norm_cat10.hdf5')
+    OracleNetTrainer.run_test(model, 10)
+    # plt.show()
 
     # model = load_model('./model/weights_conv_cat40.hdf5')
     # trainer.evaluate(model, num_cat=40, confusion=False)

### 2019-12-08 2-oracle/report/fig/testset/resize.py

@@ -1,0 +1,10 @@
+import os
+from PIL import Image
+
+if __name__ == "__main__":
+  fnames = os.listdir()
+  for fname in fnames:
+      if fname == 'resize.py': continue
+      img = Image.open(fname)
+      img = img.resize((64, 64), Image.ANTIALIAS)
+      img.save(fname)

### 2019-12-10 2-oracle/code/template_matching.py
fix bugs and add filters

@@ -22,8 +22,13 @@ class TemplateMatch:
         self.scale_threshold = scale_threshold
         self.templates = []
         self.method = method
+        self.white_thres = 150
 
     def get_best_scale(self, img):
+        # set near white color to white
+        img[img > self.white_thres] = 255
+        # plt.hist(img.ravel())
+        # plt.show()
         # add padding
         img = cv2.copyMakeBorder(img, self.padding, self.padding, self.padding, self.padding,
                                  cv2.BORDER_CONSTANT, None, 255)
@@ -39,7 +44,7 @@ class TemplateMatch:
 
         # find the smallest square that enclose 99% of mass
         thres = self.scale_threshold
-        halfsize = 30
+        halfsize = 10
         while 1:
             tmp = inv[cx - halfsize:cx + halfsize + 1, cy - halfsize:cy + halfsize + 1]
             if np.sum(tmp) > thres * suminv:
@@ -138,9 +143,11 @@ class TemplateMatch:
         if method:
             self.method = method
 
-        X_val, y_val = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val'], inclusive=True)
+        X_val, y_val = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['test'], inclusive=True,
+                                         normalize=True)
+        X_val *= 255
 
-        m = self.match(X_val)
+        m = self.match(X_val.copy())
 
         print('method:', self.method)
         print('cat40', np.mean(m == y_val))
@@ -170,5 +177,5 @@ if __name__ == '__main__':
     # tm.train(40, 0.99, output_dir='./model/')
     tm.load_model('./model/templ.pkl')
 
-    for method in methods:
+    for method in ['CCORR_NORMED']:
         tm.evaluate(method)

### 2019-12-10 2-oracle/report/paper.tex
write introduction and related work part

@@
 \section{Introduction}
-\IEEEPARstart{T}{his}
+\IEEEPARstart{O}{racle} bone script is the earliest known Chinese writing, which dates back to the late 2nd millennium BC.
+Detection and recognition of oracle bone script is crucial for the understanding of the social and political characteristics of ancient Chinese.
+It is also significant in education and arts nowadays, as the script is a cultural heritage of both China and the human civilization.
+
+In this paper, we propose different methods to detect hand-written oracle bone script, which facilitates interactive applications.
+We try both the traditional template matching and the convolutional neural network.
+We also make an ensemble of the two methods to get a better performance.
+
+\section{Related Work}
+Though not been widely researched, Lin \cite{ssd} uses Single Shot Multibox Detector (SSD) to detect oracle bone inscription and receives considerable results.
 
@@
 \begin{align*}
-	c_x=\frac{\sum_{i,j}\hat{G}(i,j)\cdot i}{\sum_{i,j} \hat{G}(i,j)}\\
+	c_x=\frac{\sum_{i,j}\hat{G}(i,j)\cdot i}{\sum_{i,j} \hat{G}(i,j)} \\
 	c_y=\frac{\sum_{i,j}\hat{G}(i,j)\cdot j}{\sum_{i,j} \hat{G}(i,j)}
@@
 \begin{align*}
-	\text{NMSE}(G',T)= \frac{\sum_{x,y} (T(x,y)-G'(x,y))^2}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}\\
+	\text{NMSE}(G',T)= \frac{\sum_{x,y} (T(x,y)-G'(x,y))^2}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}} \\
 	\text{NCOR}(G',T)= \frac{\sum_{x,y} (T(x,y) \cdot G'(x,y))}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}
@@
 \subsection{Ensemble of Two Methods}
+To improve the performance of the model, we add an ensemble network for CNN and template matching.
+It takes the output of CNN and template matching as input, and through a linear regression, produces the score of each class.
 
@@
 For the test on the neural network, we normalize images as before and set pixels with values less than some threshold $\delta$ to 0.
-For the test on the template matching, we do not normalize images but set pixels with values less than some threshold $\Delta$ to 0.
+For the test on the template matching, besides the normalization, we also set pixels with values less than some threshold $\Delta$ to 0.
 In this way, we can remove the influence of the background color on the recognition result.
@@
 		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56   \\\hline
-		TM ($\Delta=?$) & ? & ? \\\hline
+		TM ($\Delta=150$, NMSE)     & 0.7775 & 0.6325 \\\hline
+		TM ($\Delta=150$, NCCOR)    & 0.8000 & 0.6500 \\\hline
 		TM Ensemble ($\Delta=?$)    & ?      & ?      \\\hline

### 2019-12-10 2-oracle/code/template_matching.py
ensemble update

@@ -116,7 +116,7 @@ class TemplateMatch:
         self.scale_threshold = scale_thres
         self.templates = []
 
-        X_train, y_train = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=ALL_KEYS, inclusive=False)
+        X_train, y_train = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['test'], normalize=False)
 
         for i in range(40):
             templ = self.get_template(X_train[y_train == i])
@@ -164,8 +164,8 @@ class TemplateMatch:
         :param X: nparray m*h*w
         :return: softmax score of each category
         '''
-        if X.ndim == 4:
-            X = X[:, :, :, 0]
+        # if X.ndim == 4:
+        #     X = X[:, :, :, 0]
         scores = np.array([self.score(X, t) for t in self.templates])
         return softmax(scores.T, axis=1)
 
@@ -177,5 +177,5 @@ if __name__ == '__main__':
     # tm.train(40, 0.99, output_dir='./model/')
     tm.load_model('./model/templ.pkl')
 
-    for method in ['CCORR_NORMED']:
+    for method in ['MSE_NORMED', 'CCORR_NORMED']:
         tm.evaluate(method)

### 2019-12-10 2-oracle/report/paper.tex
experiment data update

@@
 \subsection{Ensemble of Two Methods}
-To improve the performance of the model, we add an ensemble network for CNN and template matching.
-It takes the output of CNN and template matching as input, and through a linear regression, produces the score of each class.
+To improve the performance of the model, we add an ensemble network for CNN. (UNFINISHED)
 
@@
 		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56   \\\hline
-		TM ($\Delta=150$, NMSE)     & 0.7775 & 0.6325 \\\hline
-		TM ($\Delta=150$, NCCOR)    & 0.8000 & 0.6500 \\\hline
+		TM ($\Delta=150$, NMSE)     & 0.7575 & 0.6125 \\\hline
+		TM ($\Delta=150$, NCCOR)    & 0.8475 & 0.7000 \\\hline
 		TM Ensemble ($\Delta=?$)    & ?      & ?      \\\hline

### 2019-12-10 3-UHD/code/faker.m
initialize project UHD

@@ -1,0 +1,47 @@
+mkdir('images//1080P//bilinear//');
+mkdir('images//1080P//bicubic//');
+mkdir('images//1080P//lanczos2//');
+mkdir('images//720P//bilinear//');
+mkdir('images//720P//bicubic//');
+mkdir('images//720P//lanczos2//');
+for i=1:200
+    ['Current progress: ', num2str(i), ' / 200']
+    str = ['images//4K//',num2str(i),'.bmp'];
+    I = imread(str);
+    %降采样
+    R = I(:,:,1);
+    G = I(:,:,2);
+    B = I(:,:,3);
+    R1=R(1:2:end,1:2:end);%每2位采集1位  1080p
+    G1=G(1:2:end,1:2:end);
+    B1=B(1:2:end,1:2:end);
+    I1(:,:,1)=R1;
+    I1(:,:,2)=G1;
+    I1(:,:,3)=B1;
+    R2=R(1:3:end,1:3:end);
+    G2=G(1:3:end,1:3:end);
+    B2=B(1:3:end,1:3:end);%每3位采集1位 720p
+    I2(:,:,1)=R2;
+    I2(:,:,2)=G2;
+    I2(:,:,3)=B2;
+    
+    J1 = imresize(I1,[2160,3840], 'bilinear'); %双线性插值
+    str1 = ['images//1080P//bilinear//',num2str(i),'.bmp'];
+    imwrite(J1, str1);
+    K1 = imresize(I1,[2160,3840], 'bicubic');  %双三次插值
+    str2 = ['images//1080P//bicubic//',num2str(i),'.bmp'];
+    imwrite(K1, str2);
+    L1 = imresize(I1,[2160,3840], 'lanczos2'); %Lanczos-2核
+    str3 = ['images//1080P//lanczos2//',num2str(i),'.bmp'];
+    imwrite(L1, str3);
+    
+    J2 = imresize(I2,[2160,3840], 'bilinear'); %双线性插值
+    str4 = ['images//720P//bilinear//',num2str(i),'.bmp']; 
+    imwrite(J2, str4);
+    K2 = imresize(I2,[2160,3840], 'bicubic');  %双三次插值
+    str5 = ['images//720P//bicubic//',num2str(i),'.bmp'];
+    imwrite(K2, str5);
+    L2 = imresize(I2,[2160,3840], 'lanczos2'); %Lanczos-2核
+    str6 = ['images//720P//lanczos2//',num2str(i),'.bmp']; 
+    imwrite(L2, str6);
+end

### 2019-12-11 2-oracle/report/paper.tex
enrich related work and add some reference

@@
 \section{Related Work}
-Though not been widely researched, Lin \cite{ssd} uses Single Shot Multibox Detector (SSD) to detect oracle bone inscription and receives considerable results.
+For years researchers have tried traditional image processing methods on oracle bone script, like template matching \cite{tm}.
+Meng et al.
+\cite{tm1} improves this method by devising a two-stage method.
+They extract line points using Hough transform and generate templates in that space.
+
+Currently, Deep learning is widely used in the field of object detection and classification with exciting accuracy.
+Meng et al.
+\cite{conv} use AlexNet on their own generated dataset of oracle bone inscription and achieved considerable results.
+Since in that research, they need to first segment each character before doing the classification, they later proposed a method \cite{ssd} to use Single Shot Multibox Detector (SSD) on oracle bone inscription.
 

### 2019-12-13 2-oracle/report/paper.tex
include ensemble in network model

@@
 
+It is possible to improve the performance of DNN method by building an ensemble of the Cat10 network model and Cat40 network model so that we can cancel some errors in one network with the support of another.
+We use the outputs from two networks as the inputs to another dense layer to further classify samples based on the first stage results.
+We train the extra dense layer still using the train samples.
+However, the performance of the ensemble models does not improve wrt. the original DNN.
+
 % ljy
@@
 
-% ljy
-\subsection{Ensemble of Two Methods}
-To improve the performance of the model, we add an ensemble network for CNN. (UNFINISHED)
-
 \section{Experiments}
@@
 		                            & Cat10  & Cat40  \\\hline
-		DNN ($\delta=0.5$)          & 0.8475 & 0.5275 \\\hline
+		DNN ($\delta=0.5$)          & \textbf{0.8475} & 0.5275 \\\hline
 		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56   \\\hline
 		TM ($\Delta=150$, NMSE)     & 0.7575 & 0.6125 \\\hline
-		TM ($\Delta=150$, NCCOR)    & 0.8475 & 0.7000 \\\hline
-		TM Ensemble ($\Delta=?$)    & ?      & ?      \\\hline
+		TM ($\Delta=150$, NCCOR)    & \textbf{0.8475} & \textbf{0.7000} \\\hline
 	\end{tabular}
@@
 Table~\ref{tab:result} shows the accuracy of different models wrt. the test set.
+It turns out that the DNN is no better than template matching in the case of micro category classification due to its sensitiveness to noises.
 

### 2019-12-13 3-UHD/code/DCT_Judger.py
update DCT exploration

@@ -1,0 +1,37 @@
+import cv2
+import numpy as np
+import matplotlib.pyplot as plt
+from utils import *
+
+
+def tile_dct(img, i, j, tile, channel=0):
+    if len(img.shape) < 3:
+        return cv2.dct(np.float32(img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile]))
+    elif len(img.shape) < 4:
+        if img.shape[2] <= 3:
+            return cv2.dct(np.float32(img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile, channel]))
+        else:
+            return cv2.dct(np.float32(img[:, i * tile:(i + 1) * tile, j * tile:(j + 1) * tile]))
+    else:
+        return cv2.dct(np.float32(img[:, i * tile:(i + 1) * tile, j * tile:(j + 1) * tile, channel]))
+
+
+def dct_hist_union(img, tile, channel=0):
+    nx = img.shape[0] // tile
+    ny = img.shape[1] // tile
+    dcts = np.array([])
+    for i in range(nx):
+        for j in range(ny):
+            dcts = np.concatenate([dcts, tile_dct(img, i, j, tile, channel).flatten()])
+    hst = plt.hist(dcts)[0]
+
+
+if __name__ == '__main__':
+    plt.figure()
+    img_4k = get_image("./images/4k/1.bmp")
+    dct_hist_union(img_4k, 32)
+    plt.figure()
+    img_18bc = get_image("./images/1080P/bicubic/1.bmp")
+    dct_hist_union(img_18bc, 32)
+    plt.show()
+    pass

### 2019-12-13 3-UHD/code/utils.py

@@ -1,0 +1,58 @@
+import os
+import cv2
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+def get_image(fname):
+    return cv2.imread(fname)
+
+
+def get_folder(folder="./images/4k/", callback=None, num_img=None):
+    fnames = [e for e in os.listdir(folder) if e.split('.')[-1] in ('bmp', 'jpg', 'png')]
+    imgs = []
+    for i, fname in enumerate(fnames):
+        if num_img is not None and i >= num_img:
+            break
+        if callback is not None:
+            callback()
+        print('{} / {}'.format(i, len(fnames)))
+        img = get_image(folder + fname)
+        imgs.append(img)
+    return np.array(imgs)
+
+
+def down_sample(img, rate=2, sx=0, sy=0):
+    if len(img.shape) < 3:
+        return img[sx::rate, sy::rate]
+    else:
+        return img[sx::rate, sy::rate, :]
+
+
+def vis_hist(img, thresholds=(100, 1000, 10000), level=None):
+    tmp = img.flatten()
+
+    if thresholds is None:
+        plt.hist(tmp, bins=100)
+    else:
+        num_plots = len(thresholds) + 1
+
+        plt.figure(figsize=[12, 4 * ((num_plots + 1) // 2)])
+
+        for idx in range(num_plots):
+            if level == idx:
+                break
+            plt.subplot((num_plots + 1) // 2, 2, idx + 1)
+            if idx == 0:
+                plt.hist(tmp[abs(tmp) < thresholds[0]], bins=100)
+            elif idx == num_plots - 1:
+                plt.hist(tmp[abs(tmp) >= thresholds[idx - 1]], bins=100)
+            else:
+                plt.hist(tmp[(abs(tmp) >= thresholds[idx - 1]) & (abs(tmp) < thresholds[idx])], bins=100)
+
+    plt.show()
+
+
+if __name__ == '__main__':
+    imgs = get_folder()
+    print(imgs.shape)

### 2019-12-14 2-oracle/report/paper.tex
write conclusion

@@
 \section{Introduction}
-\IEEEPARstart{O}{racle} bone script is the earliest known Chinese writing, which dates back to the late 2nd millennium BC.
-Detection and recognition of oracle bone script is crucial for the understanding of the social and political characteristics of ancient Chinese.
-It is also significant in education and arts nowadays, as the script is a cultural heritage of both China and the human civilization.
+\IEEEPARstart{O}{racle} bone inscription (OBI) is the earliest known Chinese writing, which dates back to the late 2nd millennium BC.
+Detection and recognition of oracle bone inscription is crucial for the understanding of the social and political characteristics of ancient Chinese.
+It is also significant in education and arts nowadays, as OBI is a cultural heritage of both China and the human civilization.
 
@@
 \section{Related Work}
-For years researchers have tried traditional image processing methods on oracle bone script, like template matching \cite{tm}.
+For years researchers have tried traditional image processing methods on oracle bone inscription, like template matching \cite{tm}.
 Meng et al.
@@
 Meng et al.
-\cite{conv} use AlexNet on their own generated dataset of oracle bone inscription and achieved considerable results.
-Since in that research, they need to first segment each character before doing the classification, they later proposed a method \cite{ssd} to use Single Shot Multibox Detector (SSD) on oracle bone inscription.
+\cite{conv} use AlexNet on their own generated dataset of OBI and achieved considerable results.
+Since in that research, they need to first segment each character before doing the classification, they later proposed a method \cite{ssd} to use Single Shot Multibox Detector (SSD) on OBI.
 
@@
 \section{Conclusion}
-The conclusion goes here.
+This paper focuses on detection of hand-written oracle bone script.
+We first manually generate a small dataset and use data augmentation, like affine transform and noise augmentation, to get more data.
+Then we try light-weight models like template matching and low-depth convolutional neural network.
+We improve the two methods with scale transformation and ensemble network respectively.
+The experiment shows that the two methods achieve similar performance, probably because the lack of data impairs CNN's generalization ability.
 

### 2019-12-14 3-UHD/report/bare_jrnl.tex
write subsampling and interpolation

\documentclass[journal]{IEEEtran}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{graphicx} 
\usepackage{subfigure}
%\usepackage{cases}
%\usepackage{subeqnarray}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Bare Demo of IEEEtran.cls for Journals}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
        John~Doe,~\IEEEmembership{Fellow,~OSA,}
        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\thanks{M. Shell is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~13, No.~9, September~2014}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
%
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}
\IEEEPARstart{T}{his}

\section{Related Work}
% lcx
\section{Subsampling and Interpolation}

\subsection{Subsampling}
Resampling using pixel area relation. Suppose $x\times y$ image subsampled down to size $x'\times y'$. scale\_x = x/x', scale\_y = y/y', and then we get block $scale\_x \times scale\_y$, block\_area = $scale\_x \times scale\_y$, the new image's each pixel is the weighted average of pixels in corresponding block's of the original image: 
\begin{align*}
	p'(x',y')=\sum_{i,j}{\frac{covered\_area \cdot p(i,j)}{block\_area}}
\end{align*}
i,j are nonnegative integers, $i \in [scale\_x\times x,scale\_x\times (x+1)]$ $j \in [scale\_y\times y,scale\_y\times (y+1)]$

\subsection{Interpolation}
In the mathematical field of numerical analysis, interpolation is a type of estimation, a method of constructing new data points within the range of a discrete set of known data points. In this project we use bilinear interpolation, bicubic interpolation, Lanczos resampling.

\subsubsection{Bilinear Interpolation}
~\\
\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\linewidth]{fig/1.png}
	\label{fig:Bilinear Interpolation}
\end{figure}
\par First do linear interpolation in the x-direction:
\begin{align*}
p(R_1) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{11})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{21})\\
p(R_2) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{12})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{22})
\end{align*}
Then interpolate in the y-direction:
\begin{align*}
p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}}{\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}{\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}}
\end{align*}
\par We can get the corresponding pixel's coordinate in original image: $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_1=int(x),x_2=int(x)+1,y_1=int(y), y_2=int(y)+1$, do interpolation.
\par This algorithm reduces some of the visual distortion caused by resizing an image to a non-integral zoom factor.
~\\
\subsubsection{Bicubic Interpolation}
~\\
\par In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image. An interpolator can be obtained by applying a convolution with the following kernel in both dimensions:
\begin{align*}
{\displaystyle W(x)={\begin{cases}(a+2)|x|^{3}-(a+3)|x|^{2}+1&{\text{for }}|x|\leq 1,\\a|x|^{3}-5a|x|^{2}+8a|x|-4a&{\text{for }}1<|x|<2,\\0&{\text{otherwise}},\end{cases}}}
\end{align*}
where a is usually set to −0.5 or −0.75.
\par $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_i$=int(x+i), $y_j$=int(y+j), i, j = -1,0,1,2:

do interpolation in the x-direction:
\begin{align*}
p(x',y_j)=\sum_{i}{W(x-x_i)\cdot p(x_i,y_j)}
\end{align*}
then do interpolation in the y-direction:
\begin{align*}
p(x',y')=\sum_{j}{W(y-y_j)\cdot p(x',y_j)} 
\end{align*}
\par Images resampled with bicubic interpolation are smoother and have fewer interpolation artifacts.
~\\
\subsubsection{Lanczos Resampling}
~\\
\par The effect of each input sample on the interpolated values is defined by the filter's reconstruction kernel L(x), called the Lanczos kernel. 
\begin{align*}
{\displaystyle L(x)={\begin{cases}\operatorname {sinc} (x)\,\operatorname {sinc} (x/a)&{\text{if}}\ -a<x<a,\\0&{\text{otherwise}}.\end{cases}}}
\end{align*}
Equivalently,
\begin{align*}
{\displaystyle L(x)={\begin{cases}1&{\text{if}}\ x=0,\\{\dfrac {a\sin(\pi x)\sin(\pi x/a)}{\pi ^{2}x^{2}}}&{\text{if}}\ -a\leq x<a\ {\text{and}}\ x\neq 0,\\0&{\text{otherwise}}.\end{cases}}}
\end{align*}
\par The parameter $a$ is a positive integer, typically 2 or 3 (but in opencv, the method is cv2.INTER$\_$LANCZOS4, $a$=4), which determines the size of the kernel. The Lanczos kernel has $2a-1$ labes:a positive one at the center, and $a-1$ alternating negative and positive lobes on each side.
\begin{align*}
L(x,y) &= L(x) \cdot L(y)\\
p(x',y') &= \sum_{i,j}{L(x_i-x)\cdot L(y_j-y)\cdot p(x_i,y_j)}
\end{align*}
$x_i=int(x+i)$, $y_j=int(y+j)$, $-a+1\leq i, j \leq a-1$

\section{Conclusion}
The conclusion goes here.

\bibliographystyle{IEEEtran}
\bibliography{Ref}

% that's all folks
\end{document}

### 2019-12-14 3-UHD/code/DCT_Judger.py
implement DCT feature extractor

@@ -2,36 +2,137 @@ import cv2
 import numpy as np
 import matplotlib.pyplot as plt
 from utils import *
+import sys
 
 
-def tile_dct(img, i, j, tile, channel=0):
+def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True):
+    img = np.float32(img)
     if len(img.shape) < 3:
-        return cv2.dct(np.float32(img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile]))
-    elif len(img.shape) < 4:
-        if img.shape[2] <= 3:
-            return cv2.dct(np.float32(img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile, channel]))
-        else:
-            return cv2.dct(np.float32(img[:, i * tile:(i + 1) * tile, j * tile:(j + 1) * tile]))
+        img_tile = img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile]
     else:
-        return cv2.dct(np.float32(img[:, i * tile:(i + 1) * tile, j * tile:(j + 1) * tile, channel]))
+        img_tile = img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile, channel]
+    img_ref = cv2.resize(down_sample(img_tile, rate), dsize=img_tile.shape, interpolation=cv2.INTER_AREA)
+    if divide_ref:
+        tmp = cv2.dct(img_tile) / cv2.dct(img_ref)
+    else:
+        tmp = (cv2.dct(img_tile), cv2.dct(img_ref))
+    return tmp
 
 
-def dct_hist_union(img, tile, channel=0):
+def self_ref_dct_complete(img, tile, channel=0, rate=2, threshold=20):
+    if len(img.shape) > 3:
+        img = img[:, :, channel]
     nx = img.shape[0] // tile
     ny = img.shape[1] // tile
-    dcts = np.array([])
-    for i in range(nx):
-        for j in range(ny):
-            dcts = np.concatenate([dcts, tile_dct(img, i, j, tile, channel).flatten()])
-    hst = plt.hist(dcts)[0]
+    dcts = []
+    for i in range(nx - 1):
+        for j in range(ny - 1):
+            dct = dct_tile(img[:, :], i, j, tile, rate=rate).flatten()
+            dct = dct[abs(dct) < threshold]
+            dcts.append(dct)
+    return np.array(dcts)
 
+
+def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True):
[…]

### 2019-12-14 3-UHD/code/DCT_Judger.py
better feature extract

@@ -3,6 +3,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 from utils import *
 import sys
+import os
 
 
 def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True):
@@ -69,10 +70,11 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
 
 def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True):
     fnames = [e for e in os.listdir(folder) if e.split('.')[-1] in ('bmp', 'jpg', 'png')]
+    print("Processing {}".format(folder))
     feats = []
     for i, fname in enumerate(fnames):
         print('{} / {}'.format(i, len(fnames)))
-        img = get_image(folder + fname)
+        img = get_image(os.path.join(folder, fname))
         feat, _, _, _ = dct_feature_extract(img, tile, channel, samples, ref_rate, threshold, div_dct)
         feats.append(feat)
     return np.array(feats)
@@ -100,33 +102,33 @@ def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, thre
 #     hst = plt.hist(dcts)[0]
 
 if __name__ == '__main__':
-    if len(sys.argv) < 2:
-        print("Please specify the image folder.")
-        exit(-1)
-    folder = sys.argv[1]
-    tile = 32
-    channel = 0
-    samples = 50
-    ref_rate = 2
-    threshold = 20
-    div_dct = True
-    if len(sys.argv) > 2:
-        tile = int(sys.argv[2])
-    if len(sys.argv) > 3:
-        channel = int(sys.argv[3])
-    if len(sys.argv) > 4:
-        samples = int(sys.argv[4])
-    if len(sys.argv) > 5:
-        ref_rate = int(sys.argv[5])
-    if len(sys.argv) > 6:
-        threshold = int(sys.argv[6])
-    if len(sys.argv) > 7:
-        div_dct = bool(sys.argv[7])
-
-    feats = extract_feature_folder(folder, tile, channel, samples, ref_rate, threshold, div_dct)
-    np.savetxt(folder + "tile_{}_channel_{}_samples_{}_rate_{}_threshold_{}_div_{}.txt".format(tile, channel, samples,
-                                                                                               ref_rate, threshold,
-                                                                                               div_dct), feats)
+    # if len(sys.argv) < 2:
[…]

### 2019-12-14 3-UHD/code/DCT_feature_extract.py

@@ -1,0 +1,47 @@
+import argparse
+import os
+from DCT_Judger import *
+
+
+def bool_string(input_string):
+    if input_string not in {"True", "False"}:
+        raise ValueError("Please Enter a valid Ture/False choice")
+    else:
+        return (input_string == "True")
+
+
+def parse_args():
+    """ Parse command line arguments.
+    """
+    parser = argparse.ArgumentParser(description="Deep SORT")
+    parser.add_argument("folder", help="Image folder.", type=str)
+    parser.add_argument(
+        "--tile", help="Size of tile.",
+        default=32, type=int)
+    parser.add_argument(
+        "--channel", help="Channel of image.",
+        default=0, type=int)
+    parser.add_argument(
+        "--samples", help="Number of random tile samples.",
+        default=50, type=int)
+    parser.add_argument(
+        "--ref_rate", help="Reference down sampling rate.",
+        default=2, type=int)
+    parser.add_argument(
+        "--threshold", help="Threshold on the relative DCT value. "
+                            "Effective only when div_dct is True.",
+        default=0, type=int)
+    parser.add_argument(
+        "--div_ref_before", help="Divide reference before statistics.",
+        default=True, type=bool_string)
+    return parser.parse_args()
+
+
+if __name__ == '__main__':
+    args = parse_args()
+    feats = extract_feature_folder(args.folder, args.tile, args.channel, args.samples,
+                                   args.ref_rate, args.threshold, args.div_ref_before)
+    np.savetxt(os.path.join(args.folder, "tile_{}_channel_{}_samples_{}_rate_{}_threshold_{}_div_{}.txt"
+               .format(args.tile, args.channel, args.samples,
+                       args.ref_rate, args.threshold,
+                       args.div_ref_before), feats))

### 2019-12-14 3-UHD/code/DCT_feature_extract.py
bugfix for DCT feature extract

@@ -13,7 +13,7 @@ def bool_string(input_string):
 def parse_args():
     """ Parse command line arguments.
     """
-    parser = argparse.ArgumentParser(description="Deep SORT")
+    parser = argparse.ArgumentParser(description="DCT Feature")
     parser.add_argument("folder", help="Image folder.", type=str)
     parser.add_argument(
         "--tile", help="Size of tile.",
@@ -44,4 +44,4 @@ if __name__ == '__main__':
     np.savetxt(os.path.join(args.folder, "tile_{}_channel_{}_samples_{}_rate_{}_threshold_{}_div_{}.txt"
                .format(args.tile, args.channel, args.samples,
                        args.ref_rate, args.threshold,
-                       args.div_ref_before), feats))
+                       args.div_ref_before)), feats)

### 2019-12-14 3-UHD/code/DCT_Judger.py
another bugfix

@@ -63,8 +63,8 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
         dcts.append(dct)
         abds.append(abd)
         stds.append(std)
-    return np.array([np.mean(abds), np.min(abds), np.max(abds),
-                     np.mean(stds), np.min(stds), np.max(stds)]), \
+    return np.array([np.nanmean(abds), np.nanmin(abds), np.nanmax(abds),
+                     np.nanmean(stds), np.nanmin(stds), np.nanmax(stds)]), \
            np.array(dcts), np.array(abds), np.array(stds)
 
 
@@ -78,6 +78,12 @@ def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, thre
         feat, _, _, _ = dct_feature_extract(img, tile, channel, samples, ref_rate, threshold, div_dct)
         feats.append(feat)
     return np.array(feats)
+
+
+def extract_feature_single(fname, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True):
+    img = get_image(fname)
+    feat, _, _, _ = dct_feature_extract(img, tile, channel, samples, ref_rate, threshold, div_dct)
+    print(np.array(feat))
 
 
 # def tile_dct(img, i, j, tile, channel=0):
@@ -102,6 +108,9 @@ def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, thre
 #     hst = plt.hist(dcts)[0]
 
 if __name__ == '__main__':
+    extract_feature_single('images/1080P/bicubic/32.bmp', tile=32, channel=0, samples=50,
+                           ref_rate=2, threshold=20, div_dct=True)
+
     # if len(sys.argv) < 2:
     #     print("Please specify the image folder.")
     #     exit(-1)

### 2019-12-14 3-UHD/code/DCT_Judger.py
analysis and implementation of naive DCT classifier

@@ -4,6 +4,7 @@ import matplotlib.pyplot as plt
 from utils import *
 import sys
 import os
+import argparse
 
 
 def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True):
@@ -58,8 +59,8 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
             std = sqr_dev(dct)
         else:
             dct, ref = dct_tile(img[:, :], i, j, tile, rate=ref_rate, divide_ref=div_dct)
-            abd = abs_dev(dct) / abs_dev(ref)
-            std = sqr_dev(dct) / sqr_dev(ref)
+            abd = abs_dev(dct)  # / abs_dev(ref)
+            std = sqr_dev(dct)  # / sqr_dev(ref)
         dcts.append(dct)
         abds.append(abd)
         stds.append(std)
@@ -68,15 +69,20 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
            np.array(dcts), np.array(abds), np.array(stds)
 
 
-def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True):
+def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True, return_fnames=False, size=None):
     fnames = [e for e in os.listdir(folder) if e.split('.')[-1] in ('bmp', 'jpg', 'png')]
     print("Processing {}".format(folder))
     feats = []
     for i, fname in enumerate(fnames):
-        print('{} / {}'.format(i, len(fnames)))
+        if size is not None and i >= size:
+            break
+        print('{} / {}'.format(i, min(len(fnames), size)))
         img = get_image(os.path.join(folder, fname))
         feat, _, _, _ = dct_feature_extract(img, tile, channel, samples, ref_rate, threshold, div_dct)
         feats.append(feat)
+
+    if return_fnames:
+        return np.array(feats), fnames
     return np.array(feats)
 
 
@@ -84,6 +90,61 @@ def extract_feature_single(fname, tile, channel=0, samples=50, ref_rate=2, thres
     img = get_image(fname)
     feat, _, _, _ = dct_feature_extract(img, tile, channel, samples, ref_rate, threshold, div_dct)
     print(np.array(feat))
+
+
[…]

### 2019-12-14 3-UHD/code/DCT_feature_extract.py

@@ -3,13 +3,6 @@ import os
 from DCT_Judger import *
 
 
-def bool_string(input_string):
-    if input_string not in {"True", "False"}:
-        raise ValueError("Please Enter a valid Ture/False choice")
-    else:
-        return (input_string == "True")
-
-
 def parse_args():
     """ Parse command line arguments.
     """
@@ -30,9 +23,9 @@ def parse_args():
     parser.add_argument(
         "--threshold", help="Threshold on the relative DCT value. "
                             "Effective only when div_dct is True.",
-        default=0, type=int)
+        default=20, type=int)
     parser.add_argument(
-        "--div_ref_before", help="Divide reference before statistics.",
+        "--div_ref", help="Divide reference before statistics.",
         default=True, type=bool_string)
     return parser.parse_args()
 
@@ -40,8 +33,8 @@ def parse_args():
 if __name__ == '__main__':
     args = parse_args()
     feats = extract_feature_folder(args.folder, args.tile, args.channel, args.samples,
-                                   args.ref_rate, args.threshold, args.div_ref_before)
+                                   args.ref_rate, args.threshold, args.div_ref)
     np.savetxt(os.path.join(args.folder, "tile_{}_channel_{}_samples_{}_rate_{}_threshold_{}_div_{}.txt"
                .format(args.tile, args.channel, args.samples,
                        args.ref_rate, args.threshold,
-                       args.div_ref_before)), feats)
+                       args.div_ref)), feats)

### 2019-12-15 2-oracle/report/paper.tex
write abstract, title, author, and keywords

@@
 % Do not put math or special symbols in the title.
-\title{Bare Demo of IEEEtran.cls for Journals}
+\title{Oracle Bone Character Recognition\\ with CNN and Template Matching}
 %
@@
 
-\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
-	John~Doe,~\IEEEmembership{Fellow,~OSA,}
-	and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-	\thanks{M. Shell is with the Department
-		of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-		GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-	\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-	\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
+\author{
+	Zhongye~Wang,~\IEEEmembership{SJTU,}
+	Jinyu~Li,~\IEEEmembership{SJTU,}
+	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
+	Shangning~Xu,~\IEEEmembership{SJTU,}
+	and Chenxuan~Li,~\IEEEmembership{SJTU}
+}
 
@@
 \begin{abstract}
-	The abstract goes here.
+	In this project, we tackle the task of oracle bone character detection based on the dataset created in class.
+	Due to the limit size of dataset, we first augment data with affine transforms and noise transforms to obtain a larger and more robust dataset.
+	We then apply a simple CNN and template matching to implement models that can distinguish bone characters between micro categories (40 classes) and macro categories (10 classes).
+	We examine models using our homebrew bone character dataset and find the optimal models for micro and macro category classification tasks.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-	IEEEtran, journal, \LaTeX, paper, template.
+	Oracle bone character recognition, CNN, template matching, data augmentation.
 \end{IEEEkeywords}

### 2019-12-15 2-oracle/code/Dataset.py
implement CLI for OBC recognition

@@ -53,12 +53,14 @@ class Dataset:
         :param padding: add white padding around the image
         :return: images, labels
         """
-        path = '../dataset/' + folder + '/'
+        if filter_keys is not None or one_hot:
+            path = os.path.join('../dataset', folder)
+        else:
+            path = folder
         fnames = list(filter(lambda x: Dataset.aug_filter(x, filter_keys) ^ inclusive, os.listdir(path)))
-        cat = Dataset.folder_to_cat(folder, num_cat)
         imgs = []
         for fname in fnames:
-            img = Dataset.get_image_file(path + fname)
+            img = Dataset.get_image_file(os.path.join(path, fname))
             img = img.resize((Dataset.IMG_HEIGHT, Dataset.IMG_WIDTH), Image.ANTIALIAS)
             if normalize:
                 img = np.array(img)
@@ -66,11 +68,14 @@ class Dataset:
             if padding > 0:
                 img = ImageOps.expand(img, (padding, padding, padding, padding), 255)
             imgs.append(np.array(img))
-        if names:
-            return imgs, fnames
         imgs = np.array(imgs)
         if len(imgs.shape) < 4:
             imgs = imgs.reshape(imgs.shape + (1,))
+
+        if names:
+            return imgs, fnames
+
+        cat = Dataset.folder_to_cat(folder, num_cat)
         cats = np.repeat(cat, imgs.shape[0])
         if one_hot:
             cats = to_categorical(cats, num_cat)

### 2019-12-15 2-oracle/code/OBC_Recognition_app.py

@@ -1,0 +1,59 @@
+import argparse
+import numpy as np
+import pandas as pd
+from Dataset import Dataset
+from keras.models import load_model
+from template_matching import TemplateMatch
+
+
+def run(folder, output_fname, method, model_path, num_cat):
+    assert method in ['DNN', 'TM'], "Method can only be 'DNN' or 'TM'."
+    format = output_fname.split('.')[-1]
+    assert format in ['csv', 'txt'], "The format of the output file should be either 'csv' or 'txt'."
+
+    if method == 'DNN':
+        data, fnames = Dataset.get_image_folder(folder, num_cat, names=True, normalize=True)
+        data[data < 0.5] = 0
+    elif method == 'TM':
+        data, fnames = Dataset.get_image_folder(folder, num_cat, names=True, normalize=False)
+
+    if method == 'DNN':
+        model = load_model(model_path)
+        prob = model.predict(data)
+        y = np.argmax(prob, axis=1)
+    elif method == 'TM':
+        tm = TemplateMatch()
+        tm.load_model(model_path)
+        y = tm.match(data)
+
+    if format == 'csv':
+        df = pd.DataFrame({'fname': fnames, 'label': y})
+        df.to_csv(output_fname, index=False)
+    elif format == 'txt':
+        np.savetxt(output_fname, y)
+
+
+def parse_args():
+    """ Parse command line arguments.
+    """
+    parser = argparse.ArgumentParser(description="OBC Recognition")
+    parser.add_argument("--input_folder", help="Input image folder.", type=str)
+    parser.add_argument(
+        "--output_filename", help="The output txt file of classification results.",
+        default="output.csv", type=str)
+    parser.add_argument(
+        "--method", help="Method for classification. Either 'DNN' or 'TM'.",
+        default='DNN', type=str)
+    parser.add_argument(
+        "--model_path", help="Path to model for classification. Model should match 'method' and 'num_cat'.",
+        default='model/weights_norm_cat10_v2.hdf5', type=str)
+    parser.add_argument(
+        "--num_cat", help="Number of categories to classify. Either 10 or 40",
+        default=10, type=int)
+    return parser.parse_args()
+
+
+if __name__ == '__main__':
+    args = parse_args()
+    run(args.input_folder, args.output_filename, args.method,
+        args.model_path, args.num_cat)

### 2019-12-15 2-oracle/code/template_matching.py
add predict for template matching model

@@ -147,11 +147,11 @@ class TemplateMatch:
                                          normalize=True)
         X_val *= 255
 
-        m = self.match(X_val.copy())
+        m10, m40 = self.predict(X_val.copy())
 
         print('method:', self.method)
-        print('cat40', np.mean(m == y_val))
-        print('cat10', np.mean(m // 4 == y_val // 4))
+        print('cat10', np.mean(m10 == y_val // 4))
+        print('cat40', np.mean(m40 == y_val))
 
         if show_plot:
             plot_confusion_matrix(y_val // 4, m // 4, 10)
@@ -159,15 +159,29 @@ class TemplateMatch:
             plot_confusion_matrix(y_val, m, 40)
             plt.show()
 
-    def __call__(self, X):
-        '''
-        :param X: nparray m*h*w
-        :return: softmax score of each category
-        '''
-        # if X.ndim == 4:
-        #     X = X[:, :, :, 0]
-        scores = np.array([self.score(X, t) for t in self.templates])
-        return softmax(scores.T, axis=1)
+    # def __call__(self, X):
+    #     '''
+    #     :param X: nparray m*h*w
+    #     :return: softmax score of each category
+    #     '''
+    #     # if X.ndim == 4:
+    #     #     X = X[:, :, :, 0]
+    #     scores = np.array([self.score(X, t) for t in self.templates])
+    #     return softmax(scores.T, axis=1)
+
+    def predict(self, X, method=""):
+        """
+        :param X: number*height*width*channel
+        :param method: optional
+        :return: cat10_label, cat40_label
+        """
+        assert X.ndim == 4
+        if method:
+            self.method = method
+        if X.max() <= 1:
+            X *= 255
+        m = self.match(X)
+        return m // 4, m
 
 
 if __name__ == '__main__':

### 2019-12-15 2-oracle/report/paper.tex
make terminology consistent

@@
 % Do not put math or special symbols in the title.
-\title{Oracle Bone Character Recognition\\ with CNN and Template Matching}
+\title{Oracle Bone Inscription Recognition\\ with CNN and Template Matching}
 %
@@
 	Zhongye~Wang,~\IEEEmembership{SJTU,}
-	Jinyu~Li,~\IEEEmembership{SJTU,}
+	Jingyu~Li,~\IEEEmembership{SJTU,}
 	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
@@
 \begin{abstract}
-	In this project, we tackle the task of oracle bone character detection based on the dataset created in class.
+	In this project, we tackle the task of oracle bone inscription (OBI) detection based on the dataset created in class.
 	Due to the limit size of dataset, we first augment data with affine transforms and noise transforms to obtain a larger and more robust dataset.
@@
 \begin{IEEEkeywords}
-	Oracle bone character recognition, CNN, template matching, data augmentation.
+	OBI recognition, CNN, template matching, data augmentation.
 \end{IEEEkeywords}
@@
 \IEEEPARstart{O}{racle} bone inscription (OBI) is the earliest known Chinese writing, which dates back to the late 2nd millennium BC.
-Detection and recognition of oracle bone inscription is crucial for the understanding of the social and political characteristics of ancient Chinese.
+Detection and recognition of OBI is crucial for the understanding of the social and political characteristics of ancient Chinese.
 It is also significant in education and arts nowadays, as OBI is a cultural heritage of both China and the human civilization.
@@
 \section{Data Augmentation}
-The original dataset contains 40 micro categories of oracle bone characters, each with 85 samples.
+The original dataset contains 40 micro categories of OBIs, each with 85 samples.
 Therefore, we have $40 \times 85 = 3400$ samples in total.
@@
 \section{Character Recognition}
-We use two different methods to address the character recognition task for oracle bone characters.
+We use two different methods to address the character recognition task for OBIs.
 We first learn a deep convolutional neural network to recognize characters, then use the template matching method for the same task.
@@
 \subsection{Convolutional Neural Network}
-The deep neural network for learning the oracle bone characters has the structure in Figure~\ref{fig:network}.
+The deep neural network for learning the OBIs has the structure in Figure~\ref{fig:network}.
 
@@
 \subsection{Template Matching}
-For the oracle bone character recognition task, we also try a traditional method, template matching, to solve it.
+For the OBI recognition task, we also try a traditional method, template matching, to solve it.
 
@@
 \subsection{Test Set}
-We test models on our homebrew dataset where we write oracle bone characters using different pens, on different papers, and captured under different lighting condition.
+We test models on our homebrew dataset where we write OBIs using different pens, on different papers, and captured under different lighting condition.
 Figure~\ref{fig:testset} shows samples in the test set.

### 2019-12-15 2-oracle/code/template_matching.py
fix bugs

@@ -147,10 +147,10 @@ class TemplateMatch:
                                          normalize=True)
         X_val *= 255
 
-        m10, m40 = self.predict(X_val.copy())
+        m40 = self.predict(X_val.copy(), 40)
 
         print('method:', self.method)
-        print('cat10', np.mean(m10 == y_val // 4))
+        print('cat10', np.mean(m40 // 4 == y_val // 4))
         print('cat40', np.mean(m40 == y_val))
 
         if show_plot:

### 2019-12-16 3-UHD/code/DCT_Judger.py
fix the offset improvement

@@ -35,7 +35,7 @@ def self_ref_dct_complete(img, tile, channel=0, rate=2, threshold=20):
     return np.array(dcts)
 
 
-def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True):
+def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True, offset=0):
     if len(img.shape) > 3:
         img = img[:, :, channel]
 
@@ -53,7 +53,7 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
     stds = []
     for i, j in idxs:
         if div_dct:
-            dct = dct_tile(img[:, :], i, j, tile, rate=ref_rate, divide_ref=div_dct).flatten()
+            dct = dct_tile(img[:, :], i, j, tile, rate=ref_rate, divide_ref=div_dct).flatten() - offset
             dct = dct[abs(dct) < threshold]
             abd = abs_dev(dct)
             std = sqr_dev(dct)
@@ -69,16 +69,18 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
            np.array(dcts), np.array(abds), np.array(stds)
 
 
-def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True, return_fnames=False, size=None):
+def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True, return_fnames=False, size=None, offset=0):
     fnames = [e for e in os.listdir(folder) if e.split('.')[-1] in ('bmp', 'jpg', 'png')]
     print("Processing {}".format(folder))
     feats = []
+    if size is None:
+        size = len(fnames)
     for i, fname in enumerate(fnames):
-        if size is not None and i >= size:
+        if i >= size:
             break
         print('{} / {}'.format(i, min(len(fnames), size)))
         img = get_image(os.path.join(folder, fname))
-        feat, _, _, _ = dct_feature_extract(img, tile, channel, samples, ref_rate, threshold, div_dct)
+        feat, _, _, _ = dct_feature_extract(img, tile, channel, samples, ref_rate, threshold, div_dct, offset)
         feats.append(feat)
 
     if return_fnames:
@@ -86,16 +88,16 @@ def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, thre
     return np.array(feats)
 
 
[…]

### 2019-12-16 3-UHD/code/DCT_feature_extract.py

@@ -27,14 +27,21 @@ def parse_args():
     parser.add_argument(
         "--div_ref", help="Divide reference before statistics.",
         default=True, type=bool_string)
+    parser.add_argument(
+        "--offset", help="Shift the relative DCT value to left by 'offset'.",
+        default=0, type=float)
+    parser.add_argument(
+        "--max_image", help="Divide reference before statistics.",
+        default=None, type=int)
     return parser.parse_args()
 
 
 if __name__ == '__main__':
     args = parse_args()
     feats = extract_feature_folder(args.folder, args.tile, args.channel, args.samples,
-                                   args.ref_rate, args.threshold, args.div_ref)
-    np.savetxt(os.path.join(args.folder, "tile_{}_channel_{}_samples_{}_rate_{}_threshold_{}_div_{}.txt"
+                                   args.ref_rate, args.threshold, args.div_ref,
+								   offset=args.offset, size=args.max_image)
+    np.savetxt(os.path.join(args.folder, "tile_{}_channel_{}_samples_{}_rate_{}_threshold_{}_div_{}_offset_{}.txt"
                .format(args.tile, args.channel, args.samples,
                        args.ref_rate, args.threshold,
-                       args.div_ref)), feats)
+                       args.div_ref, args.offset)), feats)

### 2019-12-16 1-illusion/report/report.tex

@@
 
-\subsection{Illusion Detection}
-\label{sec:experiments_detection}
+\subsection{Dataset}
 
-\subsection{Illusion Generation}
-\label{sec:experiments_generation}
+Existing collections of illusion images feature variety rather than volume or machine readability, because these images are typically shared on social networks, displayed on websites and consumed by human beings.
+Robert and Roman's optical illusion image dataset \cite{williams2018optical} could be the first dataset about optical illusion published for research but lacks in organization.
+In light of these limitations,
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Describe how we collect the images: where are the images from and criteria
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Results}
+
+We use our own dataset for next-frame prediction and illusion detection.
+Due to the small size of our dataset, it is feasible for us to evaluate the effectiveness of our detection method on each image, both in the ``rotate'' group and the control group.
+We predict 22 frames for each image, and then the optical flow between the original image and its 7th frame is computed with Flownet and the traditional Lucas-Kanade method.
+Some representative images and their results are shown in Fig.~\ref{fig:representative-img-and-results}.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.24\linewidth]{fig/rotate-0.png}
+  \includegraphics[width=0.24\linewidth]{fig/rotate-1.png}
+  \includegraphics[width=0.24\linewidth]{fig/control-0.png}
+  \includegraphics[width=0.24\linewidth]{fig/control-1.png}
+
+  \includegraphics[width=0.24\linewidth]{fig/rotate-0-7.png}
+  \includegraphics[width=0.24\linewidth]{fig/rotate-1-7.png}
+  \includegraphics[width=0.24\linewidth]{fig/control-0-7.png}
+  \includegraphics[width=0.24\linewidth]{fig/control-1-7.png}
+
+  \includegraphics[width=0.24\linewidth]{fig/rotate-0-flo.png}
+  \includegraphics[width=0.24\linewidth]{fig/rotate-1-flo.png}
+  \includegraphics[width=0.24\linewidth]{fig/control-0-flo.png}
+  \includegraphics[width=0.24\linewidth]{fig/control-1-flo.png}
+
+  \includegraphics[width=0.24\linewidth]{fig/lk-rotate-0.png}
+  \includegraphics[width=0.24\linewidth]{fig/lk-rotate-1.png}
+  \includegraphics[width=0.24\linewidth]{fig/lk-control-0.png}
+  \includegraphics[width=0.24\linewidth]{fig/lk-control-1.png}
+
+  \caption{For Flownet, the output is a field of optical-flow vectors and visualized with a color field. Output for the Lucas-Kanade method is optical-flow vectors at keypoints in the images.}
+  \label{fig:representative-img-and-results}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.45\linewidth]{fig/control-0-vector-field.pdf}
+  \includegraphics[width=0.45\linewidth]{fig/control-1-vector-field.pdf}
+
+  \includegraphics[width=0.45\linewidth]{fig/rotate-0-vector-field.pdf}
+  \includegraphics[width=0.45\linewidth]{fig/rotate-1-vector-field.pdf}
+\end{figure*}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\linewidth]{fig/flow-mag-plot-rotate.pdf}
+  \includegraphics[width=\linewidth]{fig/flow-mag-plot-control.pdf}
+  \caption{}
+  \label{}
+\end{figure}
 

### 2019-12-16 1-illusion/report/report.tex
Complete the Experiments section

@@
 Some representative images and their results are shown in Fig.~\ref{fig:representative-img-and-results}.
+For intuitiveness, the optical-flow vector field computed by Flownet is sampled on fixed interval and plotted in Fig.~\ref{fig:vector-fields}.
+
+\subsection{Observations}
+
+From our experiment results in Fig.~\ref{fig:representative-img-and-results} and Fig.~\ref{fig:vector-fields}, some observations can be drawn:
+
+\paragraph{Neural networks can capture the motion in illusion images} From a human perspective, the 7th frame predicted by Prednet in Fig.~\ref{fig:representative-img-and-results} is almost identical to the original image, apart from the brightness change.
+However, Prednet predicts that the next frames of illusion images will have small motion compared with the original image.
+
+Traditional methods like Lucas-Kanade for computing the optical flow have the disadvantage that they work in a small neighborhood of the image and perform worse for images with significant motion.
+But in our task, the Lucas-Kanade method better captures the details in the predicted images and thus actually have an advantage.
+
+To further verify our findings, we compute optical flow for all images in our dataset and plot a histogram about magnitudes in Fig.~\ref{fig:histogram-of-magnitudes}.
+There is a significant difference in the distribution of magnitudes between the control images and the illusion images, which confirms the plausibility of our detection method.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\linewidth]{fig/flow-mag-plot-rotate.pdf}
+  \includegraphics[width=\linewidth]{fig/flow-mag-plot-control.pdf}
+  \caption{Histogram of magnitudes of optical-flow vectors computed with the Lucas-Kanade method, for the control and the ``rotate'' group.}
+  \label{fig:histogram-of-magnitudes}
+\end{figure}
+
+\paragraph{Prednet fails to recognize the direction of illusionary motion} Even though Prednet can ``see'' the illusion in the image, it misses the rotation direction in the illusion images, as evident in the last image of the second column of Fig.~\ref{fig:representative-img-and-results}.
+Some illusion images have directed rather than rotational motion.
+These images may be mistakenly classified as images with rotational illusion.
+
+\paragraph{Prednet's prediction seems to be highly dependent on the training dataset} In Watanabe \textit{et al.}'s experiment, Prednet, when trained on videos from the First-Person
+Social Interactions Dataset \cite{fathi2012social}, predicts significant and visible rotation for the upper-left image in Fig~.\ref{fig:representative-img-and-results}.
+But their experiment is limited to one single image and due to hardware limitation, we are unable to verify our hypothesis.
 
@@
 
-  \caption{For Flownet, the output is a field of optical-flow vectors and visualized with a color field. Output for the Lucas-Kanade method is optical-flow vectors at keypoints in the images.}
+  \caption{Some representative images.
+The first row consists of the original images.
+The second row is the 7th frame predicted by Prednet from the original image.
+Optical flows are computed between the original image and the 7th frame.
+The third row is the optical- flow vector field computed by Flownet and visualized with a color field.
+Each color represents a direction.
+Output for the Lucas-Kanade method is optical-flow vectors at keypoints in the images, in the fourth row.
+In and only in visualization, all optical-flow vectors computed using the Lucas-Kanade are scaled 60 times before drawing for clear comparison.}
   \label{fig:representative-img-and-results}
@@
   \includegraphics[width=0.45\linewidth]{fig/rotate-1-vector-field.pdf}
+
+  \caption{Plotted optical-flow vector fields computed by Flownet.
+Each plot from left to right, up to down, corresponds to the images in Fig.~\ref{fig:representative-img-and-results} in a left-to-right order.}
+  \label{fig:vector-fields}
 \end{figure*}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\linewidth]{fig/flow-mag-plot-rotate.pdf}
-  \includegraphics[width=\linewidth]{fig/flow-mag-plot-control.pdf}
-  \caption{}
-  \label{}
-\end{figure}
 

### 2019-12-16 3-UHD/code/DCT_Judger.py
find the threshold for the version with unit offset

@@ -95,9 +95,11 @@ def extract_feature_single(fname, tile, channel=0, samples=50, ref_rate=2, thres
 
 
 def classify_folder(folder, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True,
-                    thresholds_cut=(2.012829899787903, 3.586151076126429), method='rate2', size=None, offset=0):
+                    thresholds_cut=(2.1545941829681396, 3.656043997245576), method='rate2', size=None, offset=0):
+    # (2.012829899787903, 3.586151076126429)
     assert method in ['rate2', 'rate4', 'both'], "Parameter 'method' should be one of 'rate2', 'rate4', 'both'."
-    feats, fnames = extract_feature_folder(folder, tile, channel, samples, ref_rate, threshold, div_dct, return_fnames=True, size=size, offset=offset)
+    feats, fnames = extract_feature_folder(folder, tile, channel, samples, ref_rate, threshold, div_dct,
+                                           return_fnames=True, size=size, offset=offset)
     mask_rate2 = (feats[:, 0] > thresholds_cut[0])
     mask_rate4 = (feats[:, 3] > thresholds_cut[1])
     if method is 'rate2':

### 2019-12-16 3-UHD/report/paper.tex
some progress in the report of the third project

--- 2019-12-14 3-UHD/report/bare_jrnl.tex
@@
 \usepackage{comment}
-\usepackage{graphicx} 
+\usepackage{booktabs}
 \usepackage{subfigure}
-%\usepackage{cases}
-%\usepackage{subeqnarray}
+\usepackage{xcolor}
+\usepackage{listings}
+\lstset{
+  basicstyle=\fontsize{9}{10}\selectfont\ttfamily,
+  numbers=left,
+  numberstyle= \tiny,
+  keywordstyle= \color{ blue!70},
+  commentstyle= \color{red!50!green!50!blue!50},
+  frame=single,
+  rulesepcolor= \color{ red!20!green!20!blue!20} ,
+  escapeinside=``,
+  xleftmargin=1.5em,xrightmargin=0em, aboveskip=1em,
+  framexleftmargin=2em,
+  showstringspaces=false,
+  showtabs=false,
+  breaklines=true
+}
+\lstdefinelanguage{Solidity}
+{
+  morekeywords={contract, mapping, address, uint, private, function, public, if, payable},
+  morecomment=[l]{//},
+  morestring=[b]"
+}
+
+\usepackage{multicol}
+\usepackage{lipsum}
+\usepackage{mathtools}
+\usepackage{cuted}
+
+\usepackage{amsmath}
+\usepackage{extpfeil}
+\usepackage{mathpartir}
+\usepackage[mathscr]{eucal}
+
+\usepackage{hyperref}
+\usepackage{cleveref}
+
+\usepackage{CJK}
+
+\crefformat{section}{\S#2#1#3} % see manual of cleveref, section 8.2.1
+\crefformat{subsection}{\S#2#1#3}
+\crefformat{subsubsection}{\S#2#1#3}
 
@@
 
-\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
-        John~Doe,~\IEEEmembership{Fellow,~OSA,}
-        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-\thanks{M. Shell is with the Department
-of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
+\author{
+	Zhongye~Wang,~\IEEEmembership{SJTU,}
+	Jingyu~Li,~\IEEEmembership{SJTU,}
+	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
+	Shangning~Xu,~\IEEEmembership{SJTU,}
+	and Chenxuan~Li,~\IEEEmembership{SJTU}
+}
 
@@
 \subsubsection{Bilinear Interpolation}
-~\\
 \begin{figure}[h]
@@
 
+\section{Methodology}
+In this section, we \dots
+
+\subsection{A Naive Thought: Enumerative Search}
+\cref{sec:enumerative}
+We first try to tackle the problem with a very naive approach.
+If we know all possible ways to generate false UHD images, assuming the number of them is limited, we can actually enumerate through all of them to determine which algorithm is applied in any given false UHD image.
+
+We can do this by first subsampling a given image, then using every know algorithm to upsampling the downsampled image back to the original size.
+Say the image is originally faked with algorithm A, then the reconstructed image using algorithm A should result in very small MSE wrt. to the original one.
+If after enumerated all possible algorithms and subsampling rate (also assumed limited), no algorithm satisfy the above statement, then we can assert that the image is UHD.
+
+The naive algorithm to determine the authenticity of an UHD image is however impractical, because we cannot enumerate all possible ways to fabricate false UHD images and upsampling rate.
+The application of DNN in UHD image generation also makes such approach infeasible due to tremendous amount of hyper-parameters to it.
+
+However, we can still refer to the idea of reconstruct a reference image by first subsampling then upsampling with some reference interpolation method.
+If we use the most trivial interpolation method to generate the reference, for any given image, the more it improves from the reference, we are more confident that it is true UHD.
+This idea gives birth to the relative DCT analysis we propose later.
+
+\subsection{Relative DCT Analysis of UHD Images}
+The are natural differences between real UHD images and fake UHD image generated with interpolation.
+Real UHD images contains large amount of real objects, each with some random but distinct characteristics.
+Therefore, if we use functions to fit pixel values in different regions, there should be very few similarities between those functions.
+On the other hand, because it is often a common practice to use a single interpolation function to do upsampling to get fake UHD images, the functions in different regions should share certain similarities.
+Some interpolation methods (like bicubic) would even result in same family of those functions.
+
+Another idea is that, there are always noises in real UHD images due to the inherent deficiencies in equipments, whereas the fake UHD images undergoes a stage of subsampling, which eliminates some noises.
+As a result, the fake UHD image should be more smooth than the original one.
+We can use DCT to extract the magnitudes at different frequencies, and observe those for high frequencies is relatively lower in fake UHD images.
+
+We goes with the latter approach, while the former one is more promising if we have efficient way to identify similarities between sampled values of functions.
+Nevertheless, we need a way to extract features of those functions in both approaches, that is where discrete cosine transform (DCT) come into place.
+
+\subsubsection{Relative DCT Analysis}
+Different from traditional DCT analysis, we introduce the concept of relative DCT analysis based on the idea of reference image proposed in \ref{sec:enumerative}.
+The DCT coefficients for the original image are given by \eqref{eq:dct}.
+\begin{equation}
+	\begin{array}{l}
+		\mathcal{D}(u, v) = c(u)c(v)\sum_{x=0}^{N-1}\sum_{y=0}^{N-1}f(x, y)C(x, u)C(y, v)\\
+		\vspace{-0.75em}\\
+		\text{where } c(u) = \begin{cases}
+			\sqrt{\frac{1}{N}} & u = 0 \\
+			\sqrt{\frac{2}{N}} & u \neq 0
+		\end{cases}, C(x, u) = \cos\bigg[\frac{(x+0.5)\pi}{N}u\bigg]
+	\end{array}
+	\label{eq:dct}
+\end{equation}
+
+We define the reference image $f'$ with downsampling rate $\alpha$ and upsampling method $p$ and its DCT coefficients $\mathcal{D}'$.
+We then define the relative DCT transform in \eqref{eq:rel_dct}.
+\begin{equation}
+	\mathcal{D}_r(u, v) = \begin{cases}
+		\frac{\mathcal{D}(u, v)}{\mathcal{D}'(u, v)} - 1 & \mathcal{D}'(u, v) \neq 0 \\
+		\inf & \mathcal{D}'(u, v) = 0
+	\end{cases}
+	\label{eq:rel_dct}
+\end{equation}
+For any image, the relative DCT coefficients should give a fair criteria that is less sensitive to the content in the image.
+
+\subsubsection{Tiled DCT Analysis} We also consider it more practical to apply DCT analysis on tiles of images instead of the entire one.
+This is not only because it is faster and gives more stable and smaller DCT coefficients, but also due to the fact that the upsampling often considers only the region around the pixel to reconstruct.
+For some tile width $T$, we define the $(i, j)$ tile of image in \eqref{eq:tile}.
+\begin{equation}
+	\begin{array}{l}
+		f^{(i,j)}(x, y) = f(i * T + x, j * T + y), \\
+		\vspace{-0.75em}\\
+		\forall 0 \leq x, y < T, 0 \leq i, j < \min\{\lfloor\frac{W}{T}\rfloor, \lfloor\frac{H}{T}\rfloor\}
+	\end{array}
+	\label{eq:tile}
+\end{equation}
+We denote the relative DCT coefficients for the tile as $\mathcal{D}_r^{(i, j)}(u, v)$.
+
 \section{Conclusion}

### 2019-12-17 2-oracle/report/paper.tex
submission update for 2-oracle

@@
-\documentclass[journal]{IEEEtran}
+\documentclass[journal,conference]{IEEEtran}
 
@@
 	\begin{minipage}{\linewidth}
+		\hspace{-1.5em}
 		\subfigure[Confusion Matrix for 10 Category Classification]{
-			\includegraphics[width=\linewidth]{fig/confusion_oraclenet_conv10.png}
+			\includegraphics[width=1.1\linewidth]{fig/confusion_oraclenet_conv10.png}
 			\label{fig:network-confusion-10}
@@
 
-\subsection{Evaluation and Improvements}
+\subsection{Model Evaluation}
 To recognize characters in the test set, we need to first preprocess the samples.

### 2019-12-17 2-oracle/code/Dataset.py

@@ -13,8 +13,6 @@ ALL_KEYS = ('val', 'flipped', 'affine', 'noise', 'test')
 
 class Dataset:
     # default resize images to following size
-    # IMG_HEIGHT = 89
-    # IMG_WIDTH = 81
     IMG_HEIGHT = 64
     IMG_WIDTH = 64
 
@@ -26,9 +24,10 @@ class Dataset:
                     return False
         return True
 
-    # convert the folder name into categories
     @staticmethod
     def folder_to_cat(folder, num_cat=10):
+        """ Convert the folder name into categories
+        """
         assert num_cat in [10, 40], "Number of categories can only be 10 or 40"
         return (int(folder) - 102) // (40 / num_cat)
 
@@ -36,17 +35,15 @@ class Dataset:
     def cat40_to_cat10(cats):
         return cats // 4
 
-    # read single image
     @staticmethod
     def get_image_file(fname):
-        # img = np.array(Image.open(fname))
         img = Image.open(fname).convert('L')
-        return img  # .reshape(img.shape + (1,))
+        return img
 
     @staticmethod
     def get_image_folder(folder, num_cat=10, one_hot=False, filter_keys=None, inclusive=False, names=False, padding=0, normalize=False):
         """
-        get all resized images and their labels in one folder
+        Get all resized images and their labels in one folder
         :param folder: folder name
         :param num_cat: number of categories, 10 or 40
         :param one_hot: whether to use one hot encoding
@@ -88,7 +85,7 @@ class Dataset:
     @staticmethod
     def load_data(num_cat=10, one_hot=False, filter_keys=None, inclusive=False, padding=0, normalize=False):
         """
-        load all images in dataset folder
+        Load all images in dataset folder
         :param num_cat: number of categories
         :param one_hot: whether to use one hot encoding
         :return: X: shape [N, IMG_HEIGHT, IMG_WIDTH],
@@ -181,7 +178,7 @@ class DataAugmentation(object):
     @staticmethod
     def mark_val_folder(folder, path='../dataset/', val_per_cat=10, filter_keys=None):
         """
-
+        Mark validation samples.
         :param folder:
         :param path:
         :param val_size:
[…]

### 2019-12-17 2-oracle/code/OBC_Recognition_app.py

@@ -1,23 +1,31 @@
 import argparse
-import numpy as np
-import pandas as pd
-from Dataset import Dataset
-from keras.models import load_model
-from template_matching import TemplateMatch
 
 
-def run(folder, output_fname, method, model_path, num_cat):
+def run(folder, output_fname, method, model_path, num_cat, tm_method):
+    """ Main function that runs the classifier.
+    """
     assert method in ['DNN', 'TM'], "Method can only be 'DNN' or 'TM'."
+    assert tm_method in ['MSE', 'MSE_NORMED', 'CCORR', 'CCORR_NORMED'],\
+        "Method for template matching can only be one of 'MSE', 'MSE_NORMED', 'CCORR', 'CCORR_NORMED'"
     format = output_fname.split('.')[-1]
     assert format in ['csv', 'txt'], "The format of the output file should be either 'csv' or 'txt'."
 
+    import numpy as np
+    import pandas as pd
+    from Dataset import Dataset
+    from keras.models import load_model
+    from template_matching import TemplateMatch
+
+    # load data
     if method == 'DNN':
         data, fnames = Dataset.get_image_folder(folder, names=True, normalize=True)
         data[data < 0.5] = 0
     elif method == 'TM':
+        # fix model for template matching
         model_path = "model/templ.pkl"
         data, fnames = Dataset.get_image_folder(folder, names=True, normalize=False)
 
+    # generate prediction
     if method == 'DNN':
         model = load_model(model_path)
         prob = model.predict(data)
@@ -25,8 +33,9 @@ def run(folder, output_fname, method, model_path, num_cat):
     elif method == 'TM':
         tm = TemplateMatch()
         tm.load_model(model_path)
-        y = tm.predict(data, num_cat)
+        y = tm.predict(data, num_cat, tm_method)
 
+    # save prediction to file
     if format == 'csv':
         df = pd.DataFrame({'fname': fnames, 'label': y})
         df.to_csv(output_fname, index=False)
@@ -52,10 +61,14 @@ def parse_args():
     parser.add_argument(
         "--num_cat", help="Number of categories to classify. Either 10 or 40.",
         default=10, type=int)
+    parser.add_argument(
+        "--tm_method", help="Method for template matching to calculate the score."
+                            "Should be one of the 'MSE', 'MSE_NORMED', 'CCORR', 'CCORR_NORMED'.",
+        default='MSE', type=str)
     return parser.parse_args()
 
 
 if __name__ == '__main__':
[…]

### 2019-12-17 2-oracle/code/OracleNet.py

@@ -32,16 +32,6 @@ class OracleNetTrainer(object):
         # load original data
         self.X_train, y_train = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val', 'test'], normalize=True)
         self.X_val, y_val = Dataset.load_data(num_cat=40, one_hot=False, filter_keys=['val'], inclusive=True, normalize=True)
-        # X_train = X_train.reshape(X_train.shape)
-        # X_val = X_val.reshape(X_val.shape)
-        # X, y = Dataset.load_data(one_hot=False, num_cat=40)
-        # normalize image to 0.0 - 1.0
-        # covert to different categories
-        # y40 = Dataset.to_onehot(y, 40)
-        # y = Dataset.cat40_to_cat10(y)
-        # y10 = Dataset.to_onehot(y, 10)
-        # train test split
-        # idx = list(range(y40.shape[0]))
         self.y_train = {}
         self.y_val = {}
         self.y_train[40] = Dataset.to_onehot(y_train, 40)
@@ -50,9 +40,6 @@ class OracleNetTrainer(object):
         self.y_val[40] = Dataset.to_onehot(y_val, 40)
         y_val = Dataset.cat40_to_cat10(y_val)
         self.y_val[10] = Dataset.to_onehot(y_val, 10)
-        # self.X_train, self.X_val, y_train_idx, y_val_idx = train_test_split(X, idx, test_size=test_size, shuffle=True)
-        # self.y_train[40], self.y_val[40] = y40[y_train_idx], y40[y_val_idx]
-        # self.y_train[10], self.y_val[10] = y10[y_train_idx], y10[y_val_idx]
         # initialize callbacks
         self.checkpointer = ModelCheckpoint(filepath=autosave_path, verbose=1, save_best_only=True)
         self.visualizer = VisualizationCallback(vis_on_batch)
@@ -179,6 +166,7 @@ def cat10_model_conv():
     model.compile(loss='categorical_crossentropy', optimizer=sgd,
                   metrics=['accuracy'])
     return model
+
 
 def ensemble(model_cat10, model_cat40, num_cat):
     imgs = L.Input(shape=(64, 64, 1), name='ensemble_input')

### 2019-12-17 2-oracle/code/template_matching.py

@@ -2,19 +2,11 @@ import cv2
 import numpy as np
 import matplotlib.pyplot as plt
 from Dataset import Dataset, pipeline, ALL_KEYS
-from PIL import Image
 import pickle
 import os
-from scipy.special import softmax
 
 from utils import plot_confusion_matrix
 
-Dataset.IMG_HEIGHT = 64
-Dataset.IMG_WIDTH = 64
-
-
-# PADDING = 40
-# SCALE_THRESHOLD = 0.99
 
 class TemplateMatch:
     def __init__(self, padding=40, scale_threshold=0.99, method='CCORR_NORMED'):
@@ -27,9 +19,6 @@ class TemplateMatch:
     def get_best_scale(self, img):
         # set near white color to white
         img[img > self.white_thres] = 255
-        # plt.hist(img.ravel())
-        # plt.show()
-        # add padding
         img = cv2.copyMakeBorder(img, self.padding, self.padding, self.padding, self.padding,
                                  cv2.BORDER_CONSTANT, None, 255)
 
@@ -40,7 +29,6 @@ class TemplateMatch:
         suminv = np.sum(inv)
         cx = int(round(np.sum(inv * accx) / suminv))
         cy = int(round(np.sum(inv * accy) / suminv))
-        # print(cx,cy)
 
         # find the smallest square that enclose 99% of mass
         thres = self.scale_threshold
@@ -64,9 +52,6 @@ class TemplateMatch:
         for i in range(group.shape[0]):
             img = self.get_best_scale(group[i])
             templ += cv2.resize(img, size)
-        # show template
-        # plt.imshow(templ / group.shape[0])
-        # plt.show()
         return templ / group.shape[0]
 
     def score(self, group, template):
@@ -77,7 +62,6 @@ class TemplateMatch:
         for i in range(group.shape[0]):
             new_group[i] = cv2.resize(self.get_best_scale(group[i]), template.shape)
 
-        # custom implement
         if self.method == 'MSE':
             return np.mean((new_group - template) ** 2, axis=(1, 2))
         if self.method == 'MSE_NORMED':
@@ -90,19 +74,6 @@ class TemplateMatch:
             num = np.sum(new_group * template, axis=(1, 2))
             den = np.sqrt(np.sum(new_group ** 2, axis=(1, 2)) * np.sum(template ** 2))
             return num / den
-
-        # use cv2.matchTemplate
-        # else:
-        # # move template around to get the best match
[…]

### 2019-12-17 2-oracle/code/utils.py

@@ -6,18 +6,11 @@ from sklearn.utils.multiclass import unique_labels
 
 def plot_confusion_matrix(y_true, y_pred, classes,
                           normalize=False,
-                          title=None,
                           cmap=plt.cm.Blues):
     """
     This function prints and plots the confusion matrix.
     Normalization can be applied by setting `normalize=True`.
     """
-    if not title:
-        if normalize:
-            title = 'Normalized confusion matrix'
-        else:
-            title = 'Confusion matrix, without normalization'
-
     # Compute confusion matrix
     cm = confusion_matrix(y_true, y_pred)
     # Only use the labels that appear in the data
@@ -39,7 +32,6 @@ def plot_confusion_matrix(y_true, y_pred, classes,
            yticks=np.arange(cm.shape[0]),
            # ... and label them with the respective list entries
            xticklabels=np.arange(classes), yticklabels=np.arange(classes),
-           # title=title,
            ylabel='True label',
            xlabel='Predicted label')
 

### 2019-12-17 3-UHD/report/paper.tex
write the energy spectrum

@@
 
-\subsubsection{Relative DCT Analysis}
+\subsubsection{Relative DCT (RDCT) Analysis}
 Different from traditional DCT analysis, we introduce the concept of relative DCT analysis based on the idea of reference image proposed in \ref{sec:enumerative}.
@@
 
+Figure~\ref{fig:rdct_hist} shows the distribution of RDCT coefficients with magnitudes less than 20 in tiles of a sample image, where we use a reference sampling rate of 2 and use the nearest neighbor as a reference interpolation.
+
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{\linewidth}
+		\subfigure[Histogram for Small RDCT Coefficients in a 4K Sample]{
+			\includegraphics[width=\linewidth]{fig/rel_dct_hist_4k.png}
+			\label{fig:rdct_hist_4k}
+		}
+	\end{minipage}
+	\begin{minipage}{\linewidth}
+		\subfigure[Histogram for Small RDCT Coefficients in an upsampled 1080P Sample]{
+			\includegraphics[width=\linewidth]{fig/rel_dct_hist_1080.png}
+			\label{fig:rdct_hist_1080}
+		}
+	\end{minipage}
+	\caption{Histograms for Small RDCT Coefficients in the 64 Tiles on the Upper-Left Corner of 1.bmp: The x-axis is the magnitudes of RDCT coefficients ranging from -20 to 20.}
+	\label{fig:rdct_hist}
+\end{figure}
+
+\subsection{Relative Energy Spectrum}
+We can observe the distributions of RDCT coefficients are more flat for the true 4K image in Figure~\ref{fig:rdct_hist_4k} than those in the fake, upsampled 1080P image in Figure~\ref{fig:rdct_hist_1080}, with the peaks in the latter appearing more sharp.
+
+This phenomenon is actually prevalent not only in these tiles of the image, but also in most of tiles in all sample images.
+We can interpolate it as follows:\begin{enumerate}
+	\item The fake image become more smooth with value functions in different regions more unified towards the interpolation function.
+Therefore, some less relevant components (frequencies with small RDCT coefficients) will be suppressed in the fake, interpolated samples.
+	\item This does not mean that the components with large magnitudes are also suppressed.
+In fact, most of them stays the same as those in the original image, because they compose the dominant content of the image.
+\end{enumerate}
+
+Based on this knowledge, we step further to calculate the average relative energy spectrum in tile $(i, j)$ using \eqref{eq:energy}.
+\begin{equation}
+	E_r^{(i, j)} = \int_{u,v} \big|\mathcal{D}_r^{(i, j)}(u, v)\big|^2 dudv \Big/ \int_{u,v} dudv
+	\label{eq:energy}
+\end{equation}
+
+Figure~\ref{fig:ave-energy-hist} shows the average relative energy distribution for tiles in Figure~\ref{fig:rdct_hist}.
+It is obviously that the relative energy of the real UHD tiles is higher than those of all upsampled tiles.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{fig/rel_energy_4k_1080.png}
+	\caption{Histogram of Tile-Average Relative Energy Distribution}
+	\label{fig:ave-energy-hist}
+\end{figure}
+
+This gives us a preferable criteria to discriminate real and fake UHD image using relative DCT and energy spectrum analysis.
+We will then examine other ways of constructing the reference image and calculating the energy spectrum.
+
 \section{Conclusion}

### 2019-12-17 3-UHD/report/paper.tex
write experiments of simple thresholding

@@
 
+\usepackage{multirow}
 \usepackage{multicol}
@@
 \section{Methodology}
-In this section, we \dots
+In this section, we illustrate the concept and ideas behind our method of discriminating fake UHD images.
+We start with a naive thinking about fabrication of UHD images, and based on the idea of reference in it, we develop the concept of relative DCT analysis and the energy spectrum analysis of the RDCT.
 
@@
 
-The naive algorithm to determine the authenticity of an UHD image is however impractical, because we cannot enumerate all possible ways to fabricate false UHD images and upsampling rate.
+The naive algorithm to determine the authenticity of an UHD image is however impractical and inefficient, because we cannot enumerate all possible ways to fabricate false UHD images and upsampling rate.
 The application of DNN in UHD image generation also makes such approach infeasible due to tremendous amount of hyper-parameters to it.
@@
 \begin{equation}
-	E_r^{(i, j)} = \int_{u,v} \big|\mathcal{D}_r^{(i, j)}(u, v)\big|^2 dudv \Big/ \int_{u,v} dudv
+	E_{L_2}^{(i, j)} = \int_{u,v} \big|\mathcal{D}_r^{(i, j)}(u, v)\big|^2 dudv \Big/ \int_{u,v} dudv
 	\label{eq:energy}
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/rel_energy_4k_1080.png}
+	\includegraphics[width=0.99\linewidth]{fig/rel_energy_4k_1080.png}
 	\caption{Histogram of Tile-Average Relative Energy Distribution}
@@
 
+To extract the average relative energy spectrum of an image, we can either compute the average of all tile-average energy spectrum of all tiles of the image, or more efficiently, only compute those for randomly sampled tiles.
+In following experiments, we will go with the later one.
+
 This gives us a preferable criteria to discriminate real and fake UHD image using relative DCT and energy spectrum analysis.
 We will then examine other ways of constructing the reference image and calculating the energy spectrum.
+
+\section{Experiments}
+In this section, we build upon the concepts in the previous section to test different methods of discriminating fake UHD images.
+
+\subsection{A Simple Thresholding Method}
+We first extract the $L_1$ and $L_2$ relative energy spectrum of all images, with sampling rate 2 and nearest neighbor interpolation as the reference.
+The $L_1$ spectrum is defined by \eqref{eq:l1-energy}.
+\begin{equation}
+	E_{L_1}^{(i, j)} = \int_{u,v} \big|\mathcal{D}_r^{(i, j)}(u, v)\big| dudv \Big/ \int_{u,v} dudv
+	\label{eq:l1-energy}
+\end{equation}
+
+The average energy spectrums of all 200 images, with their original 4K resolution, and fabrication upsampled from 720P and 1080P with bicubic, bilinear, and lanzcos2 interpolation, are shown in Figure~\ref{fig:rel-energy-spec}.
+
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{0.95\linewidth}
+		\subfigure[$L_1$ Energy Spectrum and Threshold]{
+			\includegraphics[width=\linewidth]{fig/threshold_L1.png}
+		}
+	\end{minipage}
+	\begin{minipage}{0.95\linewidth}
+		\subfigure[$L_2$ Energy Spectrum and Threshold]{
+			\includegraphics[width=\linewidth]{fig/threshold_L2.png}
+		}
+	\end{minipage}
+	\caption{Relative Energy Spectrum of all 1400 Samples}
+	\label{fig:rel-energy-spec}
+\end{figure}
+
+We can easily distinguish between the energy spectrum of real 4K images and fake ones, where the curve for real ones occupy the higher part, while that of fake ones occupy the low part.
+We calculate the threshold that divides two groups by taking the average of the minimum energy spectrum value of the real ones (sample 160.bmp) and the maximum energy spectrum value of the fake ones (sample 112.bmp (720P bilinear) in $L_1$ and sample 94.bmp (720P bilinear) in $L_2$).
+We mark two thresholds with grey lines and those critical points in Figure~\ref{fig:rel-energy-spec}.
+
+We use these thresholds as criteria to judge the authenticity of a UHD image.
+When the average relative energy is higher than the threshold, then we label it as a true UHD image.
+Otherwise, we label it as a fake UHD image.
+Table~\ref{tab:threshold-confusion-table} shows the confusion matrix of classification results for 1400 samples using $L_1$ criteria and $L_2$ criteria separately.
+Both threshold models achieve remarkable accuracy.
+
+\linespread{1.2}
+\begin{table}[h]
+	\centering
+	\caption{Classification Result with Simple Thresholding}
+	\label{tab:threshold-confusion-table}
+	\begin{tabular}{|c|c|c|c|c|c|}
+	\hline
+	\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{2}{c|}{L1 Prediction} & \multicolumn{2}{c|}{L2 Prediction} \\ \cline{3-6} 
+	\multicolumn{2}{|c|}{}                  & Real             & Fake            & Real             & Fake            \\ \hline
+	\multirow{2}{*}{Truth}      & Real      & 199              & 1               & 199              & 1               \\ \cline{2-6} 
+								& Fake      & 1                & 1199            & 2                & 1198            \\ \hline
+	\end{tabular}
+\end{table}
+\linespread{1.0}
+
+We do realize that we are not testing the model on some hold-out set.
+But the model is too simple to cause overfitting, making the validation unnecessary.
+The quality of the threshold is desirable since it precisely splits the energy spectrums into two parts with no bias to any side.
+Notice that taking out those critical points causing the threshold would result in dramatic downfall in the performance.
+However, the critical points have already crossed the threshold and there are many other peak points centering around it, which means new data points will not have any meaningful improvements to the threshold.
+Therefore, our method should be valid.
 

### 2019-12-17 3-UHD/code/DCT_Judger.py
include other reference method

@@ -7,13 +7,13 @@ import os
 import argparse
 
 
-def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True):
+def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True, ref_int=cv2.INTER_AREA):
     img = np.float32(img)
     if len(img.shape) < 3:
         img_tile = img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile]
     else:
         img_tile = img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile, channel]
-    img_ref = cv2.resize(down_sample(img_tile, rate), dsize=img_tile.shape, interpolation=cv2.INTER_AREA)
+    img_ref = cv2.resize(down_sample(img_tile, rate), dsize=img_tile.shape, interpolation=ref_int)
     if divide_ref:
         tmp = cv2.dct(img_tile) / cv2.dct(img_ref)
     else:
@@ -35,7 +35,16 @@ def self_ref_dct_complete(img, tile, channel=0, rate=2, threshold=20):
     return np.array(dcts)
 
 
-def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True, offset=0):
+def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=20,
+                        div_dct=True, offset=0, ref_method='AR'):
+    ref_method_dict = {
+        'AR': cv2.INTER_AREA,
+        'NN': cv2.INTER_NEAREST,
+        'BL': cv2.INTER_LINEAR,
+        'BC': cv2.INTER_CUBIC,
+    }
+    assert ref_method in ref_method_dict.keys(), \
+        'The reference method can only be one of ' + str(ref_method_dict.keys())
     if len(img.shape) > 3:
         img = img[:, :, channel]
 
@@ -53,7 +62,8 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
     stds = []
     for i, j in idxs:
         if div_dct:
-            dct = dct_tile(img[:, :], i, j, tile, rate=ref_rate, divide_ref=div_dct).flatten() - offset
+            dct = dct_tile(img[:, :], i, j, tile,rate=ref_rate, divide_ref=div_dct,
+                           ref_int=ref_method_dict[ref_method]).flatten() - offset
             dct = dct[abs(dct) < threshold]
             abd = abs_dev(dct)
             std = sqr_dev(dct)
[…]

### 2019-12-17 3-UHD/code/DCT_feature_extract.py

@@ -33,6 +33,9 @@ def parse_args():
     parser.add_argument(
         "--max_image", help="Divide reference before statistics.",
         default=None, type=int)
+    parser.add_argument(
+        "--ref_method", help="Interpolation in reference images.",
+        default='AR', type=str)
     return parser.parse_args()
 
 
@@ -40,8 +43,8 @@ if __name__ == '__main__':
     args = parse_args()
     feats = extract_feature_folder(args.folder, args.tile, args.channel, args.samples,
                                    args.ref_rate, args.threshold, args.div_ref,
-								   offset=args.offset, size=args.max_image)
-    np.savetxt(os.path.join(args.folder, "tile_{}_channel_{}_samples_{}_rate_{}_threshold_{}_div_{}_offset_{}.txt"
-               .format(args.tile, args.channel, args.samples,
-                       args.ref_rate, args.threshold,
-                       args.div_ref, args.offset)), feats)
+								   offset=args.offset, size=args.max_image, ref_method=args.ref_method)
+    np.savetxt(os.path.join(args.folder, "tile_{}_channel_{}_samples_{}_rate_{}_threshold_{}_div_{}"
+                                         "_offset_{}_ref_{}.txt".format(args.tile, args.channel, args.samples,
+                                                                        args.ref_rate, args.threshold, args.div_ref,
+                                                                        args.offset, args.ref_method)), feats)

### 2019-12-17 1-illusion/report/report.tex
Almost complete the introduction

@@
 \label{sec:intro}
-\IEEEPARstart{M}{otion} illusion is one type of optical illusion where people perceive motions from some static images.
-Figure~\ref{fig:motion_example} shows some sample images with illusory motions.
-\begin{figure}[h]
+
+\IEEEPARstart{W}{hile} human visual system is reliable, ``mistakes'' are occasionally made, such as in the case of visual illusions.
+For example, motion illusion is one of the visual illusions in which we perceive motion that is different from that of the physical stimulus.
+Fig.~\ref{fig:motion_example} shows some sample images with illusory motions.
+In these images, the perception of motion arises from a completely static image.
+Despite being a still image, the rotating snake illusion induces strong perception motion in humans.
+Concerning this notable static stimulus, neurological and psychological studies suggest that both ocular motion and the information processing of the cerebral cortex are responsible for the perception of illusory motion \cite{HISAKATA20081940}.
+Research into visual illusion is key to the understanding of human visual system.
+
+Despite these deficiencies, until a few years ago, animate visual systems were the only ones known to be capable of broad-ranging visual object recognition.
+This has changed with the advent of deep neural networks (DNNs), which have been developed with reference to the network structures and the operational algorithms of the brain \cite{geirhos2018generalisation}.
+After having been trained on millions of labeled images, they sometimes even surpass human performance on tasks which only a few years ago were thought to be beyond an algorithmic solution for decades to come \cite{he2015delving, silver2016mastering}.
+
+Since DNNs and humans achieve similar accuracy, a number of studies have started investigating similarities and differences between DNNs and human vision \cite{cadieu2014deep, yamins2014performance, cichy2017dynamics}.
+On the one hand, the network units are an enormous simplification given the sophisticated nature and diversity of neurons in the brain .
+On the other hand, often the strength of a model lies not in replicating the original system but rather in its ability to capture the important aspects while abstracting from details of the implementation \cite{kriegeskorte2015deep}.
+
+If the analogy between neural network and neural system is plausible, then DNNs in computer vision might make the same ``mistakes'' as human visual system.
+Moreover, since predictive coding theory has been suggested to be a theoretical mechanism to generate illusions \cite{notredame2014visual}, one might expect that PredNet would also include ``mistakes'' similar to those associated with visual illusions for human.
+
+\begin{figure}[t]
   \centering
-	\begin{minipage}{0.48\linewidth}
-		\includegraphics[width=\linewidth]{fig/illusion_eg.jpg}
-	\end{minipage}\hfill
-	\begin{minipage}{0.48\linewidth}
-		\includegraphics[width=\linewidth]{fig/illusion_eg.jpg}
-	\end{minipage}
-	\caption{Motion Illusion Examples}
-	\label[]{fig:motion_example}
+  \includegraphics[width=0.48\linewidth]{fig/illusion_eg.jpg}
+  \includegraphics[width=0.48\linewidth]{fig/rotate-0.png}
+  \caption{Motion illusion examples. The image on the right is the ``rotating snake'' illusion.}
+  \label{fig:motion_example}
 \end{figure}
 
-Rest of the introduction \dots
+It should be noted that, despite the similarity in the network structure, humans and neural networks percept and acquire information in distinctive ways.
+Agents attack each problem \textit{tabula rasa}, whereas humans come in with a wealth of prior knowledge about the world, from physics to semantics to affordances.
+Rachit \textit{et al.} \cite{dubey2018investigating} experiments with giving human players and AI an original version and a modified version of a game, without any manual and instructions.
+In the modified version, the game textures are re-rendered so that objects familiar to human eyes like ladders and spikes are replaced with unfamiliar pixels.
+Despite the two games being structurally the same, human players took twice as long to finish the second game as the first one.
+In comparison, the performance of AI was approximately the same for the two games.
+Therefore, it is possible that due to these differences, DNNs ignore the visual illusion present in the images.
+
+It is worth considering whether indicators such as visual illusions can be reproduced in DNNs.
+The visual illusions that have been used to analyze the mechanism of visual processing may contribute to the study of DNNs as models of the brain.
+As another viewpoint, DNN technologies are now being applied in the real world.
+To understand the risks of DNNs, it is therefore critical to know whether DNNs would be misled by the same visual illusions as humans.
+The visual illusion reflects the constraints in the visual system and may be a legitimate adaptation to our living environment \cite{eagleman2001visual}; however, such misperception could constitute a fatal mistake, depending on the application of DNNs.
+
+In light of the possible relationship between DNNs and human visual system, we research into and evaluates Prednet's response to rotational illusion images.
+Prednet's response is characterized by the optical flow in the illusion images, and based on optical-flow vectors, we propose a detection method for motion illusion images and a potential architecture for generation of illusion images.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
   \centering

### 2019-12-17 1-illusion/report/report.tex
detailed outline

--- 2019-12-16 1-illusion/report/report.tex
@@
 \label{sec:detection_measure}
+\begin{enumerate}
+  \item Based on the motion reproduction model, we are able to represent the illusory motion with optical flows. However, we prefer a way to quantify the intensity of such motion.
+  \item Why? \begin{enumerate}
+    \item Need an objective criteria to determine the existence of motion illusion. Explain detailed reasons.
+    \item We need a numerical measurement of the intensity if we want to use GAN or similar optimization method to produce intensive illusion. Explain why.
+  \end{enumerate}
+  \item How? \begin{enumerate}
+    \item Simply sum up the norm. Explain the problem.
+    \item Find the rotation center and corresponding torque. Explain difficulty.
+    \item Other methods.
+  \end{enumerate}
+\end{enumerate}
 
@@
 \label{sec:detection_idf}
+\begin{enumerate}
+  \item We want to use flownet to replace the traditional optical flow procedure.
+  \item Pros. \begin{enumerate}
+    \item A convenient way to back propagate the error back to the prednet and further propagate it to the generator under the framework of GAN.
+Therefore the generator could improve the quality of illusory image.
+    \item Maybe some others.
+  \end{enumerate}
+  \item Cons. \begin{enumerate}
+    \item Slow.
+    \item Heavy.
+    \item Black box.
+    \item Maybe some others.
+  \end{enumerate}
+  \item How? \begin{enumerate}
+    \item Need to restructure the output of flownet to fit the context of our model. Vector field to something more quantifiable.
+    \item Assemble the adjusted flownet with the prednet to form the discriminator.
+    \item Possible fine tuning the integrated discriminator.
+  \end{enumerate}
+\end{enumerate}
 
@@
 \label{sec:generation}
+\begin{enumerate}
+  \item A brief introduction of the traditional GAN. (generator + discriminator + alternating training + the design of training loss)
+  \item In this scenario, we already have a working discriminator, and therefore we only need to design and train the generator. The training of discriminator is offline, therefore asymmetric.
+\end{enumerate}
 
@@
 \label{sec:generation_generator}
+\begin{enumerate}
+  \item Design a generator. \begin{enumerate}
+    \item Traditional DNN generator. (briefly explain the one in the original paper)
+    \item A simpler generator. Possibly some analytic functions that can be used for generating symmetric images.
+  \end{enumerate}
+\end{enumerate}
 
@@
 \label{sec:generation_criteria}
+\begin{enumerate}
+  \item The illusion intensity itself is not enough. Random noises might also have large illusion intensity. Sanity check of the image. \begin{enumerate}
+    \item Local entropy.
+    \item If using analytic function generator could avoid this.
+  \end{enumerate}
+\end{enumerate}
 

### 2019-12-17 1-illusion/report/report.tex
write construct dataset part

--- 2019-12-17 1-illusion/report/report.tex
@@
 \label{sec:detection_measure}
-\begin{enumerate}
-  \item Based on the motion reproduction model, we are able to represent the illusory motion with optical flows. However, we prefer a way to quantify the intensity of such motion.
-  \item Why? \begin{enumerate}
-    \item Need an objective criteria to determine the existence of motion illusion. Explain detailed reasons.
-    \item We need a numerical measurement of the intensity if we want to use GAN or similar optimization method to produce intensive illusion. Explain why.
-  \end{enumerate}
-  \item How? \begin{enumerate}
-    \item Simply sum up the norm. Explain the problem.
-    \item Find the rotation center and corresponding torque. Explain difficulty.
-    \item Other methods.
-  \end{enumerate}
-\end{enumerate}
 
@@
 \label{sec:detection_idf}
-\begin{enumerate}
-  \item We want to use flownet to replace the traditional optical flow procedure.
-  \item Pros. \begin{enumerate}
-    \item A convenient way to back propagate the error back to the prednet and further propagate it to the generator under the framework of GAN.
-Therefore the generator could improve the quality of illusory image.
-    \item Maybe some others.
-  \end{enumerate}
-  \item Cons. \begin{enumerate}
-    \item Slow.
-    \item Heavy.
-    \item Black box.
-    \item Maybe some others.
-  \end{enumerate}
-  \item How? \begin{enumerate}
-    \item Need to restructure the output of flownet to fit the context of our model. Vector field to something more quantifiable.
-    \item Assemble the adjusted flownet with the prednet to form the discriminator.
-    \item Possible fine tuning the integrated discriminator.
-  \end{enumerate}
-\end{enumerate}
 
@@
 \label{sec:generation}
-\begin{enumerate}
-  \item A brief introduction of the traditional GAN. (generator + discriminator + alternating training + the design of training loss)
-  \item In this scenario, we already have a working discriminator, and therefore we only need to design and train the generator. The training of discriminator is offline, therefore asymmetric.
-\end{enumerate}
 
@@
 \label{sec:generation_generator}
-\begin{enumerate}
-  \item Design a generator. \begin{enumerate}
-    \item Traditional DNN generator. (briefly explain the one in the original paper)
-    \item A simpler generator. Possibly some analytic functions that can be used for generating symmetric images.
-  \end{enumerate}
-\end{enumerate}
 
@@
 \label{sec:generation_criteria}
-\begin{enumerate}
-  \item The illusion intensity itself is not enough. Random noises might also have large illusion intensity. Sanity check of the image. \begin{enumerate}
-    \item Local entropy.
-    \item If using analytic function generator could avoid this.
-  \end{enumerate}
-\end{enumerate}
 
@@
 % Describe how we collect the images: where are the images from and criteria
+We construct a rotate group and a control group for our dataset.
+The rotate group images are those with rotating illusion manually selected from the above Robert dataset.
+The control group consists of images selected from a stock image website \emph{shutterstock}.
+We select the control group based on the principle that they have similar simple texture and symmetric pattern to those in rotate group and that they have no illusion.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-12-18 3-UHD/code/utils.py
add code to downsample 4K to 1080p and 720p

@@ -8,7 +8,7 @@ def get_image(fname):
     return cv2.imread(fname)
 
 
-def get_folder(folder="./images/4k/", callback=None, num_img=None):
+def get_folder(folder="./images/4K/", callback=None, num_img=None):
     fnames = [e for e in os.listdir(folder) if e.split('.')[-1] in ('bmp', 'jpg', 'png')]
     imgs = []
     for i, fname in enumerate(fnames):
@@ -16,7 +16,7 @@ def get_folder(folder="./images/4k/", callback=None, num_img=None):
             break
         if callback is not None:
             callback()
-        print('{} / {}'.format(i, len(fnames)))
+        print('{} / {}'.format(i + 1, len(fnames)))
         img = get_image(folder + fname)
         imgs.append(img)
     return np.array(imgs)
@@ -27,6 +27,14 @@ def down_sample(img, rate=2, sx=0, sy=0):
         return img[sx::rate, sy::rate]
     else:
         return img[sx::rate, sy::rate, :]
+
+
+def down_sample_all(imgs, rate=2, sx=0, sy=0):
+    assert len(imgs.shape) in (3, 4)
+    if len(imgs.shape) == 3:
+        return imgs[:, sx::rate, sy::rate]
+    else:
+        return imgs[:, sx::rate, sy::rate, :]
 
 
 def vis_hist(img, thresholds=(100, 1000, 10000), level=None):
@@ -55,4 +63,10 @@ def vis_hist(img, thresholds=(100, 1000, 10000), level=None):
 
 if __name__ == '__main__':
     imgs = get_folder()
-    print(imgs.shape)
+    print('downsampling...')
+    imgs2 = down_sample_all(imgs, 2)
+    imgs3 = down_sample_all(imgs, 3)
+    for i in range(imgs.shape[0]):
+        print('writing image', i + 1)
+        cv2.imwrite('./images/1080p/' + str(i + 1) + '.png', imgs2[i])
+        cv2.imwrite('./images/720p/' + str(i + 1) + '.png', imgs3[i])

### 2019-12-18 3-UHD/code/EDSR/src/main.py
edsr network

@@ -1,0 +1,39 @@
+import torch
+
+import utility
+import data
+import model
+import loss
+from option import args
+from trainer import Trainer
+import os
+
+os.environ['CUDA_VISIBLE_DEVICES'] = '1'
+
+# torch.cuda.set_device(1)
+torch.manual_seed(args.seed)
+checkpoint = utility.checkpoint(args)
+
+
+def main():
+    global model
+    if args.data_test == ['video']:
+        from videotester import VideoTester
+        model = model.Model(args, checkpoint)
+        t = VideoTester(args, model, checkpoint)
+        t.test()
+    else:
+        if checkpoint.ok:
+            loader = data.Data(args)
+            _model = model.Model(args, checkpoint)
+            _loss = loss.Loss(args, checkpoint) if not args.test_only else None
+            t = Trainer(args, loader, _model, _loss, checkpoint)
+            while not t.terminate():
+                t.train()
+                t.test()
+
+            checkpoint.done()
+
+
+if __name__ == '__main__':
+    main()

### 2019-12-18 3-UHD/code/edsr4k.sh
bash commande for edsr to generate 4K image

@@ -1,0 +1,6 @@
+cd EDSR/src
+echo "generating 4K from 1080p and 720p..."
+python main.py --data_test Demo --scale 2 --pre_train download --test_only --save_results --dir_demo ../../images/1080p
+mv ../experiment/test/results-Demo/ ../experiment/test/1080p
+python main.py --data_test Demo --scale 3 --pre_train download --test_only --save_results --dir_demo ../../images/720p
+mv ../experiment/test/results-Demo/ ../experiment/test/720p

### 2019-12-18 3-UHD/code/DCT_Judger.py
explore other features

@@ -13,11 +13,14 @@ def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True, ref_int=cv2.IN
         img_tile = img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile]
     else:
         img_tile = img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile, channel]
-    img_ref = cv2.resize(down_sample(img_tile, rate), dsize=img_tile.shape, interpolation=ref_int)
-    if divide_ref:
-        tmp = cv2.dct(img_tile) / cv2.dct(img_ref)
+    if ref_int is not None:
+        img_ref = cv2.resize(down_sample(img_tile, rate), dsize=img_tile.shape, interpolation=ref_int)
+        if divide_ref:
+            tmp = cv2.dct(img_tile) / cv2.dct(img_ref)
+        else:
+            tmp = (cv2.dct(img_tile), cv2.dct(img_ref))
     else:
-        tmp = (cv2.dct(img_tile), cv2.dct(img_ref))
+        tmp = cv2.dct(img_tile)
     return tmp
 
 
@@ -42,9 +45,12 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
         'NN': cv2.INTER_NEAREST,
         'BL': cv2.INTER_LINEAR,
         'BC': cv2.INTER_CUBIC,
+        'NO': None
     }
     assert ref_method in ref_method_dict.keys(), \
         'The reference method can only be one of ' + str(ref_method_dict.keys())
+    if ref_method == 'NO':
+        offset = 0
     if len(img.shape) > 3:
         img = img[:, :, channel]
 
@@ -62,7 +68,7 @@ def dct_feature_extract(img, tile, channel=0, samples=50, ref_rate=2, threshold=
     stds = []
     for i, j in idxs:
         if div_dct:
-            dct = dct_tile(img[:, :], i, j, tile,rate=ref_rate, divide_ref=div_dct,
+            dct = dct_tile(img[:, :], i, j, tile, rate=ref_rate, divide_ref=div_dct,
                            ref_int=ref_method_dict[ref_method]).flatten() - offset
             dct = dct[abs(dct) < threshold]
             abd = abs_dev(dct)

### 2019-12-19 3-UHD/code/combine_feature.py
include combine feature and pca visualization

@@ -1,0 +1,53 @@
+import numpy as np
+import os
+
+def load_features(fname):
+    data = {}
+    data['4k'] = np.loadtxt('images/4k/' + fname)
+    assert np.isnan(data['4k']).sum() == 0, "Missing data"
+    data['1080bl'] = np.loadtxt('images/1080P/bilinear/' + fname)
+    assert np.isnan(data['1080bl']).sum() == 0, "Missing data"
+    data['1080bc'] = np.loadtxt('images/1080P/bicubic/' + fname)
+    assert np.isnan(data['1080bc']).sum() == 0, "Missing data"
+    data['1080lz'] = np.loadtxt('images/1080P/lanczos2/' + fname)
+    assert np.isnan(data['1080lz']).sum() == 0, "Missing data"
+    data['720bl'] = np.loadtxt('images/720P/bilinear/' + fname)
+    assert np.isnan(data['720bl']).sum() == 0, "Missing data"
+    data['720bc'] = np.loadtxt('images/720P/bicubic/' + fname)
+    assert np.isnan(data['720bc']).sum() == 0, "Missing data"
+    data['720lz'] = np.loadtxt('images/720P/lanczos2/' + fname)
+    assert np.isnan(data['720lz']).sum() == 0, "Missing data"
+    return data
+
+
+def concate_features(fname_list, prefix='all'):
+    data = None
+    for fname in fname_list:
+        data_ = load_features(fname)
+        if data is None:
+            data = data_
+        else:
+            for key, item in data.items():
+                data[key] = np.concatenate([item, data_[key]], axis=1)
+    false_data = None
+    for key, item in data.items():
+        if key == '4k':
+            continue
+        if false_data is None:
+            false_data = item[:, :]
+        else:
+            false_data = np.concatenate([false_data, item], axis=0)
+    np.savetxt('images/' + prefix + '_true.txt', data['4k'])
+    np.savetxt('images/' + prefix + '_false.txt', false_data)
+
+
+if __name__ == "__main__":
+    fname_list = [
+        'tile_32_channel_0_samples_50_rate_2_threshold_20_div_True_offset_1.0.txt',
+        'tile_32_channel_0_samples_50_rate_2_threshold_20_div_True_offset_1.0_ref_NN.txt',
+        'tile_32_channel_0_samples_50_rate_2_threshold_20_div_True_offset_1.0_ref_BL.txt',
[…]

### 2019-12-19 3-UHD/code/SRCNN-keras/srcnn_4k.py
use srcnn to generate false 4K

@@ -1,0 +1,113 @@
+from keras.models import Sequential
+from keras.layers import Conv2D, Input, BatchNormalization
+# from keras.layers.advanced_activations import LeakyReLU
+from keras.callbacks import ModelCheckpoint
+from keras.optimizers import SGD, Adam
+import prepare_data as pd
+import numpy
+import math
+import cv2
+import os
+
+
+def psnr(target, ref):
+    # assume RGB image
+    target_data = numpy.array(target, dtype=float)
+    ref_data = numpy.array(ref, dtype=float)
+
+    diff = ref_data - target_data
+    diff = diff.flatten('C')
+
+    rmse = math.sqrt(numpy.mean(diff ** 2.))
+
+    return 20 * math.log10(255. / rmse)
+
+
+def model():
+    # lrelu = LeakyReLU(alpha=0.1)
+    SRCNN = Sequential()
+    SRCNN.add(Conv2D(nb_filter=128, nb_row=9, nb_col=9, init='glorot_uniform',
+                     activation='relu', border_mode='valid', bias=True, input_shape=(32, 32, 1)))
+    SRCNN.add(Conv2D(nb_filter=64, nb_row=3, nb_col=3, init='glorot_uniform',
+                     activation='relu', border_mode='same', bias=True))
+    # SRCNN.add(BatchNormalization())
+    SRCNN.add(Conv2D(nb_filter=1, nb_row=5, nb_col=5, init='glorot_uniform',
+                     activation='linear', border_mode='valid', bias=True))
+    adam = Adam(lr=0.0003)
+    SRCNN.compile(optimizer=adam, loss='mean_squared_error', metrics=['mean_squared_error'])
+    return SRCNN
+
+
+def predict_model():
+    # lrelu = LeakyReLU(alpha=0.1)
+    SRCNN = Sequential()
+    SRCNN.add(Conv2D(nb_filter=128, nb_row=9, nb_col=9, init='glorot_uniform',
+                     activation='relu', border_mode='valid', bias=True, input_shape=(None, None, 1)))
+    SRCNN.add(Conv2D(nb_filter=64, nb_row=3, nb_col=3, init='glorot_uniform',
+                     activation='relu', border_mode='same', bias=True))
[…]

### 2019-12-19 3-UHD/report/paper.tex

@@
 
+\usepackage{CJK}
+
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+
 \usepackage{hyperref}
 \usepackage{cleveref}
-
-\usepackage{CJK}
-
 \crefformat{section}{\S#2#1#3} % see manual of cleveref, section 8.2.1
@@
 
-Figure~\ref{fig:rdct_hist} shows the distribution of RDCT coefficients with magnitudes less than 20 in tiles of a sample image, where we use a reference sampling rate of 2 and use the nearest neighbor as a reference interpolation.
+Figure~\ref{fig:rdct_hist} shows the distribution of RDCT coefficients with magnitudes less than 20 in tiles of a sample image, where we use a reference sampling rate of 2 and use the area average as a reference interpolation.
 
@@
 \section{Experiments}
-In this section, we build upon the concepts in the previous section to test different methods of discriminating fake UHD images.
+In this section, we build upon previous concepts to test different methods of discriminating fake UHD images.
 
 \subsection{A Simple Thresholding Method}
-We first extract the $L_1$ and $L_2$ relative energy spectrum of all images, with sampling rate 2 and nearest neighbor interpolation as the reference.
+We first extract the $L_1$ and $L_2$ relative energy spectrum of all images, with sampling rate 2 and area average interpolation as the reference.
 The $L_1$ spectrum is defined by \eqref{eq:l1-energy}.
@@
 We can easily distinguish between the energy spectrum of real 4K images and fake ones, where the curve for real ones occupy the higher part, while that of fake ones occupy the low part.
-We calculate the threshold that divides two groups by taking the average of the minimum energy spectrum value of the real ones (sample 160.bmp) and the maximum energy spectrum value of the fake ones (sample 112.bmp (720P bilinear) in $L_1$ and sample 94.bmp (720P bilinear) in $L_2$).
+We calculate the threshold that divides two groups using the binary search depicted in Algorithm~\ref{alg:binary-search}.
+In this case, it is exactly the average of the minimum energy spectrum value of the real ones (sample 160.bmp) and the maximum energy spectrum value of the fake ones (sample 112.bmp (720P bilinear) in $L_1$ and sample 94.bmp (720P bilinear) in $L_2$).
 We mark two thresholds with grey lines and those critical points in Figure~\ref{fig:rel-energy-spec}.
+
+\begin{algorithm}[h]
+	\caption{Binary Search: A heuristic search for the optimal threshold minimizing total mistakes.}
+	\label{alg:binary-search}
+	\begin{algorithmic}
+		\Require The average energy spectrum of 200 true UHD images and 1200 fake UHD images.
+		\Ensure The threshold value.
+		\State $high \leftarrow \text{maximum energy spectrum in fake UHD images};$
+		\State $low \leftarrow \text{minimum energy spectrum in true UHD images};$
+		\State $best \leftarrow (low + high) / 2;$
+		\While{$low + \epsilon < high$}
+			\State Calculate the mistakes for positive and negative samples wrt. the current $mid$;
+			\If{False negative is more then false positive}
+				\State $low \leftarrow mid;$
+			\Else
+				\State $high \leftarrow mid;$
+			\EndIf
+			\If{The total mistakes for $mid$ are less than those for $best$}
+				\State $best \leftarrow mid;$
+			\EndIf
+		\EndWhile
+		\State \Return $best;$
+	\end{algorithmic}
+\end{algorithm}
 
@@
 
+We also test the simple thresholding method on energy spectrum extracted using other reference interpolation and reference rate.
+Table~\ref{tab:acc-ref-param} shows the accuracy for different parameter settings of the reference images.
+
+\linespread{1.2}
+\begin{table}[h]
+	\caption{Accuracy for Different Reference Settings}
+	\label{tab:acc-ref-param}
+	\begin{tabular}{|c|c|c|c|c|c|}
+	\hline
+	\multicolumn{2}{|c|}{Parameters}                                                & \multicolumn{2}{c|}{L1 Accuracy}      & \multicolumn{2}{c|}{L2 Accuracy}      \\ \hline
+	Ref Rate           & \begin{tabular}[c]{@{}c@{}}Ref\\ Method\end{tabular}       & Positive         & Negative           & Positive         & Negative           \\ \hline
+	\multirow{4}{*}{2} & Area                                                       & \textbf{199/200} & \textbf{1199/1200} & \textbf{199/200} & 1198/1200          \\ \cline{2-6} 
+					   & NN & \textbf{199/200} & \textbf{1199/1200} & \textbf{199/200} & \textbf{1199/1200} \\ \cline{2-6} 
+					   & Bilinear                                                   & 196/200          & 1199/1200          & 191/200          & 192/200            \\ \cline{2-6} 
+					   & Bicubic                                                    & 179/200          & 1178/1200          & 168/200          & 167/200            \\ \hline
+	3                  & Area                                                       & 153/200          & 1190/1200          & 155/200          & 1188/1200          \\ \hline
+	\end{tabular}
+\end{table}
+\linespread{1.0}
+
+The simplest reference interpolations, the area average and nearest neighbors, achieves the best performance, which confirms our conjecture that the reference is the baseline for the improvements of image quality.
+% Although larger reference rate causes dramatic performance drop, but from the visual
+
 \section{Conclusion}

### 2019-12-19 3-UHD/report/paper.tex
write joint feature and svm

@@
 The simplest reference interpolations, the area average and nearest neighbors, achieves the best performance, which confirms our conjecture that the reference is the baseline for the improvements of image quality.
-% Although larger reference rate causes dramatic performance drop, but from the visual
+
+\subsection{Joint Feature}
+In the previous experiments, although larger reference rate causes dramatic performance drop, we know from the visualization that the gap between the energy of true UHD images and fake UHD images varies greatly on some samples.
+Some gaps emerge in other reference method are absent from the area average and nearest neighbors ones.
+Therefore, we see the possibility of combining all possible average relative energy spectrums for one image into a feature of it, and apply traditional machine learning method to obtain a model for the joint feature.
+
+We select all 5 reference methods presented in Table~\ref{tab:acc-ref-param} along with the raw DCT energy spectrum, which is 12 features in total.
+After concatenating all features together into 10-dimensional vectors, we first apply principle component analysis to have a glance at the data distribution.
+Figure~\ref{fig:pca} shows the PCA visualization, from which we are sure there exists a efficient way to separate all true and fake UHD images.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.95\linewidth]{fig/pca.png}
+	\caption{PCA Visualization of all 12 Features}
+	\label{fig:pca}
+\end{figure}
+
+We apply the support vector machine classifier with RBF kernel and train the classifier on 43 positive samples and 237 negative samples and validate it on the rest 1120 samples.
+The SVM classifier achieves 100\% accuracy on both the training set and validation set.
+
+\subsection{Test Models on DNN Generated Images}
 

### 2019-12-20 3-UHD/report/paper.tex
write the dnn generated test and conclusion

@@
 \usepackage{cuted}
+\usepackage[normalem]{ulem}
+\useunder{\uline}{\ul}{}
 
@@
 
-\subsection{Joint Feature}
+\subsection{Joint Feature and SVM}
 In the previous experiments, although larger reference rate causes dramatic performance drop, we know from the visualization that the gap between the energy of true UHD images and fake UHD images varies greatly on some samples.
@@
 \subsection{Test Models on DNN Generated Images}
+We have previously ignored the fake UHD images generated with DNNs like SRCNN and EDSR, and now we use them to test and improve the models we have proposed.
+
+We first observe that the simple thresholding methods with area average reference and nearest neighbor reference still work for the fake UHD images generated with EDSR, while they fail dramatically for those generated with SRCNN.
+The performance for SVM using the joint feature also drops greatly encountering DNN generated images.
+Table~\ref{tab:acc-test} shows the accuracies for those methods.
+
+\linespread{1.2}
+\begin{table}[h]
+	\caption{Accuracy for Different Methods on DNN Generated Test Set}
+	\label{tab:acc-test}
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+		\hline
+		 & \multicolumn{4}{c|}{Simple Thresholding} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Joint\\ Feature\\ SVM\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Partially\\ Retrained\\ SVM\end{tabular}} \\ \cline{1-5}
+		\begin{tabular}[c]{@{}c@{}}DNN Type\\ \& Defintion\end{tabular} & AR L1 & AR L2 & NN L1 & NN L2 &  &  \\ \hline
+		SRCNN 1080P & 68\% & 55\% & \textbf{68.5\%} & 53.5\% & 46\% & {\ul \textbf{97\%}} \\ \hline
+		SRCNN 720P & 62.5\% & \textbf{63.5\%} & 60\% & 62.5\% & 37.5\% & {\ul \textbf{93.5\%}} \\ \hline
+		EDSR 1080P & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & {\ul \textbf{100\%}} & 94.5\% & {\ul \textbf{100\%}} \\ \hline
+		EDSR 720P & 95.5\% & \textbf{96.5\%} & \textbf{96.5\%} & 96\% & 93.5\% & {\ul \textbf{100\%}} \\ \hline
+	\end{tabular}
+\end{table}
+\linespread{1.0}
+
+This clearly shows the advantage of SRCNN over EDSR wrt. the ability to simulate real UHD images.
+We add the DNN generated samples onto the previous PCA visualization in Figure~\ref{fig:pca-dnn}.
+We can see that the DNN samples fills in exactly the gap between the interpolation generated samples and true UHD images, which causes the drop of the performance for various methods.
+However, this means we can also improve the performance at least for SVM by including some DNN generated samples into the training set, because the separation between true UHD samples and fake ones is still clear.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.95\linewidth]{fig/pca_dnn.png}
+	\caption{PCA Visualization with DNN Fake Samples}
+	\label{fig:pca-dnn}
+\end{figure}
+
+We combine the DNN generated samples with interpolated ones, and train a SVM model on 10\% of those samples with 97.7\% accuracy on the 10\% training set and 96.6\% accuracy on the 90\% training set.
+The accuracy of this partially trained model for different DNN fake images classification is shown in the last column of Table~\ref{tab:acc-test}.
 
 \section{Conclusion}
-The conclusion goes here.
+In this project, we explore the potential for DCT analysis on classifying true UHD images and fabricated ones by proposing the concept of reference and relative DCT analysis.
+We analyze the sampled energy spectrums of the relative DCT coefficients of a images and apply a simple thresholding method and SVM to perform the binary classification task.
+The simple thresholding requires very computation of features while the SVM provides stable performance even on DNN generated samples.
+
+In our application, we offer a simple thresholding model with area average reference and a SVM model trained on homebrew fake UHD images using both interpolation and DNN generation.
 

### 2019-12-20 3-UHD/code/DCT_Judger.py
implement interface for SVM classfier and simple thresholding classifier

@@ -1,13 +1,12 @@
 import cv2
 import numpy as np
-import matplotlib.pyplot as plt
 from utils import *
-import sys
 import os
 import argparse
+import pandas as pd
 
 
-def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True, ref_int=cv2.INTER_AREA):
+def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True, ref_int=cv2.INTER_AREA, origin=None):
     img = np.float32(img)
     if len(img.shape) < 3:
         img_tile = img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile]
@@ -15,10 +14,13 @@ def dct_tile(img, i, j, tile, channel=0, rate=2, divide_ref=True, ref_int=cv2.IN
         img_tile = img[i * tile:(i + 1) * tile, j * tile:(j + 1) * tile, channel]
     if ref_int is not None:
         img_ref = cv2.resize(down_sample(img_tile, rate), dsize=img_tile.shape, interpolation=ref_int)
-        if divide_ref:
-            tmp = cv2.dct(img_tile) / cv2.dct(img_ref)
+        if origin is not None:
+            tmp = origin / cv2.dct(img_ref)
         else:
-            tmp = (cv2.dct(img_tile), cv2.dct(img_ref))
+            if divide_ref:
+                tmp = cv2.dct(img_tile) / cv2.dct(img_ref)
+            else:
+                tmp = (cv2.dct(img_tile), cv2.dct(img_ref))
     else:
         tmp = cv2.dct(img_tile)
     return tmp
@@ -106,27 +108,48 @@ def extract_feature_folder(folder, tile, channel=0, samples=50, ref_rate=2, thre
     return np.array(feats)
 
 
-def extract_feature_single(fname, tile, channel=0, samples=50,ref_rate=2, threshold=20,
-                           div_dct=True, offset=0, ref_method='AR'):
+def extract_feature_single(fname, tile, channel=0, samples=50, ref_rate=2, threshold=20,
+                           div_dct=True, offset=1, ref_method='AR'):
     img = get_image(fname)
     feat, _, _, _ = dct_feature_extract(img, tile, channel, samples, ref_rate, threshold, div_dct, offset, ref_method)
     print(np.array(feat))
 
 
-def classify_folder(folder, tile, channel=0, samples=50, ref_rate=2, threshold=20, div_dct=True,
[…]

### 2019-12-20 3-UHD/code/SVM_Judger.py

@@ -1,0 +1,144 @@
+import os
+import argparse
+
+
+
+def complete_feature_extract(img, tile, channel=0, samples=50, threshold=20):
+    if len(img.shape) > 3:
+        img = img[:, :, channel]
+
+    xs = list(range(img.shape[0] // tile))
+    ys = list(range(img.shape[1] // tile))
+    np.random.shuffle(xs)
+    np.random.shuffle(ys)
+    idxs = list(zip(xs, ys))[:samples]
+
+    abs_dev = lambda x: abs(x).mean()
+    sqr_dev = lambda x: (x ** 2).mean() ** 0.5
+
+    # compute raw DCT
+    raw_dcts = []
+    abd = 0
+    std = 0
+    for i, j in idxs:
+        dct = dct_tile(img[:, :], i, j, tile, ref_int=None)
+        raw_dcts.append(dct)
+        abd += abs_dev(dct[dct < threshold])
+        std += sqr_dev(dct[dct < threshold])
+    raw_dcts = np.array(raw_dcts)
+    raw_feat = [abd / len(idxs), std / len(idxs)]
+
+    # compute relative DCT with rate 2
+    ref_method_dict = {
+        'AR': cv2.INTER_AREA,
+        'NN': cv2.INTER_NEAREST,
+        'BL': cv2.INTER_LINEAR,
+        'BC': cv2.INTER_CUBIC,
+    }
+    feature = []
+    for ref in ['AR', 'NN', 'BL', 'BC']:
+        abds = []
+        stds = []
+        for k, (i, j) in enumerate(idxs):
+            dct = dct_tile(img[:, :], i, j, tile, rate=2, origin=raw_dcts[k, :, :],
+                           ref_int=ref_method_dict[ref]).flatten() - 1
+            dct = dct[abs(dct) < threshold]
+            abd = abs_dev(dct)
+            std = sqr_dev(dct)
+            abds.append(abd)
+            stds.append(std)
+        feature += [np.nanmean(abds), np.nanmean(stds)]
+
+    # append raw DCT feature
+    feature += raw_feat
+
+    # compute DCT with rate 2 method AR
+    abds = []
+    stds = []
+    for k, (i, j) in enumerate(idxs):
+        dct = dct_tile(img[:, :], i, j, tile, rate=3, origin=raw_dcts[k, :, :],
+                       ref_int=ref_method_dict['AR']).flatten() - 1
+        dct = dct[abs(dct) < threshold]
[…]

### 2019-12-20 3-UHD/code/combine_feature.py

@@ -1,29 +1,39 @@
 import numpy as np
 import os
 
-def load_features(fname):
+def load_features(fname, mode='train'):
     data = {}
-    data['4k'] = np.loadtxt('images/4k/' + fname)
-    assert np.isnan(data['4k']).sum() == 0, "Missing data"
-    data['1080bl'] = np.loadtxt('images/1080P/bilinear/' + fname)
-    assert np.isnan(data['1080bl']).sum() == 0, "Missing data"
-    data['1080bc'] = np.loadtxt('images/1080P/bicubic/' + fname)
-    assert np.isnan(data['1080bc']).sum() == 0, "Missing data"
-    data['1080lz'] = np.loadtxt('images/1080P/lanczos2/' + fname)
-    assert np.isnan(data['1080lz']).sum() == 0, "Missing data"
-    data['720bl'] = np.loadtxt('images/720P/bilinear/' + fname)
-    assert np.isnan(data['720bl']).sum() == 0, "Missing data"
-    data['720bc'] = np.loadtxt('images/720P/bicubic/' + fname)
-    assert np.isnan(data['720bc']).sum() == 0, "Missing data"
-    data['720lz'] = np.loadtxt('images/720P/lanczos2/' + fname)
-    assert np.isnan(data['720lz']).sum() == 0, "Missing data"
+    if mode in ['train', 'all']:
+        data['4k'] = np.loadtxt('images/4k/' + fname)
+        assert np.isnan(data['4k']).sum() == 0, "Missing data"
+        data['1080bl'] = np.loadtxt('images/1080P/bilinear/' + fname)
+        assert np.isnan(data['1080bl']).sum() == 0, "Missing data"
+        data['1080bc'] = np.loadtxt('images/1080P/bicubic/' + fname)
+        assert np.isnan(data['1080bc']).sum() == 0, "Missing data"
+        data['1080lz'] = np.loadtxt('images/1080P/lanczos2/' + fname)
+        assert np.isnan(data['1080lz']).sum() == 0, "Missing data"
+        data['720bl'] = np.loadtxt('images/720P/bilinear/' + fname)
+        assert np.isnan(data['720bl']).sum() == 0, "Missing data"
+        data['720bc'] = np.loadtxt('images/720P/bicubic/' + fname)
+        assert np.isnan(data['720bc']).sum() == 0, "Missing data"
+        data['720lz'] = np.loadtxt('images/720P/lanczos2/' + fname)
+        assert np.isnan(data['720lz']).sum() == 0, "Missing data"
[…]

### 2019-12-20 3-UHD/code/DCT_Judger.py
update readme for project 3 and some minor fixes

@@ -166,7 +166,7 @@ def parse_args():
     parser.add_argument("--input_folder", help="Input image folder.", type=str)
     parser.add_argument(
         "--output_filename", help="The output txt file of classification results.",
-        default="output.txt", type=str
+        default="output.csv", type=str
     )
     parser.add_argument(
         "--max_image", help="Divide reference before statistics.",

### 2019-12-20 3-UHD/code/SVM_Judger.py

@@ -2,7 +2,6 @@ import os
 import argparse
 
 
-
 def complete_feature_extract(img, tile, channel=0, samples=50, threshold=20):
     if len(img.shape) > 3:
         img = img[:, :, channel]

### 2019-12-20 3-UHD/code/combine_feature.py

@@ -1,6 +1,7 @@
 import numpy as np
 import os
 
+
 def load_features(fname, mode='train'):
     data = {}
     if mode in ['train', 'all']:
@@ -51,7 +52,6 @@ def concate_features(fname_list, prefix='all', mode='train'):
         np.savetxt('images/' + prefix + '_true.txt', data['4k'])
     np.savetxt('images/' + prefix + '_false.txt', false_data)
     # print(false_data)
-
 
 
 if __name__ == "__main__":

### 2019-12-20 1-illusion/report/report.tex
add details to illusion detection, illusion generation and related work

--- 2019-12-17 1-illusion/report/report.tex
@@
 
+  Based on the motion reproduction model, we are able to represent the illusory motion with optical flows.
+To be more exact, the model generates one vector at each pixel, which indicates the strength and direction there.
+However, there is still some work to be done on the flow so as to quantify the intensity of rotating.
+
+  The first reason is that we prefer an objective criteria to determine the existence of motion illusion.
+Admittedly, optical flows can be a straightforward way to illustrate.
+For example, most people would concur that the first optical flow in Fig.~\ref{fig:standard_rotating_flows} is rotating, but different people may have different idea about the how strong the feeling is.
+Also, the question that whether flows are rotating can be more difficult to answer when the flows are more complex, such as the second flows in Fig.~\ref{fig:standard_rotating_flows}.
+
+  Another reason for establishing quantitative standards is that numerical measurement is necessary if we want to use Generative Adversarial Network(GAN) or other similar optimization method to produce intensive illusion.
+Generally, GAN is composed of two neural networks, one for generation and the other for discrimination.
+To apply the method, the discriminative network needs to know how "good" the generated photo is.
+In other word, it should evaluate the rotating intensity objectively.
+
+  \begin{figure}[t]
+    \centering
+    \includegraphics[width=0.4\linewidth,height=0.4\linewidth]{fig/standard_rotating.pdf}
+      \includegraphics[width=0.4\linewidth, height=0.4\linewidth]{fig/non_standard_rotating.pdf}
+    \caption{Examples of rotating flows.}
+    \label{fig:standard_rotating_flows}
+  \end{figure}
+
+  Given adequate reasons to build an objective standard, what is left to do is to use mathematical tools to devise such a standard. There are several ways to achieve the goal.
+
+  Summing up all the norms can be the most simple solution.
+The greater the sum is, the more the flows are moving.
+In spite of this, norms only use partial information of the flow, regardless of the direction, which can be equally important in detecting rotation.
+Similar to the case that histogram contains no information about the distribution of contents, we have no idea whether one or more "sources" exist in the flows indeed.
+
+  If we want to make use of direction as well as norm, a natural idea is to borrow the notion of "torque" in physics.
+Torque is the product of the magnitude of the force(flow) and the perpendicular distance of the line of action of force(flow) from the axis of rotation.
+It can describes how strong the inclination to rotate clockwise is on a two-dimensional plane.
+The main obstacle to fulfilling the algorithm is that some prior knowledge about source is necessary.
+On the one hand, the accuracy to choose the right source can play a big role in the final result.
+On the other hand, if we have multiple sources in a flow graph, then we also need to allocate each flow to its corresponding source, which can be another difficulty.
+
+  There are also other ways to judge the intensity of rotation from flows.
+For instance, Riemannian geometry provides us with some tools to assess some qualities of flows, but we don't consider it as our way to implement mainly because of its computational complexity.
+Besides, it is more suitable in continuous cases, while the flows calculated from the reproduction model is discrete.
+
   \subsection{Integrated Detector with Flownet}
   \label{sec:detection_idf}
+
+  In our experiment, we propose to use flownet to replace the traditional optical flow detection procedure.
+Flownet is comprised of appropriate convolutional neural networks (CNNs), which are capable of solving the optical flow estimation problem as a supervised learning task.
+
+  Traditionally, an optical flow detector is composed of several components.
+Sensors are carried on platform, which is responsible for removing undesirable motion, or background noise.
+\cite{sebok1997optical} After that, we apply well-designed filters, such as gradient for flow detection.
+\cite{naoya1990optical} Some other parts may be responsible for flow prediction, based on the input from the preceding components.
+Such a procedure is largely designed to detect and predict motions between different frames.
+To the best of our knowledge,  no previous work has been done on the prediction of flow given one frame.
+Moreover, it is too difficult to accomplish the task with traditional methods, given that the majority of them use the difference between frames as their main features.
+
+  Things can be different when it comes to convolutional neural network.
+It integrates these parts into a black box and directly output the prediction of flows, while what we need to do is to send input and receive output.
+With flownet, it is convenient to back propagate the error back to the prednet and further propagate it to the generator under the framework of GAN.
+Therefore, the generator assists in improving the quality of illusory image.
+
+  Although it is relatively easier to use flownet, we can not escape the shortcomings in applying CNN.
+First of all, it takes more time and CPU resources to compute the result for each pair of input, although it truly alleviate the pressure to design good algorithms for estimation and prediction by ourselves.
+Besides, the black box nature impose trouble in modifying the model, while we do benefit from the simple usage of such a network.
+
+  In order to incorporate flownet into our illusion detecting procedure, we need to reconstruct the output of flownet, which is shown in vector field, into something more quantifiable to fit the context of our model, just as described in part B.
+Apart from that, we just send two identical pictures into the model, and get output.
+The flownet should be adjusted and we need to finely tune the model for better performance if it is further used to form the discriminator.
 
@@
 
+  GAN was first proposed as estimating generative models in 2014.
+Similar to a a minimax two-player game, the generative model G is trained to maximize the probability of discriminative model D making a mistake, while D tries to better its performance in discrimination.
+\cite{goodfellow2014generative} In 2015, deep convolutional generative adversarial networks (DCGANs) to tackle unsupervised learning.
+It learns good image representations by training GANs, and later reuses parts of the generator and discriminator networks as feature extractors for supervised tasks.\cite{radford2015unsupervised} The generator and the discriminator are trained alternatively to improve their quality, where the proper design of training loss has huge influence on the final model.
+
+  When it comes to our scenario, a working discriminator has been chosen, thus we only need to design and train the generator.
+Here, the discriminator has already been trained and the training of discriminator is offline, therefore, the whole model is asymmetric.
+
   \subsection{Motion Illusion Generator}
@@
 
+  In theory, it is possible to construct a traditional DNN generator.
+However, consider the fact that we do not have too much pictures that can generate rotating illusion and we do not know much about principle behind the illusion, it can be difficult to write a model from scratch.
+  As a solution to the above problem, we may have to write a simpler generator, with more information given.
+For example, we may assume that we have a down-sampled picture as input, and what we need to do is to provide more details so that the output may seem to be rotating.
+Besides, there are also other properties that we can use.
+For example, we can make the assumption that the photo is symmetric, which can also make the generating procedure much easier.
+
   \subsection{Sanity Constraint Criteria}
   \label{sec:generation_criteria}
+
+  The illusion intensity itself is not enough.
+When a human looks at a picture, he will extract certain information from it, rather than look at all the pixels one by one.
+Some details may be omitted while others may be closely examined.
+In contrast, most computing-based models don't have the function, therefore are not immune to slight changes in input sometimes.
+In some cases, the original photos may not be rotating, but if we add rotating noise which is almost invisible to human eyes, the detection model can output wrong results.
+Thus, other sanity constraint criteria is also a necessity.
+We may apply local entropy calculation as a method, where whether or not it is a good criteria is another question.
 
@@
 
+  Probably the most closely related work is done by Eiji Watanabe et al.
+They propose to use natural scene videos of the self-motion of the viewer to train deep neural networks based model, PredNet, so as to detect rotational illusory motion.
+\cite{watanable2018illusory} Despite our work is based on similar networks, we do our experiment on a wider range of rotating illusions rather than one or two single pictures.
+What's more, we also propose an architecture to use GAN to generate pictures with similar illusory effects.
+
+  A more recent work by Emily use a pre-trained neural network to see if the network exhibits similar perceptual biases as human.
+The researcher examines four classic illusions,  Muller-Lyer, Ebbinghaus,  Ponzo and Vertical-Horizontal, and finds out that deep neural networks trained exclusively for object recognition exhibit the Muller-Lyer illusion, but not other illusions.
+\cite{ward2019exploring} .
+Gomez-Villa et al.
+also reveal that CNNs can be deceived by color illusion.
+\cite{gomez2018convolutional}
+
+  To the best of our knowledge, there are not many other researchers trying to apply neutral networks to the detection of illusion.
+In spite of this, CNNs have already been used for similar work such as object recognition.
+Liang et al.
+are inspired by the difference between feed-forward  architecture of CNN and abundant recurrent connections in the visual system, and propose a recurrent CNN (RCNN) for object recognition by incorporating recurrent connections into each convolutional layer.\cite{liang2015recurrent}
+
   \section{Conclusion}
   \label{sec:conclusion}
+
   The conclusion of the paper \dots

### 2019-12-20 1-illusion/report/report.tex
add details to conclusion

@@
 
-  The conclusion of the paper \dots
+  Applying deep neural networks to detect and generate rotation illusions has been of interest to more researchers.
+On the one hand, it provides us with a tool to better understand the nature of human vision systems.
+On the other hand, the procedure may exhibit special features of our neutral network, so that we may improve the network in the future.
+
+  In this paper, we focus on rotating illusions specifically, where a majority of people will view these pictures as rotating despite their static nature.
+A DNN model for future frame prediction, PredNet, is adopted to generate future frames, given several identical illusion pictures as input.
+After that, Flownet, composed of several convolutional neural networks, is used to detect flow in the output.
+The flows are further manipulated to decide the strength of rotation.
+We also discuss the pros and cons of different methodology, and propose to use asymmetric GAN to generate rotating illusory pictures.
+
+  In the experiments, we construct a rotate group and a control group from an optical illusion image dataset.
+With log magnitude histogram, we display certain feature of optical-flow field computed by Flownet.
+In our observations, Neural networks can capture the motion in illusion images as the distribution of log of magnitudes is significantly different in the rotate group and control group.
+However, Prednet fails to recognize the direction of illusionary motion, and some illusion images with directed motion may also be mistakenly classified as rotational ones.
+We illustrate that Prednet seems to be highly dependent on the training dataset, and its performance also differ on various pictures.
+
+  There are still some work to be done to understand the performance of neural network in illusion detection and generation.
+Some knowledge about the nature of human vision system and neural network may assist in future work.
+Moreover, more sophisticated tools may be used to refined our model, especially in the manipulation of flow vectors.
+In the future, we will also try to accomplish the proposed GAN to generate models, although how we can make use of prior knowlege requires deeper consideration.
 

### 2019-12-21 1-illusion/report/report.tex
Minor fix for the report
Notes on illusion generation

@@
 Robert and Roman's optical illusion image dataset \cite{williams2018optical} could be the first dataset about optical illusion published for research but lacks in organization.
-In light of these limitations,
-
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  % Describe how we collect the images: where are the images from and criteria
-  We construct a rotate group and a control group for our dataset.
+In light of these limitations, we construct a rotate group and a control group for our dataset.
 The rotate group images are those with rotating illusion manually selected from the above Robert dataset.
@@
 We select the control group based on the principle that they have similar simple texture and symmetric pattern to those in rotate group and that they have no illusion.
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   \paragraph{Prednet fails to recognize the direction of illusionary motion} Even though Prednet can ``see'' the illusion in the image, it misses the rotation direction in the illusion images, as evident in the last image of the second column of Fig.~\ref{fig:representative-img-and-results}.
+
+  Due to incorrectly-predicted directions, our proposed methods for detecting rotation couldn't distinguish rotation and translation.
 Some illusion images have directed rather than rotational motion.
 These images may be mistakenly classified as images with rotational illusion.
+The implementation of motion illusion creation is left as future work, as Flownet couldn't detect small displacements.
 
-  \paragraph{Prednet's prediction seems to be highly dependent on the training dataset} In Watanabe \textit{et al.}'s experiment, Prednet, when trained on videos from the First-Person
-  Social Interactions Dataset \cite{fathi2012social}, predicts significant and visible rotation for the upper-left image in Fig~.\ref{fig:representative-img-and-results}.
+  \paragraph{Prednet's prediction seems to be highly dependent on the training dataset} In Watanabe \textit{et al.}'s experiment, Prednet, when trained on videos from the First-Person Social Interactions Dataset \cite{fathi2012social}, predicts significant and visible rotation for the upper-left image in Fig~.\ref{fig:representative-img-and-results}.
 But their experiment is limited to one single image and due to hardware limitation, we are unable to verify our hypothesis.

### 2019-12-21 1-illusion/report/report.tex
Add an abstract

@@
   \begin{abstract}
-  The abstract goes here.
+    Visual illusion is key to the understanding of human visual system.
+Given that current deep neural networks' performance on some visual tasks is comparable to or can even surpass human performance, we explore the possibility of detecting and generating motion illusion images with neural networks, and discover potential similarity between human visual system and neural networks.
+We propose an architecture for motion illusion image detection and generation and evaluate the detector on our own dataset.
+The detector can distinguish between illusion images and non-illusion images because the motion in the illusion images is percepted by Prednet.
   \end{abstract}

### 2019-12-22 3-UHD/report/paper.tex
update fake image generation

@@
 % lcx
-\section{Subsampling and Interpolation}
+\section{Fake Image Generation}
 
-\subsection{Subsampling}
-Resampling using pixel area relation.
-Suppose $x\times y$ image subsampled down to size $x'\times y'$.
+\subsection{Downsampling}
+We first construct 1080P and 720P images using downsampling according to pixel area relation.
+Suppose $x\times y$ image downsampled down to size $x'\times y'$.
 scale\_x = x/x', scale\_y = y/y', and then we get block $scale\_x \times scale\_y$, block\_area = $scale\_x \times scale\_y$, the new image's each pixel is the weighted average of pixels in corresponding block's of the original image:
@@
 \subsection{Interpolation}
+The next step to construct fake images is to upsample those downsampled images back to 4K defintion.
 In the mathematical field of numerical analysis, interpolation is a type of estimation, a method of constructing new data points within the range of a discrete set of known data points.
-In this project we use bilinear interpolation, bicubic interpolation, Lanczos resampling.
+In this project we use bilinear interpolation, bicubic interpolation, Lanczos interpolation to generate fake images.
 
 \subsubsection{Bilinear Interpolation}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.6\linewidth]{fig/1.png}
-	\label{fig:Bilinear Interpolation}
-\end{figure}
 \par First do linear interpolation in the x-direction:
@@
 \begin{align*}
-p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}}{\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}{\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}}
+p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}} F {\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}} \\
+& \text{where } F = {\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}
 \end{align*}
@@
 
+Now we have 6 different categories of 1200 fake UHD images versus 200 real UHD images.
+Notice that we have not used DNN models for generating fake UHD images, which will be later used to examine our models.
+We then start developing models to distinguish real ones from fake ones.
+
 \section{Methodology}
@@
 
-We can do this by first subsampling a given image, then using every know algorithm to upsampling the downsampled image back to the original size.
+We can do this by first downsampling a given image, then using every know algorithm to upsampling the downsampled image back to the original size.
 Say the image is originally faked with algorithm A, then the reconstructed image using algorithm A should result in very small MSE wrt. to the original one.
-If after enumerated all possible algorithms and subsampling rate (also assumed limited), no algorithm satisfy the above statement, then we can assert that the image is UHD.
+If after enumerated all possible algorithms and downsampling rate (also assumed limited), no algorithm satisfy the above statement, then we can assert that the image is UHD.
 
@@
 
-However, we can still refer to the idea of reconstruct a reference image by first subsampling then upsampling with some reference interpolation method.
+However, we can still refer to the idea of reconstruct a reference image by first downsampling then upsampling with some reference interpolation method.
 If we use the most trivial interpolation method to generate the reference, for any given image, the more it improves from the reference, we are more confident that it is true UHD.
@@
 
-Another idea is that, there are always noises in real UHD images due to the inherent deficiencies in equipments, whereas the fake UHD images undergoes a stage of subsampling, which eliminates some noises.
+Another idea is that, there are always noises in real UHD images due to the inherent deficiencies in equipments, whereas the fake UHD images undergoes a stage of downsampling, which eliminates some noises.
 As a result, the fake UHD image should be more smooth than the original one.

### 2019-12-22 3-UHD/report/paper.tex
write abstract and update author

@@
 	Zhongye~Wang,~\IEEEmembership{SJTU,}
+	Chenxuan~Li,~\IEEEmembership{SJTU}
+	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
 	Jingyu~Li,~\IEEEmembership{SJTU,}
-	Xiaoyi~Bao,~\IEEEmembership{SJTU,}
-	Shangning~Xu,~\IEEEmembership{SJTU,}
-	and Chenxuan~Li,~\IEEEmembership{SJTU}
+	and Shangning~Xu,~\IEEEmembership{SJTU,}
 }
@@
 \begin{abstract}
-The abstract goes here.
+In this project, we tackle the problem of distinguishing fake UHD images from real UHD images with 4K resolution.
+We extend the basic DCT analysis to the relative DCT (RDCT) analysis by considering the DCT coefficients of the reference images, i.e., the fake UHD image constructed for the given image, which could be fake itself.
+This allows us to eliminate the influence of the context in the image to the DCT coefficients' distribution to certain degree.
+We consider different reference methods and use a simple thresholding classifier and a SVM classifier on the joint feature to perform the classification.
+The final SVM classifier achieves an accuracy rate higher than 95\% on the test set.
 \end{abstract}

### 2019-12-22 3-UHD/report/paper.tex
write related work and update title

@@
 % Do not put math or special symbols in the title.
-\title{Bare Demo of IEEEtran.cls for Journals}
+\title{Distinguish Real and Fake UHD Images with Relative Discrete Cosine Transform (RDCT)}
 %
@@
 \begin{IEEEkeywords}
-IEEEtran, journal, \LaTeX, paper, template.
+Ultra-High Definition, discrete cosine analysis, support vector machine
 \end{IEEEkeywords}
@@
 
-\section{Related Work}
 % lcx
@@
 \subsection{Interpolation}
-The next step to construct fake images is to upsample those downsampled images back to 4K defintion.
+The next step to construct fake images is to upsample those downsampled images back to 4K Definition.
 In the mathematical field of numerical analysis, interpolation is a type of estimation, a method of constructing new data points within the range of a discrete set of known data points.
@@
 		 & \multicolumn{4}{c|}{Simple Thresholding} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Joint\\ Feature\\ SVM\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Partially\\ Retrained\\ SVM\end{tabular}} \\ \cline{1-5}
-		\begin{tabular}[c]{@{}c@{}}DNN Type\\ \& Defintion\end{tabular} & AR L1 & AR L2 & NN L1 & NN L2 &  &  \\ \hline
+		\begin{tabular}[c]{@{}c@{}}DNN Type\\ \& Definition\end{tabular} & AR L1 & AR L2 & NN L1 & NN L2 &  &  \\ \hline
 		SRCNN 1080P & 68\% & 55\% & \textbf{68.5\%} & 53.5\% & 46\% & {\ul \textbf{97\%}} \\ \hline
@@
 
+\section{Related Work}
+There have not been many research into the task of classifying real and fake UHD images.
+Zhu \textit{et al.} \cite{zhu2016distinguish} also approach the problem using frequency domain analysis.
+They perform more complex analysis on the energy spectrum of images and give an efficient algorithm to classify real and fake UHD images.
+In comparison, our method is more naive but also achieves comparable results.
+
 \section{Conclusion}

### 2019-12-22 3-UHD/report/paper.tex
some intro

@@
 \section{Introduction}
-\IEEEPARstart{T}{his}
+\IEEEPARstart{U}tral-High Definition images refer to images with extremely high definitions.
+A common UHD is 4K resolution, which includes many definitions, one of which is 3840*2160 and is the images under the consideration of this project.
 
@@
 \subsection{A Naive Thought: Enumerative Search}
-\cref{sec:enumerative}
+\label{sec:enumerative}
 We first try to tackle the problem with a very naive approach.

### 2019-12-23 3-UHD/report/paper.tex
Replace en-dash with its ASCII equivalent
Otherwise pdfLaTeX will report errors for these characters.
Add an introduction for Project 3' report

@@
 A common UHD is 4K resolution, which includes many definitions, one of which is 3840*2160 and is the images under the consideration of this project.
+4K content, due to its high resolution and preservation of fine details, is superior in image quality to 2K and traditional HD content, and thus significantly enhance visual experience.
+4K content, especially 4K videos, is prevalent on all mainstream content providers.
+Also, given content providers' unprecedented willingness to purchase 4K content even at a much higher price, it is only natural that customers' acceptance and desire for 4K content will continue to increase.
+
+But the upgrade from HD to 4K is not only a change in the number of pixels.
+A complete upgrade of existing equipment and more processing power are only some of the prerequisites for producing true 4K videos.
+Customers' (and therefore content providers') desire for 4K content and the high cost of 4K production have given rise to a new concerning trend: some producers are actively selling 4K videos upscaled from 2K or HD to content providers, at the same price as true 4K videos.
+Wenhan \textit{et al.} \cite{zhu2016distinguish} claimed that visual quality of fake 4K videos are often worse than the HD contents being upscaled automatically by the 4K display devices due to the fact that their compression rate is generally higher to meet the bandwidth constraint.
+A method for distinguishing fake 4K from true 4K content has wide applications in real-life scenarios.
+
+Distinguishing fake 4K videos by subjective assessment is difficult and inefficient, because their differences in spatial domain are small.
+Also, the recent advancement of deep neural networks (DNN) for super resolution calls for evaluation of existing methods and possibly new methods.
+DNNs for super resolution are fundamentally different from traditional upscaling methods and capable of generating convincing high-resolution images from low-resolution images because of their strong priors.
+
+In this paper, we devise several methods to distinguish between true and fake 4K images.
+A dataset of fake 4K images is generated by first downsampling and then upscaling true 4K images, with both traditional methods like bilinear, bicubic, Lanczos and DNNs like SRCNN \cite{dong2015image} and EDSR \cite{lim2017enhanced}.
+The final SVM classifier achieves an accuracy rate greater than 95\% on the test set.
 
@@
 \end{align*}
-where a is usually set to −0.5 or −0.75.
+where a is usually set to $-0.5$ or $-0.75$.
 \par $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_i$=int(x+i), $y_j$=int(y+j), i, j = -1,0,1,2:

### 2019-12-23 3-UHD/report/paper.tex
fix report layout

@@
 p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}} F {\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}} \\
-& \text{where } F = {\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}
+\end{align*}
+\begin{align*}
+\text{where } F = {\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}
 \end{align*}
@@
 \par This algorithm reduces some of the visual distortion caused by resizing an image to a non-integral zoom factor.
-~\\
+
 \subsubsection{Bicubic Interpolation}
-~\\
-\par In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image.
+In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image.
 An interpolator can be obtained by applying a convolution with the following kernel in both dimensions:
@@
 \end{align*}
-\par Images resampled with bicubic interpolation are smoother and have fewer interpolation artifacts.
-~\\
+
+Images resampled with bicubic interpolation are smoother and have fewer interpolation artifacts.
+
 \subsubsection{Lanczos Resampling}
-~\\
-\par The effect of each input sample on the interpolated values is defined by the filter's reconstruction kernel L(x), called the Lanczos kernel. 
-\begin{align*}
-{\displaystyle L(x)={\begin{cases}\operatorname {sinc} (x)\,\operatorname {sinc} (x/a)&{\text{if}}\ -a<x<a,\\0&{\text{otherwise}}.\end{cases}}}
-\end{align*}
-Equivalently,
+The effect of each input sample on the interpolated values is defined by the filter's reconstruction kernel L(x), called the Lanczos kernel. 
+% \begin{align*}
+% {\displaystyle L(x)={\begin{cases}\operatorname {sinc} (x)\,\operatorname {sinc} (x/a)&{\text{if}}\ -a<x<a,\\0&{\text{otherwise}}.\end{cases}}}
+% \end{align*}
+% Equivalently,
 \begin{align*}
@@
 
-We use these thresholds as criteria to judge the authenticity of a UHD image.
-When the average relative energy is higher than the threshold, then we label it as a true UHD image.
-Otherwise, we label it as a fake UHD image.
-Table~\ref{tab:threshold-confusion-table} shows the confusion matrix of classification results for 1400 samples using $L_1$ criteria and $L_2$ criteria separately.
-Both threshold models achieve remarkable accuracy.
-
 \linespread{1.2}
@@
 \linespread{1.0}
+
+We use these thresholds as criteria to judge the authenticity of a UHD image.
+When the average relative energy is higher than the threshold, then we label it as a true UHD image.
+Otherwise, we label it as a fake UHD image.
+Table~\ref{tab:threshold-confusion-table} shows the confusion matrix of classification results for 1400 samples using $L_1$ criteria and $L_2$ criteria separately.
+Both threshold models achieve remarkable accuracy.
 

### 2020-01-02 1-illusion/lucas-kanade-visualization.py
Upload visualization code

@@ -1,0 +1,48 @@
+# no need to scale the image, because LaTeX will do it for you
+import cv2 as cv
+
+FLOW_SCALE_FACTOR = 60
+
+# params for ShiTomasi corner detection
+feature_params = dict(maxCorners=100,
+                      qualityLevel=0.3,
+                      minDistance=7,
+                      blockSize=7)
+# Parameters for lucas kanade optical flow
+lk_params = dict(winSize=(15, 15),
+                 maxLevel=2,
+                 criteria=(cv.TERM_CRITERIA_EPS | cv.TERM_CRITERIA_COUNT, 10, 0.03))
+red = (0, 0, 255)
+circle_color = (0, 255, 0)
+
+
+def visualize(group: str):
+    template_path = 'dataset/' + group + '/img{}-{}.png'
+
+    for i in range(2):
+        old_frame = cv.imread(template_path.format(i, 0))
+        old_gray = cv.cvtColor(old_frame, cv.COLOR_BGR2GRAY)
+        p0 = cv.goodFeaturesToTrack(old_gray, mask=None, **feature_params)
+
+        for j in range(7, 8):
+            drawings = old_frame.copy()
+            frame = cv.imread(template_path.format(i, j))
+            frame_gray = cv.cvtColor(frame, cv.COLOR_BGR2GRAY)
+            # calculate optical flow
+            p1, st, err = cv.calcOpticalFlowPyrLK(old_gray, frame_gray, p0, None, **lk_params)
+            # Select good points
+            good_new = p1[st == 1]
+            good_old = p0[st == 1]
+            # draw the tracks
+            for new, old in zip(good_new, good_old):
+                offset = (old - new) * FLOW_SCALE_FACTOR
+                old = tuple(new + offset)
+                new = tuple(new)
+                cv.line(drawings, new, old, red, 2)
+                cv.circle(drawings, new, 2, circle_color, -1)
+            cv.imwrite('lk-' + group + '-{}.png'.format(i), drawings)
+
+
+if __name__ == '__main__':
+    visualize('control')
+    visualize('rotate')

### 2020-01-02 1-illusion/optical-flow-histogram-blind.py

@@ -1,0 +1,44 @@
+import numpy as np
+import cv2 as cv
+import matplotlib.pyplot as plt
+
+# params for ShiTomasi corner detection
+feature_params = dict(maxCorners=100,
+                      qualityLevel=0.3,
+                      minDistance=7,
+                      blockSize=7)
+# Parameters for lucas kanade optical flow
+lk_params = dict(winSize=(15, 15),
+                 maxLevel=2,
+                 criteria=(cv.TERM_CRITERIA_EPS | cv.TERM_CRITERIA_COUNT, 10, 0.03))
+
+
+def visualize(n_img):
+    template_path = '/home/shining/school/cs386/1/pred_rotate1/img{}-{}.png'
+
+    bin_edges = np.linspace(-2, 2, 11)
+
+    for i in range(n_img):
+        hist = np.zeros(10)
+        old_gray = cv.imread(template_path.format(i, 0), cv.IMREAD_GRAYSCALE)
+        p0 = cv.goodFeaturesToTrack(old_gray, mask=None, **feature_params)
+        for j in range(7, 8):
+            frame_gray = cv.imread(template_path.format(i, j), cv.IMREAD_GRAYSCALE)
+            # calculate optical flow
+            p1, st, err = cv.calcOpticalFlowPyrLK(old_gray, frame_gray, p0, None, **lk_params)
+            # Select good points
+            good_new = p1[st == 1]
+            good_old = p0[st == 1]
+            log_magnitudes = tuple(
+                np.log10(np.square(new - old).sum()) / 2
+                for new, old in zip(good_new, good_old)
+            )
+            temp_hist, _ = np.histogram(log_magnitudes, bin_edges)
+            hist += temp_hist
+        plt.ylim(top=31)
+        plt.hist(bin_edges[:-1], bin_edges, weights=hist)
+        plt.show()
+
+
+if __name__ == '__main__':
+    visualize(6)

### 2020-01-02 1-illusion/optical-flow-histogram.py

@@ -1,0 +1,51 @@
+import numpy as np
+import cv2 as cv
+import matplotlib.pyplot as plt
+
+# params for ShiTomasi corner detection
+feature_params = dict(maxCorners=100,
+                      qualityLevel=0.3,
+                      minDistance=7,
+                      blockSize=7)
+# Parameters for lucas kanade optical flow
+lk_params = dict(winSize=(15, 15),
+                 maxLevel=2,
+                 criteria=(cv.TERM_CRITERIA_EPS | cv.TERM_CRITERIA_COUNT, 10, 0.03))
+
+
+def visualize(group_name, n_img):
+    template_path = '/home/shining/school/cs386/results/pred_' + group_name + '/img{}-{}.png'
+
+    bin_edges = np.linspace(-2, 2, 11)
+    hist = np.zeros(10)
+
+    for i in range(n_img):
+        old_gray = cv.imread(template_path.format(i, 0), cv.IMREAD_GRAYSCALE)
+        p0 = cv.goodFeaturesToTrack(old_gray, mask=None, **feature_params)
+        for j in range(7, 8):
+            frame_gray = cv.imread(template_path.format(i, j), cv.IMREAD_GRAYSCALE)
+            # calculate optical flow
+            p1, st, err = cv.calcOpticalFlowPyrLK(old_gray, frame_gray, p0, None, **lk_params)
+            # Select good points
+            good_new = p1[st == 1]
+            good_old = p0[st == 1]
+            log_magnitudes = tuple(
+                np.log10(np.square(new - old).sum()) / 2
+                for new, old in zip(good_new, good_old)
+            )
+            temp_hist, _ = np.histogram(log_magnitudes, bin_edges)
+            hist += temp_hist
+    hist /= n_img
+
+    plt.ylim(top=31)
+    plt.hist(bin_edges[:-1], bin_edges, weights=hist)
+    plt.xlabel('Lg of magnitudes')
+    plt.title(group_name)
+
+
+if __name__ == '__main__':
+    visualize('rotate', 17)
+    plt.savefig('flow-mag-plot-rotate.pdf')
+    plt.close()
+    visualize('control', 13)
+    plt.savefig('flow-mag-plot-control.pdf')

### 2020-01-02 1-illusion/vector-field-visualization.py

@@ -1,0 +1,22 @@
+import flowiz as fz
+import matplotlib.pyplot as plt
+
+STEP_SIZE = 8
+N_IMAGES = 2
+
+
+def visualize(group: str):
+    flow_path_template: str = 'dataset/flow/' + group + '-img{}.flo'
+    for i in range(N_IMAGES):
+        f = fz.read_flow(flow_path_template.format(i))
+
+        u = f[::STEP_SIZE, ::STEP_SIZE, 0]
+        v = f[::STEP_SIZE, ::STEP_SIZE, 1]
+        plt.quiver(u, v, color='orange')
+        plt.savefig(group + '-{}-vector-field.pdf'.format(i))
+        plt.close()
+
+
+if __name__ == '__main__':
+    visualize('control')
+    visualize('rotate')

### 2020-01-02 1-illusion/flownet2-docker/FN2_run-flownet-docker.py
Flownet2 code

@@ -1,0 +1,158 @@
+#!/usr/bin/env python2.7
+
+from __future__ import print_function
+
+import os, sys, numpy as np
+import argparse
+from scipy import misc
+import caffe
+import tempfile
+from math import ceil
+from pathlib import Path
+
+
+def dockerize_filepath_input(path):
+    """
+    Convert a given filepath to be relative to the inputfolder that this
+    container gets from the host system.
+    """
+    return os.path.join('/input', path)
+
+def dockerize_filepath_output(path):
+    """
+    Convert a given filepath to be relative to the output folder that this
+    container gets from the host system.
+    """
+    return os.path.join('/output', path)
+
+def readFlow(name):
+    if name.endswith('.pfm') or name.endswith('.PFM'):
+        return readPFM(name)[0][:,:,0:2]
+
+    f = open(name, 'rb')
+
+    header = f.read(4)
+    if header.decode("utf-8") != 'PIEH':
+        raise Exception('Flow file header does not contain PIEH')
+
+    width = np.fromfile(f, np.int32, 1).squeeze()
+    height = np.fromfile(f, np.int32, 1).squeeze()
+
+    flow = np.fromfile(f, np.float32, width * height * 2).reshape((height, width, 2))
+
+    return flow.astype(np.float32)
+
+def writeFlow(name, flow):
+    p = Path(name)
+    print(name)
+    p.parent.mkdir(parents=True, exists_ok=True)
+    f = open(name, 'wb')
+    f.write('PIEH'.encode('utf-8'))
+    np.array([flow.shape[1], flow.shape[0]], dtype=np.int32).tofile(f)
+    flow = flow.astype(np.float32)
+    flow.tofile(f)
+    f.flush()
+    f.close() 
+
+parser = argparse.ArgumentParser()
+parser.add_argument('caffemodel', help='path to model')
+parser.add_argument('deployproto', help='path to deploy prototxt template')
+parser.add_argument('img0', help='image 0 path')
+parser.add_argument('img1', help='image 1 path')
+parser.add_argument('out',  help='output filename')
+parser.add_argument('--gpu',  help='gpu id to use (0, 1, ...)', default=0, type=int)
+parser.add_argument('--verbose',  help='whether to output all caffe logging', action='store_true')
+
+args = parser.parse_args()
+
[…]

### 2020-01-02 1-illusion/flownet2-docker/resize.py

@@ -1,0 +1,10 @@
+from pathlib import Path
+
+import cv2 as cv
+
+input_dir = Path('pred_results')
+
+for p in input_dir.glob('**/*.png'): 
+   img = cv.imread(str(p)) 
+   res = cv.resize(img, None, fx=4, fy=4, interpolation=cv.INTER_CUBIC) 
+   cv.imwrite(str(p), res) 

### 2020-01-02 1-illusion/flownet2-docker/run-network.sh

@@ -1,0 +1,190 @@
+##
+# Author: Nikolaus Mayer
+##
+
+#!/usr/bin/env bash
+
+## Fail if any command fails (use "|| true" if a command is ok to fail)
+set -e
+## Treat unset variables as error
+set -u
+
+## Exit with error code
+fun__die () {
+  exit `false`;
+}
+
+## Print usage help
+fun__print_usage () {
+  printf "###################################################################\n";
+  printf "#                           FlowNet 2.0                           #\n";
+  printf "###################################################################\n";
+  printf "\n";
+  printf "Usage: ./run-network.sh -n network [-g gpu] [-v|vv] first-input second-input output\n";
+  printf "\n";
+  printf "where 'first-input' and 'second-input' are either both images (in which\n";
+  printf "case 'output' is interpreted as output file) or both files of newline-\n";
+  printf "separated filepaths (in which case the output argument must be a file\n";
+  printf "of newline-separated output filenames). All files must have the exact\n";
+  printf "same number of lines (one output per input pair).\n";
+  printf "The estimated flow maps the first input to the second input (i.e.\n";
+  printf "'first'==t, 'second'==t+1).\n";
+  printf "The input files must be within the current directory. All input and\n";
+  printf "output filenames will be treated as relative to this directory.\n";
+  printf "\n";
+  printf "The 'gpu' argument is the numeric index of the GPU you want to use.\n";
+  printf "This only makes sense on a multi-GPU system.\n";
+  printf "\n";
+  printf "By default, only errors are printed. Single verbosity (-v) prints\n";
+  printf "debug outputs, and double verbosity (-vv) also prints whatever the\n";
+  printf "docker container prints to stdout\n";
+  printf "\n";
+  printf "Available 'network' values:\n";
+  printf "  FlowNet2\n";
[…]
